### 2020-02-11 README.Rmd
Initial commit.

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# listdown

<!-- badges: start -->
[![Build Status](https://travis-ci.org/kaneplusplus/listdown.svg?branch=master)](https://travis-ci.org/kaneplusplus/listdown)
[![Build status](https://ci.appveyor.com/api/projects/status/by1g0f07uqvehh8t/branch/master?svg=true)](https://ci.appveyor.com/project/kaneplusplus/listdown/branch/master)
[![Codecov test coverage](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown?branch=master)
<!-- badges: end -->

The goal of listdown is to programmatically create R Markdown files from 
named lists. The package currently supports the creation of workflowr, 
pdf, word, html, and slide documents.

## Installation

<!--
You can install the released version of listdown from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("listdown")
```

And the development version from [GitHub](https://github.com/) with:
-->

You can install the development version of listdown from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kaneplusplus/listdown")
```

<!-- 
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(listdown)
## basic example code
```
-->

### 2020-02-11 README.Rmd
Fixes.

@@
 [![Build Status](https://travis-ci.org/kaneplusplus/listdown.svg?branch=master)](https://travis-ci.org/kaneplusplus/listdown)
-[![Build status](https://ci.appveyor.com/api/projects/status/by1g0f07uqvehh8t/branch/master?svg=true)](https://ci.appveyor.com/project/kaneplusplus/listdown/branch/master)
+[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kaneplusplus/listdown?branch=master&svg=true)](https://ci.appveyor.com/project/kaneplusplus/listdown)
 [![Codecov test coverage](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown?branch=master)

### 2020-02-11 README.Rmd
Appveyor.

@@
 
-The goal of listdown is to programmatically create R Markdown files from 
-named lists. The package currently supports the creation of workflowr, 
-pdf, word, html, and slide documents.
+## Overview
+
+The listdown package provides functions to programmatically create R Markdown files from 
+named lists. It is intended for data analysis pipelines where the presentation of the results
+is separated from their creation. For this use case, a data processing (or analysis) is performed
+and the results are provided in a single named list, organized heirarchically. From the list, 
+listdown creates a workflowr, pdf, word, or html page. List element names denote sections, subsections,
+subsubsection, etc. and the list elements contain the data structure to be presented including
+graphs and tables.
+The goal of the package is not to provide a finished, readable document.
+It is to provide a document  with all tables and visualization that will appear.
+This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions.
+
+listdown provides a reproducible means for _analytical_ document elements. It is most compatible with
+data analysis pipelines where the data format is fixed but the analyses are either being updated, 
+which may affect _narrative_ elements including the result discussion and conclusion, or where the
+experiment is different, which affects all narrative elements.
 

### 2020-02-12 README.Rmd
Testing.

@@
 is separated from their creation. For this use case, a data processing (or analysis) is performed
-and the results are provided in a single named list, organized heirarchically. From the list, 
-listdown creates a workflowr, pdf, word, or html page. List element names denote sections, subsections,
+and the results are provided in a single named list, organized heirarchically.
+With the list and a listdown object a workflowr, pdf, word, or html page.
+List element names denote sections, subsections,
 subsubsection, etc. and the list elements contain the data structure to be presented including
@@
 The goal of the package is not to provide a finished, readable document.
-It is to provide a document  with all tables and visualization that will appear.
-This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions.
+It is to provide a document with all tables and visualization that will appear (_computational_ components).
+This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions (_narrative_ components).
 
-listdown provides a reproducible means for _analytical_ document elements. It is most compatible with
-data analysis pipelines where the data format is fixed but the analyses are either being updated, 
-which may affect _narrative_ elements including the result discussion and conclusion, or where the
-experiment is different, which affects all narrative elements.
+listdown provides a reproducible means for producing a document with specified computational components.
+It is most compatible with data analysis pipelines where the data format is fixed but the analyses are either being updated, which may affect narrative components including the result discussion and conclusion, or where the experiment is different, which affects all narrative components If the narrative components are not changing with the data being pushed through your analysis pipeline, then you may be better off writing the R Markdown code manually.
 
@@
 
+## Example
+
+As a toy example, suppose we would like to create an html document plotting Anscombe's quartet with
+each plot having it's own section. To construct the document, we will need to two objects. The first
+is a presentation list, whose names indicate section (or subsection) titles and whose elements are
+the objects to present. The second is a `listdown` object, which describes how the object should 
+be rendered in the document.
+
+```{r eval = FALSE}
+library(listdown)
+library(ggplot2)
+
+data(anscombe)
+
+# Create the ggplot objects to display.
+pres_list <- list(
+  Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point() + theme_bw(),
+  `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point() + theme_bw(),
+  `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point() + theme_bw(),
+  `Outlier Horizontal` = ggplot(anscombe, aes(x = x4, y = y4)) + geom_point() + theme_bw())
+
+# Save the pres_list object so that it can be used in the R Markdown document.
+saveRDS(pres_list, "pres-list.rds")
+
+# Create a listdown object.
+ld <- listdown(load_ld_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
+               package = "ggplot2",                     # The packges needed to render plots.
+               decorator = list(ggplot = identity))     # What to do with the pres_list elements.
+
+# Output an html document to a string.
+doc <- c(
+  ld_rmarkdown_header("Anscombe's Quartet",
+                     author = "Francis Anscombe",
+                     date = "1973"),
+  ld_make_chunks(pres_list, ld))
+
+doc
+```
+
+```{r eval = TRUE, echo = FALSE}
+library(listdown)
+library(ggplot2)
+
+data(anscombe)
+
+# Create the ggplot objects to display.
+pres_list <- list(
+  Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point() + theme_bw(),
+  `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point() + theme_bw(),
+  `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point() + theme_bw(),
+  `Outlier Horizontal` = ggplot(anscombe, aes(x = x4, y = y4)) + geom_point() + theme_bw())
+
+# Create a listdown object.
+ld <- listdown(load_ld_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
+               package = "ggplot2",                     # The packges needed to render plots.
+               decorator = list(ggplot = identity))     # What to do with the plot types.
+
+# Output an html document to a string.
+doc <- c(
+  ld_rmarkdown_header("Anscombe's Quartet",
+                     author = "Francis Anscombe",
+                     date = "1973"),
+  ld_make_chunks(pres_list, ld))
+
+doc
+```
+
+The document can then be written to a file, rendered, and viewed with the following code.
+
+```{r message = FALSE, eval = FALSE}
+library(rmarkdown)
+
+writeLines(doc, file("anscombe.Rmd"))
+render("anscombe.Rmd")
+browseURL("anscombe.html")
+```
+
 <!-- 

### 2020-02-12 R/chunk-writer.r

@@ -50,6 +50,7 @@ ld_make_chunks.default <- function(pres_list, ld) {
            paste(class(ld), collapse = ":"), ".", sep = ""))
 }
 
+#' @export
 ld_make_chunks.listdown <- function(pres_list, ld) {
 
   ret_string <- ""

### 2020-02-12 R/depth-first-pres-list-visitor.r

@@ -1,19 +1,4 @@
 
-# Utility functions for depth-first traversal of presentation lists.
-list_loc_dive <- function(ll) {
-  ll <- c(ll, 1)
-  ll
-}
-
-list_loc_inc <- function(ll) {
-  if (is.null(ll)) {
-    ll <- 1
-  } else {
-    ll[length(ll)] <- ll[length(ll)] + 1
-  }
-  ll
-}
-
 list_loc_string <- function(ll) {
   if (is.null(ll)) {
     NULL

### 2020-02-12 tests/testthat/test-add-chunk-option.r

@@ -14,6 +14,10 @@ ld <- listdown(readRDS(here("option-check.rds")),
                package = "knitr",
                decorator = list(data.frame = kable))
 
+test_that("Only listdown objects can be used to make chunks.", {
+  expect_error(ld_make_chunks(letters, 1:10))
+})
+
 if (make_reference) {
   saveRDS(ld_make_chunks(pres_list, ld),
           file.path("reference-data", "chunk-option-1.rds"))
@@ -61,3 +65,13 @@ test_that("Chunks can have names and options.", {
                readRDS(file.path("reference-data", "chunk-option-4.rds")))
 })
 
+test_that("Options can be NULL", {
+  plt <- ld_chunk_opts(pres_list$iris, results = NULL)
+  expect_equal(attributes(plt)$listdown$results, "NULL")
+})
+
+test_that("Arg liststs can be created.", {
+  arg_list = list(echo = FALSE, eval = TRUE)
+  plt <- ld_chunk_opts(pres_list$iris, arg_list = arg_list)
+  expect_equal(attributes(plt)$listdown, arg_list)
+})

### 2020-02-12 tests/testthat/test-headers.r

@@ -1,0 +1,44 @@
+library(ggplot2)
+library(DT)
+
+context("Headers")
+
+source("make-reference.r")
+
+if (make_reference) {
+  dir.create("reference-data", showWarnings = FALSE)
+}
+
+if (make_reference) {
+  saveRDS(ld_workflowr_header("Workflow R"),
+          file.path("reference-data", "test-workflowr-header.rds"))
+}
+
+test_that("The workflowr header hasn't changed.", {
+  expect_equal(ld_workflowr_header("Workflow R"),
+               readRDS(file.path("reference-data", 
+                       "test-workflowr-header.rds")))
+})
+
+if (make_reference) {
+  saveRDS(ld_rmarkdown_header("R Markdown", "Author", "Date"),
+          file.path("reference-data", "test-rmarkdown-header.rds"))
+}
+
+test_that("The R Markdown header hasn't changed.", {
+  expect_equal(ld_rmarkdown_header("R Markdown", "Author", "Date"),
+               readRDS(file.path("reference-data", 
+                       "test-rmarkdown-header.rds")))
+})
+
+if (make_reference) {
+  saveRDS(ld_ioslides_header("R Markdown", "Author", "Date"),
+          file.path("reference-data", "test-ioslides-header.rds"))
+}
+
+test_that("The ioslides header hasn't changed.", {
+  expect_equal(ld_ioslides_header("R Markdown", "Author", "Date"),
+               readRDS(file.path("reference-data", 
+                       "test-ioslides-header.rds")))
+})
+

### 2020-02-12 README.Rmd
codecov.

@@
 [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kaneplusplus/listdown?branch=master&svg=true)](https://ci.appveyor.com/project/kaneplusplus/listdown)
-[![Codecov test coverage](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown?branch=master)
+[![codecov](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown)
 <!-- badges: end -->

### 2020-02-28 README.Rmd
COC
COC2
Added a default decorator option.

@@
 
-The listdown package provides functions to programmatically create R Markdown files from 
+The {listdown} package provides functions to programmatically create R Markdown files from 
 named lists. It is intended for data analysis pipelines where the presentation of the results
@@
 and the results are provided in a single named list, organized heirarchically.
-With the list and a listdown object a workflowr, pdf, word, or html page.
+With the list and a {listdown} object a workflowr, pdf, word, or html page.
 List element names denote sections, subsections,
@@
 
-listdown provides a reproducible means for producing a document with specified computational components.
+{listdown} provides a reproducible means for producing a document with specified computational components.
 It is most compatible with data analysis pipelines where the data format is fixed but the analyses are either being updated, which may affect narrative components including the result discussion and conclusion, or where the experiment is different, which affects all narrative components If the narrative components are not changing with the data being pushed through your analysis pipeline, then you may be better off writing the R Markdown code manually.
@@
 
-You can install the development version of listdown from [GitHub](https://github.com/) with:
+You can install the development version of {listdown} from [GitHub](https://github.com/) with:
 
@@
 -->
+
+## Code of Conduct
+
+Please note that the {listdown} project is released with a
+[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
+By contributing to this project, you agree to abide by its terms.

### 2020-02-28 R/chunk-writer.r

@@ -11,17 +11,30 @@
 #' to a decorator function.
 #' @param init_expr an initial expression that will be added to the outputted
 #' document after the libraries have been called.
+#' @param default_decorator the decorator to use for list elements whos type
+#' is not inherited from the decorator list. If NULL then the those
+#' elements will not be included when the chunks are written. By default
+#' this is identity, meaning that the elements will be passed directly 
+#' (through the identity() function).
 #' @param ... default options sent to the chunks of the outputted document.
 #' @export
 listdown <- function(load_ld_expr,
                      package = NULL,
                      decorator = list(),
                      init_expr = NULL,
+                     default_decorator = identity,
                      ...) {
+
+  if ( !("default_decorator" %in% names(as.list(match.call))) ) {
+    default_decorator = as.symbol("identity")
+  } else {
+    default_decorator = as.list(match.call()$default_decorator)
+  }
   ret <- list(load_ld_expr = match.call()$load_ld_expr,
               decorator = as.list(match.call()$decorator)[-1],
               package = package,
               init_expr = match.call()$init_expr,
+              default_decorator = default_decorator,
               dots = list(...))
   class(ret) <- "listdown"
   ret

### 2020-02-28 R/depth-first-pres-list-visitor.r

@@ -89,6 +89,17 @@ depth_first_concat <- function(pres_list, ld, heading = "#",
         depth_first_concat_impl(pres_list = pres_list, ld = ld,
                                 heading = paste0(heading, "#"),
                                 list_location = list_loc)
+      } else {
+        # It's not one of the decorators, and it's not a list. Use the
+        # default decorator.
+        if (!is.null(ld$default_decorator)) {
+          ret_str <<- c(ret_str,
+            sprintf("```{r%s}", 
+                    make_chunk_option_string(ld, eval(parse(text = pl)))),
+            paste0(as.character(ld$default_decorator), "(", pl, ")"),
+            "```",
+            "")
+        }
       }
     }
   }

### 2020-02-28 tests/testthat/test-make-chunks.r

@@ -57,8 +57,7 @@ test_that("The listdown object is the same as before.", {
 
 ld2 <- listdown(load_ld_expr = readRDS("a/file"),
                 package = c("ggplot2", "DT", "purrr"),
-                decorator = list(ggplot = identity,
-                                  data.frame = datatable),
+                decorator = list(data.frame = datatable),
                 init_expr = {
                   datatable <- partial(DT::datatable,
                                        options = list(ordering = FALSE))},

### 2020-03-02 R/chunk-writer.r
Vignettes and bug squashing.

@@ -5,7 +5,7 @@
 #' unquoted expression indicating how the presentation list will be loaded.
 #' In addition, libraries required by the outputted document and other
 #' paraeters can be specified.
-#' @param load_ld_expr an unquoted expression to load the presentation list.
+#' @param load_cc_expr an unquoted expression to load the presentation list.
 #' @param package a quoted list of package required by the outputted document.
 #' @param decorator a named list mapping the potential types of list elements
 #' to a decorator function.
@@ -18,7 +18,7 @@
 #' (through the identity() function).
 #' @param ... default options sent to the chunks of the outputted document.
 #' @export
-listdown <- function(load_ld_expr,
+listdown <- function(load_cc_expr,
                      package = NULL,
                      decorator = list(),
                      init_expr = NULL,
@@ -30,7 +30,7 @@ listdown <- function(load_ld_expr,
   } else {
     default_decorator = as.list(match.call()$default_decorator)
   }
-  ret <- list(load_ld_expr = match.call()$load_ld_expr,
+  ret <- list(load_cc_expr = match.call()$load_cc_expr,
               decorator = as.list(match.call()$decorator)[-1],
               package = package,
               init_expr = match.call()$init_expr,
@@ -46,26 +46,25 @@ listdown <- function(load_ld_expr,
 #' constructed the chunks can be rendered to a string, which can be appended
 #' to a file, with appropriate headers, resulting in a compilable R Markdown
 #' document.
-#' @param pres_list the presentation list. A named list of object to be
-#' displayed in the outputted R Markdown document.
 #' @param ld the listdown object that provides
 #' information on how a presentation object should be displayed in the
 #' output.
 #' @seealso \code{\link{listdown}}
 #' @export
-ld_make_chunks <- function(pres_list, ld) {
+ld_make_chunks <- function(ld) {
   UseMethod("ld_make_chunks", ld)
 }
 
 #' @importFrom crayon red
-ld_make_chunks.default <- function(pres_list, ld) {
+ld_make_chunks.default <- function(ld) {
   stop(red("Don't know how to render an object of class ",
            paste(class(ld), collapse = ":"), ".", sep = ""))
 }
 
 #' @export
-ld_make_chunks.listdown <- function(pres_list, ld) {
+ld_make_chunks.listdown <- function(ld) {
 
[…]

### 2020-03-02 R/depth-first-pres-list-visitor.r

@@ -47,22 +47,22 @@ make_chunk_option_string <- function(ld, pres_obj = NULL) {
   chunk_option_string
 }
 
-depth_first_concat <- function(pres_list, ld, heading = "#",
+depth_first_concat <- function(cc_list, ld, heading = "#",
                                list_location = c()) {
 
   ret_str <- ""
 
-  depth_first_concat_impl <- function(pres_list, ld, heading, list_location) {
+  depth_first_concat_impl <- function(cc_list, ld, heading, list_location) {
 
-    current_location <- paste0("pres_list", list_loc_string(list_location))
+    current_location <- paste0("cc_list", list_loc_string(list_location))
 
 
      list_locs <- lapply(seq_along(eval(parse(text = current_location))),
                          function(x) c(list_location, x))
 
     for (list_loc in list_locs) {
-      pll <- paste0("pres_list", list_loc_list_string(list_loc))
-      pl <- paste0("pres_list", list_loc_string(list_loc))
+      pll <- paste0("cc_list", list_loc_list_string(list_loc))
+      pl <- paste0("cc_list", list_loc_string(list_loc))
       pll_name <- names(eval(parse(text = pll)))
       if (pll_name != "") {
         ret_str <<- c(ret_str,
@@ -86,7 +86,7 @@ depth_first_concat <- function(pres_list, ld, heading = "#",
           "")
 
       } else if (inherits(eval(parse(text = pl)), "list")) {
-        depth_first_concat_impl(pres_list = pres_list, ld = ld,
+        depth_first_concat_impl(cc_list = cc_list, ld = ld,
                                 heading = paste0(heading, "#"),
                                 list_location = list_loc)
       } else {
@@ -103,7 +103,7 @@ depth_first_concat <- function(pres_list, ld, heading = "#",
       }
     }
   }
-  depth_first_concat_impl(pres_list = pres_list, ld = ld, heading = heading,
+  depth_first_concat_impl(cc_list = cc_list, ld = ld, heading = heading,
                           list_location = list_location)
   while(length(ret_str) > 0 && ret_str[length(ret_str)] == "") {
     ret_str <- ret_str[-length(ret_str)]

### 2020-03-02 tests/testthat/test-add-chunk-option.r

@@ -10,7 +10,9 @@ if (make_reference) {
 pres_list <- list(iris = iris, 
                   mtcars = mtcars)
 
-ld <- listdown(readRDS(here("option-check.rds")),
+saveRDS(pres_list, "reference-data/option-check.rds")
+
+ld <- listdown(readRDS("reference-data/option-check.rds"),
                package = "knitr",
                decorator = list(data.frame = kable))
 
@@ -19,12 +21,12 @@ test_that("Only listdown objects can be used to make chunks.", {
 })
 
 if (make_reference) {
-  saveRDS(ld_make_chunks(pres_list, ld),
+  saveRDS(ld_make_chunks(ld),
           file.path("reference-data", "chunk-option-1.rds"))
 }
 
 test_that("Output with no options works.", {
-  expect_equal(ld_make_chunks(pres_list, ld),
+  expect_equal(ld_make_chunks(ld),
                readRDS(file.path("reference-data", "chunk-option-1.rds")))
 })
 
@@ -32,36 +34,36 @@ pres_list$mtcars <- ld_chunk_opts(pres_list$mtcars,
                                   echo = FALSE, results = "as.is")
 
 if (make_reference) {
-  saveRDS(ld_make_chunks(pres_list, ld),
+  saveRDS(ld_make_chunks(ld),
           file.path("reference-data", "chunk-option-2.rds"))
 }
 
 test_that("Chunk options can be added.", {
-  expect_equal(ld_make_chunks(pres_list, ld),
+  expect_equal(ld_make_chunks(ld),
                readRDS(file.path("reference-data", "chunk-option-2.rds")))
 })
 
 pres_list$iris <- ld_chunk_opts(pres_list$iris, chunk_name = "iris_chunk")
 
 if (make_reference) {
-  saveRDS(ld_make_chunks(pres_list, ld),
+  saveRDS(ld_make_chunks(ld),
           file.path("reference-data", "chunk-option-3.rds"))
 }
 
 test_that("Chunk names can be added.", {
-  expect_equal(ld_make_chunks(pres_list, ld),
+  expect_equal(ld_make_chunks(ld),
                readRDS(file.path("reference-data", "chunk-option-3.rds")))
 })
 
 pres_list$iris <- ld_chunk_opts(pres_list$iris, echo = TRUE)
 
 if (make_reference) {
-  saveRDS(ld_make_chunks(pres_list, ld),
+  saveRDS(ld_make_chunks(ld),
[…]

### 2020-03-02 tests/testthat/test-make-chunks.r

@@ -31,7 +31,8 @@ test_list <- list(iris = iris,
 # If it sees a ggplot object, it does nothing. If it sees a dataframe
 # it decorates with datatable from the DT package.
 
-ld <- listdown(load_ld_expr = readRDS("a/file"),
+saveRDS(test_list, "reference-data/test_list.rds")
+ld <- listdown(load_cc_expr = readRDS("reference-data/test_list.rds"),
                package = c("ggplot2", "DT", "purrr"),
                decorator = list(ggplot = identity,
                                 data.frame = datatable),
@@ -46,16 +47,16 @@ test_that("A listdown object can be created.", {
 # Create the RMarkdown string.
 
 if (make_reference) {
-  saveRDS(ld_make_chunks(test_list, ld),
+  saveRDS(ld_make_chunks(ld),
            file.path("reference-data", "test-make-chunks-1.rds"))
 }
 
 test_that("The listdown object is the same as before.", {
-  expect_equal(ld_make_chunks(test_list, ld),
+  expect_equal(ld_make_chunks(ld),
                readRDS(file.path("reference-data", "test-make-chunks-1.rds")))
 })
 
-ld2 <- listdown(load_ld_expr = readRDS("a/file"),
+ld2 <- listdown(load_cc_expr = readRDS("reference-data/test_list.rds"),
                 package = c("ggplot2", "DT", "purrr"),
                 decorator = list(data.frame = datatable),
                 init_expr = {
@@ -72,11 +73,11 @@ test_that("A listdown object with initial expression can be created.", {
 # Create the RMarkdown string.
 
 if (make_reference) {
-  saveRDS(ld_make_chunks(test_list, ld2),
+  saveRDS(ld_make_chunks(ld2),
            file.path("reference-data", "test-make-chunks-2.rds"))
 }
 
 test_that("The listdown object with init expr is the same as before.", {
-  expect_equal(ld_make_chunks(test_list, ld2),
+  expect_equal(ld_make_chunks(ld2),
                readRDS(file.path("reference-data", "test-make-chunks-2.rds")))
 })

### 2020-03-08 README.Rmd
Vignettes and bug squashing.
Fixed a problem with README.

@@
 # Create a listdown object.
-ld <- listdown(load_ld_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
+ld <- listdown(load_cc_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
                package = "ggplot2",                     # The packges needed to render plots.
@@
 
+# Save the pres_list object so that it can be used in the R Markdown document.
+saveRDS(pres_list, "pres-list.rds")
+
 # Create a listdown object.
-ld <- listdown(load_ld_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
+ld <- listdown(load_cc_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
                package = "ggplot2",                     # The packges needed to render plots.
@@
                       date = "1973"),
-  ld_make_chunks(pres_list, ld))
+  ld_make_chunks(ld))
 
@@
 browseURL("anscombe.html")
+```
+
+```{r cleanup, echo = FALSE, warning = FALSE, error = FALSE}
+unlink("pres-list.rds")
 ```

### 2020-03-08 tests/testthat/test-make-chunks.r

@@ -10,21 +10,18 @@ if (make_reference) {
 }
 
 # The list we'll make an RMarkdown document from.
-test_list <- list(iris = iris,
-     list(Sepal.Length =
-          list(Sepal.Width = ggplot(iris,
-                                    aes(x = Sepal.Length, y = Sepal.Width)) +
-                 geom_point()),
-          list(Petal.Length = ggplot(iris,
-                                     aes(x = Sepal.Length, y = Sepal.Width))),
-          list(Colored = list(Sepal.Width = ggplot(iris,
-                                    aes(x = Sepal.Length, y = Sepal.Width,
-                                        color = Species)) +
-                                geom_point(),
-                              Petal.Length = ggplot(iris,
-                                    aes(x = Sepal.Length, y = Petal.Length,
-                                        color = Species)) +
-                                geom_point()))))
+test_list <- list(
+    iris = iris,
+     Sepal.Length = list(
+          Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) +
+            geom_point(),
+          Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) +
+            geom_point(),
+     Colored = list(
+          Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width,
+            color = Species)) + geom_point(),
+          Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Petal.Length,
+            color = Species)) + geom_point())))
 
 # The listdown object. It needs the libraries to load, the decorators,
 # and, coming soon, arbitrary code.

### 2020-03-08 R/depth-first-pres-list-visitor.r
Bugfix.

@@ -64,7 +64,7 @@ depth_first_concat <- function(cc_list, ld, heading = "#",
       pll <- paste0("cc_list", list_loc_list_string(list_loc))
       pl <- paste0("cc_list", list_loc_string(list_loc))
       pll_name <- names(eval(parse(text = pll)))
-      if (pll_name != "") {
+      if (length(pll_name) && pll_name != "") {
         ret_str <<- c(ret_str,
           sprintf(paste0(heading, " %s"), pll_name),
           "")

### 2020-03-08 inst/r-journal/listdown-article.rmd
Extra R chunk option checking.

---
title: Programmatic Generation of R Markdown Documents with \pkg{listdown}
author:
  - name: Michael Kane
    affiliation: Yale University
    address:
    - 60 College Street
    - New Haven, CT 06510, USA
    email:  michael.kane@yale.edu
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

# Background and concepts

R Markdown documents support the construction of reproducible documents by allowing authors to insert R code for data processing, exploration, analysis, table-making, and visualization directly into structured, prose documents. In the context of this document, we will refer to the R code in these documents as _computational components_ since they are generated by computational means (namely the R interpreter). The prose in these documents will be referred to as _narrative components_. They may serve to help a reader understand the background, goal, theme, and results of the paper as well as contextualizing the computational components.

R Markdown [@baumer2014] integrates the process of integrating the computational and narrative components of a document. By itself this is not novel. It was identified as "Literate Programming" by @knuth1984 and software tools, like Sweave [@leisch2002] have supported this functionality for almost two decades. R Markdown's popularity has likely been driven by two factors. The first is the relative ease with which these documents can be constructed. While it is more expressive, \LaTeX is relatively technical and requires an investment in time to become proficient. By contrast R Markdown documents are easier to create and format and, when the document is used to create \LaTeX formatting can be passed through to the underlying .tex file. The second factor driving adoption is likely its support for creating _modifiable_ documents, Microsoft Word in particular. Researchers and analysts, especially those creating applied statistical analyses, often collaborate with domain experts with less technical knowledge. In these cases, the analyst focuses on creating the computational components and narrative components related to results and interpretation. After this initial document is created, the domain expert is free to develop narrative components directly in the document without needing to go through the analyst.

Since computational components are, by definition, computationally derived objects and R Markdown is a well-defined standard it is possible to programmatically create R Markdown documents with computational components. This is the focus of this paper. However, before proceeding down this avenue, we would like to highlight two fundamental limitations to automated R Markdown document construction. First and foremost, without narrative components a document has no context. Quantitative analyses require research questions, hypotheses, reviews, interpretations, and conclusions. Computational components are necessary but not sufficient for constructing an analysis. Second, it is not possible to construct computational components for an arbitary set of distinct analyses. An analysis itself has a context and it is built with a set of assumptions and goals. Computational components are constructed for a narrow class of problems.

However, this is not to say the programmatic creation of R Markdown documents is unwarranted or not useful. In fact it has at least two appealing characteristics. The first is convenience. <FILL THIS IN - TALK ABOUT REUSE TO MOTIVATE LARGER PIPELINES>. The second is that for fixed analysis pipelines processing uniformly-formatted but domain-distinct data, automated document generation enforces uniformity across those domains being serviced. <FILL THIS IN USE MULTIPLE-HISTOLOGY THERAPY AS AN EXAMPLE>.

The \pkg{listdown} package provides functions to programmatically create R Markdown files from 
named lists. It is intended for data analysis pipelines where the presentation of the results
is separated from their creation. For this use case, a data processing (or analysis) is performed
and the results are provided in a single named list, organized heirarchically. With the list and a \pkg{listdown} object a workflowr [@blischak2019], pdf, word, or html page. List element names denote sections, subsections,
subsubsection, etc. and the list elements contain the data structure to be presented including
graphs and tables. The goal of the package is not to provide a finished, readable document. It is to provide a document with all tables and visualization that will appear (_computational_ components). This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions (_narrative_ components).

\pkg{listdown} provides a reproducible means for producing a document with specified computational components. It is most compatible with data analysis pipelines where the data format is fixed but the analyses are either being updated, which may affect narrative components including the result discussion and conclusion, or where the experiment is different, which affects all narrative components If the narrative components are not changing with the data being pushed through your analysis pipeline, then you may be better off writing the R Markdown code manually.

The package itself is relatively simple with 6 distinct methods that can be easily incorporated into existing analysis pipelines for automatically creating documents that can be used for data exploration and reviewing analysis results as well as a starting point for a more formal write up. These methods include:

\begin{itemize}
\item{\bf ld\_cc\_dendro() }{- create a dendrogram from a list of computational components}
\item{\bf ld\_chunk\_opts() }{- apply chunk options to a presentation object}
\item{\bf ld\_ioslides\_header() }{- create an ioslides presentation header}
\item{\bf ld\_make\_chunks() }{- write a listdown object to a string}
\item{\bf ld\_workflowr\_header() }{- create a worflowr header}
\item{\bf ld\_rmarkdown\_header() }{- create an R Markdown header}
\item{\bf listdown() }{- create a listdown object to create an R Markdown document}
\end{itemize}

The rest of this paper is structured as follow. The next section goes over basic usage and commentary. This section is meant to convey the basic approach used by the package and shows how to describe an output document using \pkg{listdown}, create a document, and change how the presentation of computational components can be specialized using \pkg{listdown} decorators. With the user accustomed to the package's basic usage, section 3 describes the design of the package. Section 4 goes over advanced usage of the package including adding initialization code to and outputted document as well as how to control chunk-level options. Section 5 concludes the paper with a few final remarks.

# Basic usage and overview

Suppose we have just completed and analysis and have collected all of the results into a list where the list elements are roughly in the order we would like to present them in a document. It may be noted that this is not always how computational components derived from data analyses are collated. Often individual components are stored in multiple locations on a single machine or across machines. However, it is important to realize that even for analyses on large-scale data, the digital artifact that will be presented will be relatively small. Centralizing them makes it easier to access them, since they don't need to be found in mulitple locations. Also, storing them as a list provides a hierarchical structure that translates directly to a document as we will see below.

As a first example, we will consider the a list of visualizations from the anscombe data set. The list is composed of four \pkg{ggplot2} [@wickham2016]elements (named Linear, Non Linear, Outlier Vertical, and Outlier Horizontal) each containing a scatter plot from the famous Anscome Quartet - made available in the \pkg{datasets} package [@R]. From the `computational_components` list, we would like to create a document with four sections with names corresponding to the list names, each containing their respective visualizations.

```{r}
# Use ggplot2 to create the visualizations.
library(ggplot2)

# Load the Anscombe Quartet.
data(anscombe)

# Create the ggplot objects to display.
  computational_components <- list(
    Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
    `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
    `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
    `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + geom_point())

# Save the file to disk to be read by the output R Markdown document.
saveRDS(computational_components, "comp-comp.rds")
```

## Creating a document with \pkg{listdown}

Creating a document from the `computational_components` will require two steps. First, we will create a `listdown` object that specifies how the `computational_components` object will be loaded into the document,  which libraries and code needs to be included, the options for the R chunks, and how the list elements will be presented in the output R markdown document.

```{r}
library(listdown)

ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), # The expression to load pres_list in the .Rmd.
               package = "ggplot2")                     # The packges needed to render plots.
```

The `ld` object, along with the computational components in the `comp-comp.rds` file are sufficient to to create the sections, subsections, and R chunks of a document. The only other thing requires to create the document is the header. The listdown package currently supports regular R Markdown, workflowr, and ioslides headers. A complete document can then be written to the console using the code shown below. It could easily be written to a file for rendering using the `writeLines()` function, for example.

```{r}
doc <- c(
  ld_rmarkdown_header("Anscombe's Quartet",
                     author = "Francis Anscombe",
                     date = "1973"),
  ld_make_chunks(ld))

cat(paste(doc, collapse = "\n"))
```

The `listdown()` function provides _document-wide_ R chunk options for displaying computational components. The chunk options are exactly the same as those in the R markdown document and can be used to tailor the default presentation for a variety of needs. The complete set of options can be found in the [R Markdown Reference Guide](https://rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf). As a concrete example, the code used to create present the plots could be hidden in the output document using the following code.

```{r}
ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
               package = "ggplot2",
               echo = FALSE)

cat(paste(ld_make_chunks(ld)[1:7], collapse = "\n"))
```

## Decorators

The first example is simple in part because the ggplot objects both contain the data we want to display and, at the same time, provide the mechanism for presenting them - rendering them in a graph. However, this is not always the case. The objects being stored in the list of computational components may not translate directly to the presentation in a document. In these cases a function is needed that takes the list component and returns an object to be displayed. For example, suppose that, along with showing graphs from the Anscombe Quartet, we would like to include the data themselves. We could add the data to the `computational_components` list and then create the document with:

```{r}
computational_components$Data <- anscombe
saveRDS(computational_components, "comp-comp.rds")
cat(paste(ld_make_chunks(ld)[32:36], collapse = "\n"))
```

In this case, the \pkg{listdown} package will show the entire data set as is the default specified. However, suppose we do not want to show the entire data set in the document. This is common, especially when the data set is large and requires too much vertical space in the outputted document resulting in too much or irrelevant data being shown. Instead, we would like to output to an html document where the data is shown in a datatable thereby controlling the amount of real-estate needed to present the data and, at the same time, providing the user with interactivity to sort and search the data set.

In \pkg{listdown} a function or method that implments the presentation of a computational component is referred to as a _decorator_ since if follows the classic decorator pattern described in @gamma1995. A decorator takes the element that will be presented as an argument and returns an object for presentation in the output directory. A decorator is specified using the `decorator` parameter of the `listdown()` function using a named list where the name corresponds to the type and the element correspond to the function or method that will decorate an object of that type. For example, the `anscombe` data set can be decorated with the `DT::datatable()` function [@xie2020] as:

```{r}
ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
               package = c("ggplot2", "DT"),
               decorator = list(data.frame = datatable))
cat(paste(ld_make_chunks(ld)[33:37], collapse = "\n"))
```

List names in the `decorator` argument provide a key to which a function or method is mapped. The underlying decorator resolution is implemented for a given computational component by going through decorator names sequentially to see if the component inherits from the name using the `inherits()` function. The function or method is selected from the corresponding name which the element first inherits from. This means that when customizing the presentation of objects that inherit from a common class, the more abstract classes should appear at the end of the list. This will ensure that specialized classes will be encountered first in the resolution process.

A separate argument, `default_decorator`, allows the user to specify the default decorator for an object whose type does not appear in the `decorator` list. This allows the user to specify any class name for the decorator and avoids a potential type name collision with a default decorator whose name is determined by convention. By default, this argument is set to `identity` but it can be use to not display a computational component by default if the argument is set to `NULL`.

# Design

A \pkg{listdown} object specifies the location of a list of computational components and options for presenting those components in an R Markdown document. The list is a hierarchical data structure that also provides the structure of the outputted document. A corresponding document has two sections "Iris" and "Sepal.Length". The latter has three subsections "Sepal.Width", "Petal.Length", and "Colored". The "Colored" subsection has two sub-subsections, "Sepal.Width" and "Petal.Length".
The structure can be seen using the `ld_cc_dendro()` function.

```{r}
# Create a more hierarchical list of computational components.
comp_comp2 <- list(
  Iris = iris,
  Sepal.Length = list(
    Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + geom_point(),
    Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + geom_point(),
    Colored = list(
      Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) + 
        geom_point(),
      Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) + 
        geom_point())))

# Create the dendrogram.
ld_cc_dendro(comp_comp2)
```

Both the `ld_cc_dendro()` and `ld_make_chunks()` functions work by recursively descending the computational components list depth-first. If the list containing and element has a name, it is written to the output as a section, subsection, subsubsection, etc. to a return string. If the visited list element is itself a list, then the same procedure is called on the child list through a recursive call. If the element is not a list, then it is outputted inside an R Markdown chunk in the return string using the appropropriate decorator.

# Advanced usage

Along with the basic usage, the \pkg{listdown} package supports methods to further customize the presentation. Two specific areas of customization are addressed. The first is where custom code is required either to modify decorators or even define the decorators. In this case, we would to add a small portion of code, immediately after loading required libraries. In the second case, rather than changing the R code inside of a chunk, we would like to change the options for an individual chunk. Both of these features are supported in the package and are presented below.

## Initialization code

```{r}
saveRDS(comp_comp2, "comp-comp2.rds")
ld <- listdown(load_cc_expr = readRDS("comp-comp2.rds"),
               package = c("ggplot2", "DT", "purrr"),
               decorator = list(ggplot = identity,
                                data.frame = datatable),
               init_expr = {
                 datatable <- partial(datatable,
                                      options = list(dom = 't'))
                 },
               echo = FALSE)

cat(paste(ld_make_chunks(ld)[1:13], collapse = "\n"))
```

## Controlling chunk-level options

Along with providing document-wide chunk options, it is also possible to control individual chunk options

```{r}
comp_comp2$Iris <- ld_chunk_opts(comp_comp2$Iris, echo = TRUE)
saveRDS(comp_comp2, "comp-comp2.rds")
cat(paste(ld_make_chunks(ld)[1:19], collapse = "\n"))
```
# Conclusion

\bibliography{RJreferences}

### 2020-03-08 inst/r-journal/listdown-article.tex
Extra R chunk option checking.

--- 2020-03-08 inst/r-journal/listdown-article.rmd
@@
----
-title: Programmatic Generation of R Markdown Documents with \pkg{listdown}
-author:
-  - name: Michael Kane
-    affiliation: Yale University
-    address:
-    - 60 College Street
-    - New Haven, CT 06510, USA
-    email:  michael.kane@yale.edu
-abstract: >
+% !TeX root = RJwrapper.tex
+\title{Programmatic Generation of R Markdown Documents with
+\pkg{listdown}}
+\author{by Michael Kane}
+
+\maketitle
+
+\abstract{%
 An abstract of less than 150 words.
-preamble: |
-  % Any extra LaTeX you need in the preamble
-output: rticles::rjournal_article
----
+}
 
-# Background and concepts
+\hypertarget{background-and-concepts}{%
+\section{Background and concepts}\label{background-and-concepts}}
 
-R Markdown documents support the construction of reproducible documents by allowing authors to insert R code for data processing, exploration, analysis, table-making, and visualization directly into structured, prose documents.
-In the context of this document, we will refer to the R code in these documents as _computational components_ since they are generated by computational means (namely the R interpreter).
-The prose in these documents will be referred to as _narrative components_.
-They may serve to help a reader understand the background, goal, theme, and results of the paper as well as contextualizing the computational components.
+R Markdown documents support the construction of reproducible documents
+by allowing authors to insert R code for data processing, exploration,
+analysis, table-making, and visualization directly into structured,
+prose documents. In the context of this document, we will refer to the R
+code in these documents as \emph{computational components} since they
+are generated by computational means (namely the R interpreter). The
+prose in these documents will be referred to as \emph{narrative
+components}. They may serve to help a reader understand the background,
+goal, theme, and results of the paper as well as contextualizing the
+computational components.
 
-R Markdown [@baumer2014] integrates the process of integrating the computational and narrative components of a document.
-By itself this is not novel.
-It was identified as "Literate Programming" by @knuth1984 and software tools, like Sweave [@leisch2002] have supported this functionality for almost two decades.
-R Markdown's popularity has likely been driven by two factors.
-The first is the relative ease with which these documents can be constructed.
-While it is more expressive, \LaTeX is relatively technical and requires an investment in time to become proficient.
-By contrast R Markdown documents are easier to create and format and, when the document is used to create \LaTeX formatting can be passed through to the underlying .tex file.
-The second factor driving adoption is likely its support for creating _modifiable_ documents, Microsoft Word in particular.
-Researchers and analysts, especially those creating applied statistical analyses, often collaborate with domain experts with less technical knowledge.
-In these cases, the analyst focuses on creating the computational components and narrative components related to results and interpretation.
-After this initial document is created, the domain expert is free to develop narrative components directly in the document without needing to go through the analyst.
+R Markdown \citep{baumer2014} integrates the process of integrating the
+computational and narrative components of a document. By itself this is
+not novel. It was identified as ``Literate Programming'' by
+\citet{knuth1984} and software tools, like Sweave \citep{leisch2002}
+have supported this functionality for almost two decades. R Markdown's
+popularity has likely been driven by two factors. The first is the
+relative ease with which these documents can be constructed. While it is
+more expressive, \LaTeX is relatively technical and requires an
+investment in time to become proficient. By contrast R Markdown
+documents are easier to create and format and, when the document is used
+to create \LaTeX formatting can be passed through to the underlying .tex
+file. The second factor driving adoption is likely its support for
+creating \emph{modifiable} documents, Microsoft Word in particular.
+Researchers and analysts, especially those creating applied statistical
+analyses, often collaborate with domain experts with less technical
+knowledge. In these cases, the analyst focuses on creating the
+computational components and narrative components related to results and
+interpretation. After this initial document is created, the domain
+expert is free to develop narrative components directly in the document
+without needing to go through the analyst.
 
-Since computational components are, by definition, computationally derived objects and R Markdown is a well-defined standard it is possible to programmatically create R Markdown documents with computational components.
-This is the focus of this paper.
-However, before proceeding down this avenue, we would like to highlight two fundamental limitations to automated R Markdown document construction.
-First and foremost, without narrative components a document has no context.
-Quantitative analyses require research questions, hypotheses, reviews, interpretations, and conclusions.
-Computational components are necessary but not sufficient for constructing an analysis.
-Second, it is not possible to construct computational components for an arbitary set of distinct analyses.
-An analysis itself has a context and it is built with a set of assumptions and goals.
-Computational components are constructed for a narrow class of problems.
+Since computational components are, by definition, computationally
+derived objects and R Markdown is a well-defined standard it is possible
+to programmatically create R Markdown documents with computational
+components. This is the focus of this paper. However, before proceeding
+down this avenue, we would like to highlight two fundamental limitations
+to automated R Markdown document construction. First and foremost,
+without narrative components a document has no context. Quantitative
+analyses require research questions, hypotheses, reviews,
+interpretations, and conclusions. Computational components are necessary
+but not sufficient for constructing an analysis. Second, it is not
+possible to construct computational components for an arbitary set of
+distinct analyses. An analysis itself has a context and it is built with
+a set of assumptions and goals. Computational components are constructed
+for a narrow class of problems.
 
-However, this is not to say the programmatic creation of R Markdown documents is unwarranted or not useful.
-In fact it has at least two appealing characteristics.
-The first is convenience.
-<FILL THIS IN - TALK ABOUT REUSE TO MOTIVATE LARGER PIPELINES>.
-The second is that for fixed analysis pipelines processing uniformly-formatted but domain-distinct data, automated document generation enforces uniformity across those domains being serviced.
-<FILL THIS IN USE MULTIPLE-HISTOLOGY THERAPY AS AN EXAMPLE>.
+However, this is not to say the programmatic creation of R Markdown
+documents is unwarranted or not useful. In fact it has at least two
+appealing characteristics. The first is convenience. \textless FILL THIS
+IN - TALK ABOUT REUSE TO MOTIVATE LARGER PIPELINES\textgreater. The
+second is that for fixed analysis pipelines processing
+uniformly-formatted but domain-distinct data, automated document
+generation enforces uniformity across those domains being serviced. .
 
-The \pkg{listdown} package provides functions to programmatically create R Markdown files from 
-named lists. It is intended for data analysis pipelines where the presentation of the results
-is separated from their creation. For this use case, a data processing (or analysis) is performed
-and the results are provided in a single named list, organized heirarchically.
-With the list and a \pkg{listdown} object a workflowr [@blischak2019], pdf, word, or html page.
-List element names denote sections, subsections,
-subsubsection, etc. and the list elements contain the data structure to be presented including
-graphs and tables.
-The goal of the package is not to provide a finished, readable document.
-It is to provide a document with all tables and visualization that will appear (_computational_ components).
-This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions (_narrative_ components).
+The \pkg{listdown} package provides functions to programmatically create
+R Markdown files from named lists. It is intended for data analysis
+pipelines where the presentation of the results is separated from their
+creation. For this use case, a data processing (or analysis) is
+performed and the results are provided in a single named list, organized
+heirarchically. With the list and a \pkg{listdown} object a workflowr
+\citep{blischak2019}, pdf, word, or html page. List element names denote
+sections, subsections, subsubsection, etc. and the list elements contain
+the data structure to be presented including graphs and tables. The goal
+of the package is not to provide a finished, readable document. It is to
+provide a document with all tables and visualization that will appear
+(\emph{computational} components). This serves as a starting point from
+which a user can organize outputs, describe a study, discuss results,
+and provide conclusions (\emph{narrative} components).
 
-\pkg{listdown} provides a reproducible means for producing a document with specified computational components.
-It is most compatible with data analysis pipelines where the data format is fixed but the analyses are either being updated, which may affect narrative components including the result discussion and conclusion, or where the experiment is different, which affects all narrative components If the narrative components are not changing with the data being pushed through your analysis pipeline, then you may be better off writing the R Markdown code manually.
+\pkg{listdown} provides a reproducible means for producing a document
+with specified computational components. It is most compatible with data
+analysis pipelines where the data format is fixed but the analyses are
+either being updated, which may affect narrative components including
+the result discussion and conclusion, or where the experiment is
+different, which affects all narrative components If the narrative
+components are not changing with the data being pushed through your
+analysis pipeline, then you may be better off writing the R Markdown
+code manually.
 
-The package itself is relatively simple with 6 distinct methods that can be easily incorporated into existing analysis pipelines for automatically creating documents that can be used for data exploration and reviewing analysis results as well as a starting point for a more formal write up.
-These methods include:
+The package itself is relatively simple with 6 distinct methods that can
+be easily incorporated into existing analysis pipelines for
+automatically creating documents that can be used for data exploration
+and reviewing analysis results as well as a starting point for a more
+formal write up. These methods include:
 
 \begin{itemize}
-\item{\bf ld\_cc\_dendro() }{- create a dendrogram from a list of computational components}
 \item{\bf ld\_chunk\_opts() }{- apply chunk options to a presentation object}
@@
 \item{\bf listdown() }{- create a listdown object to create an R Markdown document}
+\item{\bf to\_data\_tree() }{- create a data.tree object from a list of computational components}
 \end{itemize}
 
-The rest of this paper is structured as follow.
-The next section goes over basic usage and commentary.
-This section is meant to convey the basic approach used by the package and shows how to describe an output document using \pkg{listdown}, create a document, and change how the presentation of computational components can be specialized using \pkg{listdown} decorators.
-With the user accustomed to the package's basic usage, section 3 describes the design of the package.
-Section 4 goes over advanced usage of the package including adding initialization code to and outputted document as well as how to control chunk-level options.
-Section 5 concludes the paper with a few final remarks.
+The rest of this paper is structured as follow. The next section goes
+over basic usage and commentary. This section is meant to convey the
+basic approach used by the package and shows how to describe an output
+document using \pkg{listdown}, create a document, and change how the
+presentation of computational components can be specialized using
+\pkg{listdown} decorators. With the user accustomed to the package's
+basic usage, section 3 describes the design of the package. Section 4
+goes over advanced usage of the package including adding initialization
+code to and outputted document as well as how to control chunk-level
+options. Section 5 concludes the paper with a few final remarks.
 
-# Basic usage and overview
+\hypertarget{basic-usage-and-overview}{%
+\section{Basic usage and overview}\label{basic-usage-and-overview}}
 
-Suppose we have just completed and analysis and have collected all of the results into a list where the list elements are roughly in the order we would like to present them in a document.
-It may be noted that this is not always how computational components derived from data analyses are collated.
-Often individual components are stored in multiple locations on a single machine or across machines.
-However, it is important to realize that even for analyses on large-scale data, the digital artifact that will be presented will be relatively small.
-Centralizing them makes it easier to access them, since they don't need to be found in mulitple locations.
-Also, storing them as a list provides a hierarchical structure that translates directly to a document as we will see below.
+Suppose we have just completed and analysis and have collected all of
+the results into a list where the list elements are roughly in the order
+we would like to present them in a document. It may be noted that this
+is not always how computational components derived from data analyses
+are collated. Often individual components are stored in multiple
+locations on a single machine or across machines. However, it is
+important to realize that even for analyses on large-scale data, the
+digital artifact that will be presented will be relatively small.
+Centralizing them makes it easier to access them, since they don't need
+to be found in mulitple locations. Also, storing them as a list provides
+a hierarchical structure that translates directly to a document as we
+will see below.
 
-As a first example, we will consider the a list of visualizations from the anscombe data set.
-The list is composed of four \pkg{ggplot2} [@wickham2016]elements (named Linear, Non Linear, Outlier Vertical, and Outlier Horizontal) each containing a scatter plot from the famous Anscome Quartet - made available in the \pkg{datasets} package [@R].
-From the `computational_components` list, we would like to create a document with four sections with names corresponding to the list names, each containing their respective visualizations.
+As a first example, we will consider the a list of visualizations from
+the anscombe data set. The list is composed of four \pkg{ggplot2}
+\citep{wickham2016}elements (named Linear, Non Linear, Outlier Vertical,
+and Outlier Horizontal) each containing a scatter plot from the famous
+Anscome Quartet - made available in the \pkg{datasets} package
+\citep{R}. From the \texttt{computational\_components} list, we would
+like to create a document with four sections with names corresponding to
+the list names, each containing their respective visualizations.
 
-```{r}
+\begin{Schunk}
+\begin{Sinput}
 # Use ggplot2 to create the visualizations.
@@
 saveRDS(computational_components, "comp-comp.rds")
-```
+\end{Sinput}
+\end{Schunk}
 
-## Creating a document with \pkg{listdown}
+\hypertarget{creating-a-document-with}{%
+\subsection{\texorpdfstring{Creating a document with
+\pkg{listdown}}{Creating a document with }}\label{creating-a-document-with}}
 
-Creating a document from the `computational_components` will require two steps.
-First, we will create a `listdown` object that specifies how the `computational_components` object will be loaded into the document,  which libraries and code needs to be included, the options for the R chunks, and how the list elements will be presented in the output R markdown document.
+Creating a document from the \texttt{computational\_components} will
+require two steps. First, we will create a \texttt{listdown} object that
+specifies how the \texttt{computational\_components} object will be
+loaded into the document, which libraries and code needs to be included,
+the options for the R chunks, and how the list elements will be
+presented in the output R markdown document.
 
-```{r}
+\begin{Schunk}
+\begin{Sinput}
 library(listdown)
@@
                package = "ggplot2")                     # The packges needed to render plots.
-```
+\end{Sinput}
+\end{Schunk}
 
-The `ld` object, along with the computational components in the `comp-comp.rds` file are sufficient to to create the sections, subsections, and R chunks of a document.
-The only other thing requires to create the document is the header.
-The listdown package currently supports regular R Markdown, workflowr, and ioslides headers.
-A complete document can then be written to the console using the code shown below.
-It could easily be written to a file for rendering using the `writeLines()` function, for example.
+The \texttt{ld} object, along with the computational components in the
+\texttt{comp-comp.rds} file are sufficient to to create the sections,
+subsections, and R chunks of a document. The only other thing requires
+to create the document is the header. The listdown package currently
+supports regular R Markdown, workflowr, and ioslides headers. A complete
+document can then be written to the console using the code shown below.
+It could easily be written to a file for rendering using the
+\texttt{writeLines()} function, for example.
 
-```{r}
+\begin{Schunk}
+\begin{Sinput}
 doc <- c(
@@
 cat(paste(doc, collapse = "\n"))
-```
+\end{Sinput}
+\begin{Soutput}
+#> ---
+#> title: "Anscombe's Quartet"
+#> author: "Francis Anscombe"
+#> date: "1973"
+#> output: html_document
+#> ---
+#> 
+#> ```{r}
+#> library(ggplot2)
+#> 
+#> cc_list <- readRDS("comp-comp.rds")
+#> ```
+#> 
+#> # Linear
+#> 
+#> ```{r}
+#> identity(cc_list[[1]])
+#> ```
+#> 
+#> # Non Linear
+#> 
+#> ```{r}
+#> identity(cc_list[[2]])
+#> ```
+#> 
+#> # Outlier Vertical
+#> 
+#> ```{r}
+#> identity(cc_list[[3]])
+#> ```
+#> 
+#> # Outlier Horizontal
+#> 
+#> ```{r}
+#> identity(cc_list[[4]])
+#> ```
+\end{Soutput}
+\end{Schunk}
 
-The `listdown()` function provides _document-wide_ R chunk options for displaying computational components.
-The chunk options are exactly the same as those in the R markdown document and can be used to tailor the default presentation for a variety of needs.
-The complete set of options can be found in the [R Markdown Reference Guide](https://rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf).
-As a concrete example, the code used to create present the plots could be hidden in the output document using the following code.
+The \texttt{listdown()} function provides \emph{document-wide} R chunk
+options for displaying computational components. The chunk options are
+exactly the same as those in the R markdown document and can be used to
+tailor the default presentation for a variety of needs. The complete set
+of options can be found in the
+\href{https://rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf}{R
+Markdown Reference Guide}. As a concrete example, the code used to
+create present the plots could be hidden in the output document using
+the following code.
 
-```{r}
+\begin{Schunk}
+\begin{Sinput}
 ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
@@
 cat(paste(ld_make_chunks(ld)[1:7], collapse = "\n"))
-```
+\end{Sinput}
+\begin{Soutput}
+#> 
+#> ```{r echo=FALSE}
+#> library(ggplot2)
+#> 
+#> cc_list <- readRDS("comp-comp.rds")
+#> ```
+\end{Soutput}
+\end{Schunk}
 
-## Decorators
+\hypertarget{decorators}{%
+\subsection{Decorators}\label{decorators}}
 
-The first example is simple in part because the ggplot objects both contain the data we want to display and, at the same time, provide the mechanism for presenting them - rendering them in a graph.
-However, this is not always the case.
-The objects being stored in the list of computational components may not translate directly to the presentation in a document.
-In these cases a function is needed that takes the list component and returns an object to be displayed.
-For example, suppose that, along with showing graphs from the Anscombe Quartet, we would like to include the data themselves.
-We could add the data to the `computational_components` list and then create the document with:
+The first example is simple in part because the ggplot objects both
+contain the data we want to display and, at the same time, provide the
+mechanism for presenting them - rendering them in a graph. However, this
+is not always the case. The objects being stored in the list of
+computational components may not translate directly to the presentation
+in a document. In these cases a function is needed that takes the list
+component and returns an object to be displayed. For example, suppose
+that, along with showing graphs from the Anscombe Quartet, we would like
+to include the data themselves. We could add the data to the
+\texttt{computational\_components} list and then create the document
+with:
 
-```{r}
+\begin{Schunk}
+\begin{Sinput}
 computational_components$Data <- anscombe
@@
 cat(paste(ld_make_chunks(ld)[32:36], collapse = "\n"))
-```
+\end{Sinput}
+\begin{Soutput}
+#> # Data
+#> 
+#> ```{r echo=FALSE}
+#> identity(cc_list[[5]])
+#> ```
+\end{Soutput}
+\end{Schunk}
 
-In this case, the \pkg{listdown} package will show the entire data set as is the default specified.
-However, suppose we do not want to show the entire data set in the document.
-This is common, especially when the data set is large and requires too much vertical space in the outputted document resulting in too much or irrelevant data being shown.
-Instead, we would like to output to an html document where the data is shown in a datatable thereby controlling the amount of real-estate needed to present the data and, at the same time, providing the user with interactivity to sort and search the data set.
+In this case, the \pkg{listdown} package will show the entire data set
+as is the default specified. However, suppose we do not want to show the
+entire data set in the document. This is common, especially when the
+data set is large and requires too much vertical space in the outputted
+document resulting in too much or irrelevant data being shown. Instead,
+we would like to output to an html document where the data is shown in a
+datatable thereby controlling the amount of real-estate needed to
+present the data and, at the same time, providing the user with
+interactivity to sort and search the data set.
 
-In \pkg{listdown} a function or method that implments the presentation of a computational component is referred to as a _decorator_ since if follows the classic decorator pattern described in @gamma1995.
-A decorator takes the element that will be presented as an argument and returns an object for presentation in the output directory.
-A decorator is specified using the `decorator` parameter of the `listdown()` function using a named list where the name corresponds to the type and the element correspond to the function or method that will decorate an object of that type.
-For example, the `anscombe` data set can be decorated with the `DT::datatable()` function [@xie2020] as:
+In \pkg{listdown} a function or method that implments the presentation
+of a computational component is referred to as a \emph{decorator} since
+if follows the classic decorator pattern described in \citet{gamma1995}.
+A decorator takes the element that will be presented as an argument and
+returns an object for presentation in the output directory. A decorator
+is specified using the \texttt{decorator} parameter of the
+\texttt{listdown()} function using a named list where the name
+corresponds to the type and the element correspond to the function or
+method that will decorate an object of that type. For example, the
+\texttt{anscombe} data set can be decorated with the
+\texttt{DT::datatable()} function \citep{xie2020} as:
 
-```{r}
+\begin{Schunk}
+\begin{Sinput}
 ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
@@
 cat(paste(ld_make_chunks(ld)[33:37], collapse = "\n"))
-```
+\end{Sinput}
+\begin{Soutput}
+#> # Data
+#> 
+#> ```{r}
+#> datatable(cc_list[[5]])
+#> ```
+\end{Soutput}
+\end{Schunk}
 
-List names in the `decorator` argument provide a key to which a function or method is mapped.
-The underlying decorator resolution is implemented for a given computational component by going through decorator names sequentially to see if the component inherits from the name using the `inherits()` function.
-The function or method is selected from the corresponding name which the element first inherits from.
-This means that when customizing the presentation of objects that inherit from a common class, the more abstract classes should appear at the end of the list.
-This will ensure that specialized classes will be encountered first in the resolution process.
+List names in the \texttt{decorator} argument provide a key to which a
+function or method is mapped. The underlying decorator resolution is
+implemented for a given computational component by going through
+decorator names sequentially to see if the component inherits from the
+name using the \texttt{inherits()} function. The function or method is
+selected from the corresponding name which the element first inherits
+from. This means that when customizing the presentation of objects that
+inherit from a common class, the more abstract classes should appear at
+the end of the list. This will ensure that specialized classes will be
+encountered first in the resolution process.
 
-A separate argument, `default_decorator`, allows the user to specify the default decorator for an object whose type does not appear in the `decorator` list.
-This allows the user to specify any class name for the decorator and avoids a potential type name collision with a default decorator whose name is determined by convention.
-By default, this argument is set to `identity` but it can be use to not display a computational component by default if the argument is set to `NULL`.
+A separate argument, \texttt{default\_decorator}, allows the user to
+specify the default decorator for an object whose type does not appear
+in the \texttt{decorator} list. This allows the user to specify any
+class name for the decorator and avoids a potential type name collision
+with a default decorator whose name is determined by convention. By
+default, this argument is set to \texttt{identity} but it can be use to
+not display a computational component by default if the argument is set
+to \texttt{NULL}.
 
-# Design
+\hypertarget{design}{%
+\section{Design}\label{design}}
 
-A \pkg{listdown} object specifies the location of a list of computational components and options for presenting those components in an R Markdown document.
-The list is a hierarchical data structure that also provides the structure of the outputted document.
-A corresponding document has two sections "Iris" and "Sepal.Length".
-The latter has three subsections "Sepal.Width", "Petal.Length", and "Colored".
-The "Colored" subsection has two sub-subsections, "Sepal.Width" and "Petal.Length".
-The structure can be seen using the `ld_cc_dendro()` function.
+A \pkg{listdown} object specifies the location of a list of
+computational components and options for presenting those components in
+an R Markdown document. The list is a hierarchical data structure that
+also provides the structure of the outputted document. A corresponding
+document has two sections ``Iris'' and ``Sepal.Length''. The latter has
+three subsections ``Sepal.Width'', ``Petal.Length'', and ``Colored''.
+The ``Colored'' subsection has two sub-subsections, ``Sepal.Width'' and
+``Petal.Length''. The structure can be seen using the
+\texttt{ld\_cc\_dendro()} function.
 
-```{r}
+\begin{Schunk}
+\begin{Sinput}
 # Create a more hierarchical list of computational components.
@@
 ld_cc_dendro(comp_comp2)
-```
+\end{Sinput}
+\begin{Soutput}
+#> 
+#>  comp_comp2
+#>   |-- Iris
+#>   |  °-- object of type(s):data.frame
+#>   °-- Sepal.Length
+#>    |-- Sepal.Width
+#>    |  °-- object of type(s):gg ggplot
+#>    |-- Petal.Length
+#>    |  °-- object of type(s):gg ggplot
+#>    °-- Colored
+#>     |-- Sepal.Width
+#>     |  °-- object of type(s):gg ggplot
+#>     °-- Petal.Length
+#>        °-- object of type(s):gg ggplot 
+#> 
+\end{Soutput}
+\end{Schunk}
 
-Both the `ld_cc_dendro()` and `ld_make_chunks()` functions work by recursively descending the computational components list depth-first.
-If the list containing and element has a name, it is written to the output as a section, subsection, subsubsection, etc.
-to a return string.
-If the visited list element is itself a list, then the same procedure is called on the child list through a recursive call.
-If the element is not a list, then it is outputted inside an R Markdown chunk in the return string using the appropropriate decorator.
+Both the \texttt{ld\_cc\_dendro()} and \texttt{ld\_make\_chunks()}
+functions work by recursively descending the computational components
+list depth-first. If the list containing and element has a name, it is
+written to the output as a section, subsection, subsubsection, etc. to a
+return string. If the visited list element is itself a list, then the
+same procedure is called on the child list through a recursive call. If
+the element is not a list, then it is outputted inside an R Markdown
+chunk in the return string using the appropropriate decorator.
 
-# Advanced usage
+\hypertarget{advanced-usage}{%
+\section{Advanced usage}\label{advanced-usage}}
 
-Along with the basic usage, the \pkg{listdown} package supports methods to further customize the presentation.
-Two specific areas of customization are addressed.
-The first is where custom code is required either to modify decorators or even define the decorators.
-In this case, we would to add a small portion of code, immediately after loading required libraries.
-In the second case, rather than changing the R code inside of a chunk, we would like to change the options for an individual chunk.
-Both of these features are supported in the package and are presented below.
+Along with the basic usage, the \pkg{listdown} package supports methods
+to further customize the presentation. Two specific areas of
+customization are addressed. The first is where custom code is required
+either to modify decorators or even define the decorators. In this case,
+we would to add a small portion of code, immediately after loading
+required libraries. In the second case, rather than changing the R code
+inside of a chunk, we would like to change the options for an individual
+chunk. Both of these features are supported in the package and are
+presented below.
 
-## Initialization code
+\hypertarget{initialization-code}{%
+\subsection{Initialization code}\label{initialization-code}}
 
-```{r}
+\begin{Schunk}
+\begin{Sinput}
 saveRDS(comp_comp2, "comp-comp2.rds")
@@
 cat(paste(ld_make_chunks(ld)[1:13], collapse = "\n"))
-```
+\end{Sinput}
+\begin{Soutput}
+#> 
+#> ```{r echo=FALSE}
+#> library(ggplot2)
+#> library(DT)
+#> library(purrr)
+#> 
+#> cc_list <- readRDS("comp-comp2.rds")
+#> ```
+#> 
+#> ```{r echo=FALSE}
+#> datatable <- partial(datatable, options = list(dom = "t"))
+#> ```
+\end{Soutput}
+\end{Schunk}
 
-## Controlling chunk-level options
+\hypertarget{controlling-chunk-level-options}{%
+\subsection{Controlling chunk-level
+options}\label{controlling-chunk-level-options}}
 
-Along with providing document-wide chunk options, it is also possible to control individual chunk options
+Along with providing document-wide chunk options, it is also possible to
+control individual chunk options
 
-```{r}
+\begin{Schunk}
+\begin{Sinput}
 comp_comp2$Iris <- ld_chunk_opts(comp_comp2$Iris, echo = TRUE)
@@
 cat(paste(ld_make_chunks(ld)[1:19], collapse = "\n"))
-```
-# Conclusion
+\end{Sinput}
+\begin{Soutput}
+#> 
+#> ```{r echo=FALSE}
+#> library(ggplot2)
+#> library(DT)
+#> library(purrr)
+#> 
+#> cc_list <- readRDS("comp-comp2.rds")
+#> ```
+#> 
+#> ```{r echo=FALSE}
+#> datatable <- partial(datatable, options = list(dom = "t"))
+#> ```
+#> 
+#> # Iris
+#> 
+#> ```{r echo = TRUE}
+#> datatable(cc_list[[1]])
+#> ```
+\end{Soutput}
+\end{Schunk}
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
 \bibliography{RJreferences}
+
+\address{%
+Michael Kane\\
+Yale University\\
+60 College Street\\ New Haven, CT 06510, USA\\
+}
+\href{mailto:michael.kane@yale.edu}{\nolinkurl{michael.kane@yale.edu}}

### 2020-03-08 R/cc-dendro.r

@@ -1,0 +1,55 @@
+
+#' @title Show the list of Computational Components as a Dendrogram
+#' 
+#' @description This function creates text dendrograms from 
+#' a list of computational components. It is useful for
+#' creating a dendrogram of the the computational components of a listdown
+#' object allowing the user to view the components hierarchically.
+#' @importFrom crayon red
+#' @param x a possibly named list of computational components
+#' @examples
+#' library(ggplot2)
+#' 
+#' cc_list <- list(
+#'   Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+#'  `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
+#'  `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
+#'  `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + 
+#'    geom_point())
+#'
+#' ld_cc_dendro(cc_list)
+#' @export
+ld_cc_dendro <- function(x) {
+  if (!is.list(x)) {
+    stop(red("Argument should be a list type."))
+  }
+
+  tdt_impl <- function(x, prefix_string) {
+    for (i in seq_along(x)) {
+      list_name <- names(x[i])
+      if (is.null(list_name)) {
+        list_name <- '""'
+      }
+      vert_sep <- ifelse(i == length(x), " o-- ", " |-- ")
+      tree_str <<- c(tree_str, paste0(prefix_string, vert_sep, list_name))
+      if (!class(x[[i]])[1] == "list") {
+        in_sep <- ifelse(i == length(x), "  ", " |")
+        tree_str <<- c(tree_str, 
+                       paste0(prefix_string, in_sep, "  o-- ",
+                             "object of type(s):", 
+                             paste0(class(x[[i]]), collapse = " ")))
+      } else {
+        tdt_impl(x[[i]], paste0(prefix_string, " "))
+      }
+    }
+  }
+  tree_str <- as.character(as.list(match.call())$x)
+  tdt_impl(x, " ")
+  class(tree_str) <- "ld_cc_dendro"
+  tree_str
+}
+
+#' @export
+print.ld_cc_dendro <- function(x, ...) {
+  cat("\n", paste(x, collapse = "\n"), "\n", "\n")
+}

### 2020-03-08 R/chunk-options.r

@@ -57,6 +57,10 @@ chunk_option_list <- c(
   "sanitize"
   )
 
+opt_not_r_chunk <- function(x) {
+  x[!(vapply(x, function(opt) opt %in% chunk_option_list, FALSE))]
+}
+
 #' @title Apply Chunk Options to a Presentation Object
 #' @description This function allows the user to set chunk options for 
 #' individual elements of a presentation list.
@@ -71,6 +75,12 @@ chunk_option_list <- c(
 ld_chunk_opts <- function(pres_obj, chunk_name = NULL, ..., arg_list = NULL) {
   a <- attributes(pres_obj)
   dots <- list(...)
+  not_r_chunk_opts <- opt_not_r_chunk(names(dots))
+  if (length(not_r_chunk_opts) > 0) {
+    stop(red("Unrecognized options:\n\t",
+             paste(not_r_chunk_opts, collapse = "\n\t"),
+             "\n", sep = ""))
+  }
   if (length(dots) > 0) {
     for (i in seq_along(dots)) {
       val <- dots[[i]]

### 2020-03-08 R/chunk-writer.r

@@ -17,6 +17,7 @@
 #' this is identity, meaning that the elements will be passed directly 
 #' (through the identity() function).
 #' @param ... default options sent to the chunks of the outputted document.
+#' @importFrom crayon red
 #' @export
 listdown <- function(load_cc_expr,
                      package = NULL,
@@ -30,12 +31,20 @@ listdown <- function(load_cc_expr,
   } else {
     default_decorator = as.list(match.call()$default_decorator)
   }
+  dots <- list(...)
+  not_r_chunk_opts <- opt_not_r_chunk(names(dots))
+  if (length(not_r_chunk_opts) > 0) {
+    stop(red("Unrecognized options:\n\t",
+             paste(not_r_chunk_opts, collapse = "\n\t"),
+             "\n", sep = ""))
+  }
   ret <- list(load_cc_expr = match.call()$load_cc_expr,
               decorator = as.list(match.call()$decorator)[-1],
               package = package,
               init_expr = match.call()$init_expr,
               default_decorator = default_decorator,
-              dots = list(...))
+              dots = dots)
+
   class(ret) <- "listdown"
   ret
 }

### 2020-03-08 tests/testthat/test-add-chunk-option.r

@@ -67,6 +67,10 @@ test_that("Chunks can have names and options.", {
                readRDS(file.path("reference-data", "chunk-option-4.rds")))
 })
 
+test_that("Bad options can't be added.", {
+  expect_error(ld_chunk_opts(pres_list$iris, no_way_jose = FALSE))
+})
+
 test_that("Options can be NULL", {
   plt <- ld_chunk_opts(pres_list$iris, results = NULL)
   expect_equal(attributes(plt)$listdown$results, "NULL")

### 2020-03-08 tests/testthat/test-chunk-opts.r

@@ -1,0 +1,16 @@
+
+context("Chunk Options")
+
+library(knitr)
+
+ld <- listdown(readRDS("reference-data/option-check.rds"),
+               package = "knitr",
+               decorator = list(data.frame = kable))
+
+test_that("Bad chunk options fail.", {
+  expect_error(listdown(readRDS("reference-data/option-check.rds"),
+               package = "knitr",
+               decorators = list(data.frame = kable),
+               bunk = letters))
+})
+

### 2020-04-28 inst/r-journal/listdown-article.rmd
Major bigtime revision.

@@
 Computational components are necessary but not sufficient for constructing an analysis.
-Second, it is not possible to construct computational components for an arbitary set of distinct analyses.
-An analysis itself has a context and it is built with a set of assumptions and goals.
+Second, it is not possible to construct computational components for an arbitary analyses.
+Analyses themselves have context and are built with a set of assumptions and goals.
 Computational components are constructed for a narrow class of problems.
@@
 However, this is not to say the programmatic creation of R Markdown documents is unwarranted or not useful.
-In fact it has at least two appealing characteristics.
-The first is convenience.
-<FILL THIS IN - TALK ABOUT REUSE TO MOTIVATE LARGER PIPELINES>.
-The second is that for fixed analysis pipelines processing uniformly-formatted but domain-distinct data, automated document generation enforces uniformity across those domains being serviced.
-<FILL THIS IN USE MULTIPLE-HISTOLOGY THERAPY AS AN EXAMPLE>.
+In fact, it has at least two appealing characteristics.
+The first is that it allows us to distinguish the presentation of analytical results from other steps in a data science or data processing pipeline.
+These other steps including cleaning and analysis often require their own environment and configuration with requirements very different than the computational needs of creating a presentation.
+By separating these components each can be developed independently.
+At the same time, by specifying that the output of those objects are organized hierarchically, we are essentially creating a contract by which processed data can be passed to the presentation as well as providing a way to organize the results.
+The second reason for programmatic creation of R Markdown documents is convenience.
+In collaborative environments, especially in the early stages, large numbers of graphs and tables are generated and discussed.
+By collecting these artifacts hierarchicaly as a list, they can be quickly iterated upon and restructured to more clearly present the data without needing to spend time on the creation of the presentation document.
 
@@
 and the results are provided in a single named list, organized heirarchically.
-With the list and a \pkg{listdown} object a workflowr [@blischak2019], pdf, word, or html page.
+With the list and a \pkg{listdown} object a \pkg{workflowr} [@blischak2019], pdf, word, or html page.
 List element names denote sections, subsections,
@@
 
-The package itself is relatively simple with 6 distinct methods that can be easily incorporated into existing analysis pipelines for automatically creating documents that can be used for data exploration and reviewing analysis results as well as a starting point for a more formal write up.
+One area where we have found \pkg{listdown} is particuarly useful is in the reporting and research of clinical trial data.
+These collaborations tend to be between (bio)statisticians and clinicians either analyzing past trial data to formulate a new trial or in trial monitoring where trial telemetry (enrollment, responses, etc.) is reported and initial analyses are conveyed to a clinician.
+The associated presentations require very little context - clinicians often have a better understanding of the data collected than the statistician - often eliminating the need for narrative components.
+At the same time, a large number of hierarchical, heterogenous artifacts (tables and multiple types of plots) need to be conveyed thereby making the manual creation of R Markdown documents inconvenient.
+
+Furthermore, data processing can be fixed across trials.
+This is especially true in the initial stages, which focus on patient demographics and enrollment.
+This has made it convenient for our group to quickly generate standardize and complete reports for multiple trials concurrently.
+To date, we have used listdown to report on five clinical trials, with another two currently in process.
+Results are disseminated using the \pkg{workflowr} package, usually with nine tabs conveying aspects of the data from collection through several different analyses, and each tab containing approxiately five to thirty tables, plots, or other artifacts including \pkg{trelliscopejs} [@trelliscopejs] environments which may hold hundreds of graphs.
+By generating many presentation artifacts we are able to address data-drive questions and issues during collaborative sessions and by carefully structuring these elements we allowing all members to participate in the process.
+
+The \pkg{listdown} package itself is relatively simple with 6 distinct methods that can be easily incorporated into existing analysis pipelines for automatically creating documents that can be used for data exploration and reviewing analysis results as well as a starting point for a more formal write up.
 These methods include:
@@
 \begin{itemize}
+\item{\bf as\_ld\_yml() }{- turn a computational component list into YAML with class information}
 \item{\bf ld\_cc\_dendro() }{- create a dendrogram from a list of computational components}
@@
 \item{\bf ld\_make\_chunks() }{- write a listdown object to a string}
+\item{\bf ld\_rmarkdown\_header() }{- create an R Markdown header}
 \item{\bf ld\_workflowr\_header() }{- create a worflowr header}
-\item{\bf ld\_rmarkdown\_header() }{- create an R Markdown header}
 \item{\bf listdown() }{- create a listdown object to create an R Markdown document}
@@
 Often individual components are stored in multiple locations on a single machine or across machines.
-However, it is important to realize that even for analyses on large-scale data, the digital artifact that will be presented will be relatively small.
+However, it is important to realize that even for analyses on large-scale data, the digital artifacts to be presented are relatively small.
 Centralizing them makes it easier to access them, since they don't need to be found in mulitple locations.
@@
 Creating a document from the `computational_components` will require two steps.
-First, we will create a `listdown` object that specifies how the `computational_components` object will be loaded into the document,  which libraries and code needs to be included, the options for the R chunks, and how the list elements will be presented in the output R markdown document.
+First, we will create a `listdown` object that specifies how the `computational_components` object will be loaded into the document,  which libraries and code needs to be included, and how the list elements will be presented in the output R markdown document.
 
@@
 
-ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), # The expression to load pres_list in the .Rmd.
-               package = "ggplot2")                     # The packges needed to render plots.
+ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"),
+               package = "ggplot2")
 ```
@@
 The only other thing requires to create the document is the header.
-The listdown package currently supports regular R Markdown, workflowr, and ioslides headers.
+The listdown package currently supports regular R Markdown and \pkg{workflowr} as \code{yml} objects from the \pkg{yaml} package [@yaml].
+These objects are stored as named lists in R and are easily modified to accomodate document parameters.
 A complete document can then be written to the console using the code shown below.
-It could easily be written to a file for rendering using the `writeLines()` function, for example.
+It could easily be written to a file for rendering using the `writeLines()` as in the following example.
 
@@
 doc <- c(
+  as.character(
     ld_rmarkdown_header("Anscombe's Quartet",
                         author = "Francis Anscombe",
-                     date = "1973"),
+                        date = "1973")),
   ld_make_chunks(ld))
@@
 The objects being stored in the list of computational components may not translate directly to the presentation in a document.
-In these cases a function is needed that takes the list component and returns an object to be displayed.
+In these cases, a function is needed that takes the list component and returns an object to be displayed.
 For example, suppose that, along with showing graphs from the Anscombe Quartet, we would like to include the data themselves.
@@
 
-In \pkg{listdown} a function or method that implments the presentation of a computational component is referred to as a _decorator_ since if follows the classic decorator pattern described in @gamma1995.
+In \pkg{listdown}, a function or method that implements the presentation of a computational component is referred to as a _decorator_ since if follows the classic decorator pattern described in @gamma1995.
 A decorator takes the element that will be presented as an argument and returns an object for presentation in the output directory.
@@
 This will ensure that specialized classes will be encountered first in the resolution process.
+It should be noted that an object's type is first checked against the decorator name list and then checked to see if it is a list.
+This allows a user to both decorate a list and retain `"list"` in its class attributes.
 
@@
 
-# Advanced usage
+# R code chunk customization
 
-Along with the basic usage, the \pkg{listdown} package supports methods to further customize the presentation.
-Two specific areas of customization are addressed.
-The first is where custom code is required either to modify decorators or even define the decorators.
+Along with the basic usage, the \pkg{listdown} package supports two other capabilities to further customize the presentation.
+The first is where custom code is required either to modify decorators or even define a decorators.
 In this case, we would to add a small portion of code, immediately after loading required libraries.
@@
 
+The `listdown()` function facilitates the insertion of initialization code through the `init_expr` argument.
+Code is inserted immediately after the libraries are loaded in the R Markdown document.
+In general, it is suggested that the number of initial expressions be kept small so that the R Markdown document is easy to read.
+If a large number of functions are required by the target R Markdown document then they can be put into a file and sourced using the initial expression.
+As an example, suppose we are creating an html document and presenting data using the `datatable()` function.
+However, we do not want to include the search capabilities provided.
+This can be easily accomplished by creating a new function, `datatable_no_search()`, created using the `partial()` function \cite{purrr} to partially apply `list(dom = 't')` to the `options` argument of `datatable`.
+
 ```{r}
@@
                decorator = list(ggplot = identity,
-                                data.frame = datatable),
+                                data.frame = datatable_no_search),
                init_expr = {
-                 datatable <- partial(datatable,
+                 datatable_no_search <- partial(datatable,
                                                 options = list(dom = 't'))
@@
 ```
-# Conclusion
+
+# A simple example: Reporting on the `gtsummary::trial` dataset
+
+\label{sect:simple-example}
+
+```{r, eval = FALSE}
+library(gtsummary)
+library(dplyr)
+library(glue)
+library(survival)
+library(survminer)
+library(rmarkdown)
+
+# Function to create the computational components.
+make_surv_cc <- function(trial, treat, surv_cond_chars) {
+  # Create Table 1 by treatment
+  table_1 <- trial %>%
+    tbl_summary(by = all_of(treat)) %>%
+    gtsummary::as_flextable()
+
+  # Create survival plots base on survival characteristics
+  scs <- lapply(c("1", surv_cond_chars),
+                function(sc) {
+                  glue("Surv(ttdeath, death) ~ {treat} + {sc}") %>%
+                    as.formula() %>%
+                    surv_fit(trial) %>%
+                    ggsurvplot()
+                })
+  names(scs) <- c("Overall", tools::toTitleCase(surv_cond_chars))
+  list(`Table 1` = table_1, `Survival Plots` = scs)
+}
+
+# Create the computational components and write to surv-cc.rds.
+make_surv_cc(trial, treat = "trt",
+             surv_cond_chars = c("stage", "grade")) %>%
+  saveRDS("surv-cc.rds")
+
+# Create the listdown object with appropriate dependencies
+# and presentation parameters.
+ld_surv <- listdown(load_cc_expr = readRDS("surv-cc.rds"),
+                    package = c("gtsummary", "survminer"),
+                    decorator = list(ggsurvplot = identity,
+                                     tbl_summary = identity),
+                    echo = FALSE,
+                    message = FALSE,
+                    warning = FALSE,
+                    fig.width = 7,
+                    fig.height = 4.5)
+
+# Write an RMarkdown header and chunks derived from the 
+# computational components and listdown object to trial-report.rmd.
+writeLines(
+  paste(c(
+    as.character(ld_rmarkdown_header("Simple Trial Report")),
+    ld_make_chunks(ld_surv))),
+  "trial-report.rmd")
+
+# Render the RMarkdown file to html.
+render("trial-report.rmd", quiet = TRUE, pdf_document(keep_tex = TRUE))  
+```
+
+# Using \pkg{listdown} in practice for clinical trial reporting
+
+\pagebreak
+
+# Appendix 1: RMarkdown produced in the simple example
+
+```{r eval = FALSE}
+---
+title: Simple Trial Report
+output: html_document
+---
+
+\```{r echo=FALSE}
+library(gtsummary)
+library(survminer)
+
+cc_list <- readRDS("surv-cc.rds")
+\```
+
+# Table 1
+
+\```{r echo=FALSE}
+cc_list$`Table 1`
+\```
+
+# Survival Plots
+
+## Overall
+
+\```{r echo=FALSE}
+cc_list$`Survival Plots`$Overall
+\```
+
+## Stage
+
+\```{r echo=FALSE}
+cc_list$`Survival Plots`$Stage
+\```
+
+## Grade
+
+\```{r echo=FALSE}
+cc_list$`Survival Plots`$Grade
+\```
+```
+
+\pagebreak
+
+# Appendix 2: The document produced by the simple example
 

### 2020-04-28 inst/r-journal/listdown-article.tex
Major bigtime revision.

@@
 but not sufficient for constructing an analysis. Second, it is not
-possible to construct computational components for an arbitary set of
-distinct analyses. An analysis itself has a context and it is built with
-a set of assumptions and goals. Computational components are constructed
-for a narrow class of problems.
+possible to construct computational components for an arbitary analyses.
+Analyses themselves have context and are built with a set of assumptions
+and goals. Computational components are constructed for a narrow class
+of problems.
 
 However, this is not to say the programmatic creation of R Markdown
-documents is unwarranted or not useful. In fact it has at least two
-appealing characteristics. The first is convenience. \textless FILL THIS
-IN - TALK ABOUT REUSE TO MOTIVATE LARGER PIPELINES\textgreater. The
-second is that for fixed analysis pipelines processing
-uniformly-formatted but domain-distinct data, automated document
-generation enforces uniformity across those domains being serviced. .
+documents is unwarranted or not useful. In fact, it has at least two
+appealing characteristics. The first is that it allows us to distinguish
+the presentation of analytical results from other steps in a data
+science or data processing pipeline. These other steps including
+cleaning and analysis often require their own environment and
+configuration with requirements very different than the computational
+needs of creating a presentation. By separating these components each
+can be developed independently. At the same time, by specifying that the
+output of those objects are organized hierarchically, we are essentially
+creating a contract by which processed data can be passed to the
+presentation as well as providing a way to organize the results. The
+second reason for programmatic creation of R Markdown documents is
+convenience. In collaborative environments, especially in the early
+stages, large numbers of graphs and tables are generated and discussed.
+By collecting these artifacts hierarchicaly as a list, they can be
+quickly iterated upon and restructured to more clearly present the data
+without needing to spend time on the creation of the presentation
+document.
 
@@
 performed and the results are provided in a single named list, organized
-heirarchically. With the list and a \pkg{listdown} object a workflowr
-\citep{blischak2019}, pdf, word, or html page. List element names denote
-sections, subsections, subsubsection, etc. and the list elements contain
-the data structure to be presented including graphs and tables. The goal
-of the package is not to provide a finished, readable document. It is to
-provide a document with all tables and visualization that will appear
-(\emph{computational} components). This serves as a starting point from
-which a user can organize outputs, describe a study, discuss results,
-and provide conclusions (\emph{narrative} components).
+heirarchically. With the list and a \pkg{listdown} object a
+\pkg{workflowr} \citep{blischak2019}, pdf, word, or html page. List
+element names denote sections, subsections, subsubsection, etc. and the
+list elements contain the data structure to be presented including
+graphs and tables. The goal of the package is not to provide a finished,
+readable document. It is to provide a document with all tables and
+visualization that will appear (\emph{computational} components). This
+serves as a starting point from which a user can organize outputs,
+describe a study, discuss results, and provide conclusions
+(\emph{narrative} components).
 
@@
 
-The package itself is relatively simple with 6 distinct methods that can
-be easily incorporated into existing analysis pipelines for
-automatically creating documents that can be used for data exploration
-and reviewing analysis results as well as a starting point for a more
-formal write up. These methods include:
+One area where we have found \pkg{listdown} is particuarly useful is in
+the reporting and research of clinical trial data. These collaborations
+tend to be between (bio)statisticians and clinicians either analyzing
+past trial data to formulate a new trial or in trial monitoring where
+trial telemetry (enrollment, responses, etc.) is reported and initial
+analyses are conveyed to a clinician. The associated presentations
+require very little context - clinicians often have a better
+understanding of the data collected than the statistician - often
+eliminating the need for narrative components. At the same time, a large
+number of hierarchical, heterogenous artifacts (tables and multiple
+types of plots) need to be conveyed thereby making the manual creation
+of R Markdown documents inconvenient.
+
+Furthermore, data processing can be fixed across trials. This is
+especially true in the initial stages, which focus on patient
+demographics and enrollment. This has made it convenient for our group
+to quickly generate standardize and complete reports for multiple trials
+concurrently. To date, we have used listdown to report on five clinical
+trials, with another two currently in process. Results are disseminated
+using the \pkg{workflowr} package, usually with nine tabs conveying
+aspects of the data from collection through several different analyses,
+and each tab containing approxiately five to thirty tables, plots, or
+other artifacts including \pkg{trelliscopejs} \citep{trelliscopejs}
+environments which may hold hundreds of graphs. By generating many
+presentation artifacts we are able to address data-drive questions and
+issues during collaborative sessions and by carefully structuring these
+elements we allowing all members to participate in the process.
+
+The \pkg{listdown} package itself is relatively simple with 6 distinct
+methods that can be easily incorporated into existing analysis pipelines
+for automatically creating documents that can be used for data
+exploration and reviewing analysis results as well as a starting point
+for a more formal write up. These methods include:
 
 \begin{itemize}
+\item{\bf as\_ld\_yml() }{- turn a computational component list into YAML with class information}
+\item{\bf ld\_cc\_dendro() }{- create a dendrogram from a list of computational components}
 \item{\bf ld\_chunk\_opts() }{- apply chunk options to a presentation object}
@@
 \item{\bf ld\_make\_chunks() }{- write a listdown object to a string}
+\item{\bf ld\_rmarkdown\_header() }{- create an R Markdown header}
 \item{\bf ld\_workflowr\_header() }{- create a worflowr header}
-\item{\bf ld\_rmarkdown\_header() }{- create an R Markdown header}
 \item{\bf listdown() }{- create a listdown object to create an R Markdown document}
-\item{\bf to\_data\_tree() }{- create a data.tree object from a list of computational components}
 \end{itemize}
@@
 important to realize that even for analyses on large-scale data, the
-digital artifact that will be presented will be relatively small.
-Centralizing them makes it easier to access them, since they don't need
-to be found in mulitple locations. Also, storing them as a list provides
-a hierarchical structure that translates directly to a document as we
-will see below.
+digital artifacts to be presented are relatively small. Centralizing
+them makes it easier to access them, since they don't need to be found
+in mulitple locations. Also, storing them as a list provides a
+hierarchical structure that translates directly to a document as we will
+see below.
 
@@
 loaded into the document, which libraries and code needs to be included,
-the options for the R chunks, and how the list elements will be
-presented in the output R markdown document.
+and how the list elements will be presented in the output R markdown
+document.
 
@@
 
-ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), # The expression to load pres_list in the .Rmd.
-               package = "ggplot2")                     # The packges needed to render plots.
+ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"),
+               package = "ggplot2")
 \end{Sinput}
@@
 to create the document is the header. The listdown package currently
-supports regular R Markdown, workflowr, and ioslides headers. A complete
-document can then be written to the console using the code shown below.
-It could easily be written to a file for rendering using the
-\texttt{writeLines()} function, for example.
+supports regular R Markdown and \pkg{workflowr} as \code{yml} objects
+from the \pkg{yaml} package \citep{yaml}. These objects are stored as
+named lists in R and are easily modified to accomodate document
+parameters. A complete document can then be written to the console using
+the code shown below. It could easily be written to a file for rendering
+using the \texttt{writeLines()} as in the following example.
 
@@
 #> ---
-#> title: "Anscombe's Quartet"
-#> author: "Francis Anscombe"
-#> date: "1973"
+#> title: Anscombe's Quartet
+#> author: Francis Anscombe
+#> date: '1973'
 #> output: html_document
@@
 #> ```{r}
-#> identity(cc_list[[1]])
+#> cc_list$Linear
 #> ```
@@
 #> ```{r}
-#> identity(cc_list[[2]])
+#> cc_list$`Non Linear`
 #> ```
@@
 #> ```{r}
-#> identity(cc_list[[3]])
+#> cc_list$`Outlier Vertical`
 #> ```
@@
 #> ```{r}
-#> identity(cc_list[[4]])
+#> cc_list$`Outlier Horizontal`
 #> ```
@@
 computational components may not translate directly to the presentation
-in a document. In these cases a function is needed that takes the list
+in a document. In these cases, a function is needed that takes the list
 component and returns an object to be displayed. For example, suppose
@@
 #> ```{r echo=FALSE}
-#> identity(cc_list[[5]])
+#> cc_list$Data
 #> ```
@@
 
-In \pkg{listdown} a function or method that implments the presentation
+In \pkg{listdown}, a function or method that implements the presentation
 of a computational component is referred to as a \emph{decorator} since
@@
 #> ```{r}
-#> datatable(cc_list[[5]])
+#> datatable(cc_list$Data)
 #> ```
@@
 the end of the list. This will ensure that specialized classes will be
-encountered first in the resolution process.
+encountered first in the resolution process. It should be noted that an
+object's type is first checked against the decorator name list and then
+checked to see if it is a list. This allows a user to both decorate a
+list and retain \texttt{"list"} in its class attributes.
 
@@
 #>   |-- Iris
-#>   |  °-- object of type(s):data.frame
-#>   °-- Sepal.Length
+#>   |  o-- object of type(s):data.frame
+#>   o-- Sepal.Length
 #>    |-- Sepal.Width
-#>    |  °-- object of type(s):gg ggplot
+#>    |  o-- object of type(s):gg ggplot
 #>    |-- Petal.Length
-#>    |  °-- object of type(s):gg ggplot
-#>    °-- Colored
+#>    |  o-- object of type(s):gg ggplot
+#>    o-- Colored
 #>     |-- Sepal.Width
-#>     |  °-- object of type(s):gg ggplot
-#>     °-- Petal.Length
-#>        °-- object of type(s):gg ggplot 
+#>     |  o-- object of type(s):gg ggplot
+#>     o-- Petal.Length
+#>        o-- object of type(s):gg ggplot 
 #> 
@@
 
-\hypertarget{advanced-usage}{%
-\section{Advanced usage}\label{advanced-usage}}
+\hypertarget{r-code-chunk-customization}{%
+\section{R code chunk customization}\label{r-code-chunk-customization}}
 
-Along with the basic usage, the \pkg{listdown} package supports methods
-to further customize the presentation. Two specific areas of
-customization are addressed. The first is where custom code is required
-either to modify decorators or even define the decorators. In this case,
-we would to add a small portion of code, immediately after loading
-required libraries. In the second case, rather than changing the R code
-inside of a chunk, we would like to change the options for an individual
-chunk. Both of these features are supported in the package and are
-presented below.
+Along with the basic usage, the \pkg{listdown} package supports two
+other capabilities to further customize the presentation. The first is
+where custom code is required either to modify decorators or even define
+a decorators. In this case, we would to add a small portion of code,
+immediately after loading required libraries. In the second case, rather
+than changing the R code inside of a chunk, we would like to change the
+options for an individual chunk. Both of these features are supported in
+the package and are presented below.
 
@@
 \subsection{Initialization code}\label{initialization-code}}
+
+The \texttt{listdown()} function facilitates the insertion of
+initialization code through the \texttt{init\_expr} argument. Code is
+inserted immediately after the libraries are loaded in the R Markdown
+document. In general, it is suggested that the number of initial
+expressions be kept small so that the R Markdown document is easy to
+read. If a large number of functions are required by the target R
+Markdown document then they can be put into a file and sourced using the
+initial expression. As an example, suppose we are creating an html
+document and presenting data using the \texttt{datatable()} function.
+However, we do not want to include the search capabilities provided.
+This can be easily accomplished by creating a new function,
+\texttt{datatable\_no\_search()}, created using the \texttt{partial()}
+function \cite{purrr} to partially apply
+\texttt{list(dom\ =\ \textquotesingle{}t\textquotesingle{})} to the
+\texttt{options} argument of \texttt{datatable}.
 
@@
 #> ```{r echo=FALSE}
-#> datatable <- partial(datatable, options = list(dom = "t"))
+#> 
+#> datatable_no_search <- partial(datatable, options = list(dom = "t"))
 #> ```
@@
 #> ```{r echo = TRUE}
-#> datatable(cc_list[[1]])
+#> datatable_no_search(cc_list$Iris)
 #> ```
@@
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+\hypertarget{a-simple-example-reporting-on-the-gtsummarytrial-dataset}{%
+\section{\texorpdfstring{A simple example: Reporting on the
+\texttt{gtsummary::trial}
+dataset}{A simple example: Reporting on the gtsummary::trial dataset}}\label{a-simple-example-reporting-on-the-gtsummarytrial-dataset}}
+
+\label{sect:simple-example}
+
+\begin{Schunk}
+\begin{Sinput}
+library(gtsummary)
+library(dplyr)
+library(glue)
+library(survival)
+library(survminer)
+library(rmarkdown)
+
+# Function to create the computational components.
+make_surv_cc <- function(trial, treat, surv_cond_chars) {
+  # Create Table 1 by treatment
+  table_1 <- trial %>%
+    tbl_summary(by = all_of(treat)) %>%
+    gtsummary::as_flextable()
+
+  # Create survival plots base on survival characteristics
+  scs <- lapply(c("1", surv_cond_chars),
+                function(sc) {
+                  glue("Surv(ttdeath, death) ~ {treat} + {sc}") %>%
+                    as.formula() %>%
+                    surv_fit(trial) %>%
+                    ggsurvplot()
+                })
+  names(scs) <- c("Overall", tools::toTitleCase(surv_cond_chars))
+  list(`Table 1` = table_1, `Survival Plots` = scs)
+}
+
+# Create the computational components and write to surv-cc.rds.
+make_surv_cc(trial, treat = "trt",
+             surv_cond_chars = c("stage", "grade")) %>%
+  saveRDS("surv-cc.rds")
+
+# Create the listdown object with appropriate dependencies
+# and presentation parameters.
+ld_surv <- listdown(load_cc_expr = readRDS("surv-cc.rds"),
+                    package = c("gtsummary", "survminer"),
+                    decorator = list(ggsurvplot = identity,
+                                     tbl_summary = identity),
+                    echo = FALSE,
+                    message = FALSE,
+                    warning = FALSE,
+                    fig.width = 7,
+                    fig.height = 4.5)
+
+# Write an RMarkdown header and chunks derived from the 
+# computational components and listdown object to trial-report.rmd.
+writeLines(
+  paste(c(
+    as.character(ld_rmarkdown_header("Simple Trial Report")),
+    ld_make_chunks(ld_surv))),
+  "trial-report.rmd")
+
+# Render the RMarkdown file to html.
+render("trial-report.rmd", quiet = TRUE, pdf_document(keep_tex = TRUE))  
+\end{Sinput}
+\end{Schunk}
+
+\hypertarget{using-in-practice-for-clinical-trial-reporting}{%
+\section{\texorpdfstring{Using \pkg{listdown} in practice for clinical
+trial
+reporting}{Using  in practice for clinical trial reporting}}\label{using-in-practice-for-clinical-trial-reporting}}
+
+\pagebreak
+
+\hypertarget{appendix-1-rmarkdown-produced-in-the-simple-example}{%
+\section{Appendix 1: RMarkdown produced in the simple
+example}\label{appendix-1-rmarkdown-produced-in-the-simple-example}}
+
+\begin{Schunk}
+\begin{Sinput}
+---
+title: Simple Trial Report
+output: html_document
+---
+
+\```{r echo=FALSE}
+library(gtsummary)
+library(survminer)
+
+cc_list <- readRDS("surv-cc.rds")
+\```
+
+# Table 1
+
+\```{r echo=FALSE}
+cc_list$`Table 1`
+\```
+
+# Survival Plots
+
+## Overall
+
+\```{r echo=FALSE}
+cc_list$`Survival Plots`$Overall
+\```
+
+## Stage
+
+\```{r echo=FALSE}
+cc_list$`Survival Plots`$Stage
+\```
+
+## Grade
+
+\```{r echo=FALSE}
+cc_list$`Survival Plots`$Grade
+\```
+\end{Sinput}
+\end{Schunk}
+
+\pagebreak
+
+\hypertarget{appendix-2-the-document-produced-by-the-simple-example}{%
+\section{Appendix 2: The document produced by the simple
+example}\label{appendix-2-the-document-produced-by-the-simple-example}}
 

### 2020-04-28 R/as-yml.r

@@ -1,0 +1,63 @@
+
+# Helper function Eval Parse Paste (epp)
+epp <- function(..., env = parent.frame(n = 2)) {
+  eval(parse(text = paste0(...)), envir = env)
+}
+
+last_index_as_list <- function(loc) {
+  re <- regexpr("\\[\\[[0-9]+\\]\\]$", loc)
+  # Get the list location. Not the list element.
+  paste0(substr(loc, 1, re[1] - 1),
+         "[",
+         gsub("\\]\\]", "", gsub("\\[\\[", "", substr(loc, re, nchar(loc)))),
+         "]")
+}
+
+#' @title Turn a Computational Component List into YAML with Class Information
+#'
+#' @description Create an object of type ymlthis::yml from a list of
+#' computational components. The function recursively descends into the list
+#' and when an element type is not a list the class information substituted
+#' for the object.
+#' @param x a named list of computational components.
+#' @importFrom ymlthis as_yml
+#' @examples
+#'  library(ggplot2)
+#'  cc_list <- list(
+#'    Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+#'   `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
+#'   `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
+#'   `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) +
+#'     geom_point())
+#' 
+#'  as_ld_yml(cc_list)
+#' @export
+as_ld_yml <- function(x) {
+
+  depth_first_copy <- function(loc = "") {
+    elem <- epp("x", loc) 
+    locs <- vapply(seq_along(elem),
+                  function(i) paste0(loc, "[[", i, "]]"), NA_character_)
+    for (loc in locs) {
+      elem <- epp("x", loc) 
+
+      if (inherits(elem, "list")) {
+        depth_first_copy(loc)
+      } else {
+        loc_list <- last_index_as_list(loc)
+        if (is.null(names(epp("x", loc_list)))) {
+          eval(parse(text = paste("x", loc, " <<- paste(", 
+                     deparse(class(elem)), ", collapse = \":\")")))
+        } else {
+          # Wrap in a list for formatting.
+          eval(parse(text = paste("x", loc, " <<- list(paste(", 
[…]

### 2020-04-28 R/cc-dendro.r

@@ -23,13 +23,34 @@ ld_cc_dendro <- function(x) {
   if (!is.list(x)) {
     stop(red("Argument should be a list type."))
   }
-  tree_yml <- as_ld_yml(x)
-  class(tree_str) <- c("ld_cc_dendro", class(tree_str))
+
+  tdt_impl <- function(x, prefix_string) {
+    for (i in seq_along(x)) {
+      list_name <- names(x[i])
+      if (is.null(list_name)) {
+        list_name <- '""'
+      }
+      vert_sep <- ifelse(i == length(x), " o-- ", " |-- ")
+      tree_str <<- c(tree_str, paste0(prefix_string, vert_sep, list_name))
+      if (!class(x[[i]])[1] == "list") {
+        in_sep <- ifelse(i == length(x), "  ", " |")
+        tree_str <<- c(tree_str, 
+                       paste0(prefix_string, in_sep, "  o-- ",
+                             "object of type(s):", 
+                             paste0(class(x[[i]]), collapse = " ")))
+      } else {
+        tdt_impl(x[[i]], paste0(prefix_string, " "))
+      }
+    }
+  }
+  tree_str <- as.character(as.list(match.call())$x)
+  tdt_impl(x, " ")
+  class(tree_str) <- "ld_cc_dendro"
   tree_str
 }
 
-#' importFom ymlthis draw_yml_tree
 #' @export
 print.ld_cc_dendro <- function(x, ...) {
-  draw_yml_tree(x, ...)
+  cat("\n", paste(x, collapse = "\n"), "\n", "\n")
+
 }

### 2020-04-28 R/chunk-options.r

@@ -54,10 +54,11 @@ chunk_option_list <- c(
   "out.width",
   "resize.height",
   "resize.width",
-  "sanitize"
+  "sanitize",
+  ""
   )
 
-opt_not_r_chunk <- function(x) {
+not_r_chunk_opts <- function(x) {
   x[!(vapply(x, function(opt) opt %in% chunk_option_list, FALSE))]
 }
 
@@ -69,34 +70,38 @@ opt_not_r_chunk <- function(x) {
 #' @param chunk_name the name of the chunk. By default this is NULL, 
 #' correpsonding to no chunk name.
 #' @param ... named chunk options and their values.
-#' @param arg_list the list of chunk options can be specified. If ... 
-#' parameters are specified, then this option is ignored.
+#' @param chunk_opts list of chunk options can be specified. Takes priority
+#' over arguments provided to ...
 #' @export
-ld_chunk_opts <- function(pres_obj, chunk_name = NULL, ..., arg_list = NULL) {
+ld_chunk_opts <- function(pres_obj, chunk_name = NULL, ..., chunk_opts = NULL) {
   a <- attributes(pres_obj)
-  dots <- list(...)
-  not_r_chunk_opts <- opt_not_r_chunk(names(dots))
+  if (is.null(chunk_opts)) {
+    chunk_opts <- list(...)
+  }
+  not_r_chunk_opts <- not_r_chunk_opts(names(chunk_opts))
   if (length(not_r_chunk_opts) > 0) {
     stop(red("Unrecognized options:\n\t",
              paste(not_r_chunk_opts, collapse = "\n\t"),
              "\n", sep = ""))
   }
-  if (length(dots) > 0) {
-    for (i in seq_along(dots)) {
-      val <- dots[[i]]
+  if (length(chunk_opts) > 0) {
+    for (i in seq_along(chunk_opts)) {
+      val <- chunk_opts[[i]]
       if (is.character(val)) {
         val <- sprintf('"%s"', val)
       } else if (is.null(val)) {
         val <- "NULL"
+      } else if (is.logical(val)) {
+        val <- val
       } else {
         val <- as.character(val)
       }
-      name <- names(dots)[i]
+      name <- names(chunk_opts)[i]
       a$listdown[name] <- list(val)
     }
     attributes(pres_obj) <- a
-  } else if (!is.null(arg_list)) {
-    a$listdown <- arg_list
+  } else if (!is.null(chunk_opts)) {
[…]

### 2020-04-28 R/chunk-writer.r

@@ -11,39 +11,61 @@
 #' to a decorator function.
 #' @param init_expr an initial expression that will be added to the outputted
 #' document after the libraries have been called.
+#' @param elem_chunk_opts a named list mapping the potential types of list
+#' elements to chunk options that should be included for those types.
 #' @param default_decorator the decorator to use for list elements whos type
 #' is not inherited from the decorator list. If NULL then the those
 #' elements will not be included when the chunks are written. By default
 #' this is identity, meaning that the elements will be passed directly 
 #' (through the identity() function).
 #' @param ... default options sent to the chunks of the outputted document.
+#' @param chunk_opts a named list of options sent to the chunks of outputted
+#' documents. Note: takes priority over argument provided to ...
 #' @importFrom crayon red
 #' @export
 listdown <- function(load_cc_expr,
                      package = NULL,
                      decorator = list(),
                      init_expr = NULL,
+                     elem_chunk_opts = list(),
                      default_decorator = identity,
-                     ...) {
+                     ...,
+                     chunk_opts = NULL) {
 
   if ( !("default_decorator" %in% names(as.list(match.call))) ) {
     default_decorator = as.symbol("identity")
   } else {
     default_decorator = as.list(match.call()$default_decorator)
   }
-  dots <- list(...)
-  not_r_chunk_opts <- opt_not_r_chunk(names(dots))
+
+  if (is.null(chunk_opts)) {
+    chunk_opts <- list(...) 
+  }
+ 
+  not_r_chunk_opts <- not_r_chunk_opts(names(chunk_opts))
   if (length(not_r_chunk_opts) > 0) {
     stop(red("Unrecognized options:\n\t",
              paste(not_r_chunk_opts, collapse = "\n\t"),
              "\n", sep = ""))
   }
+
+  # Check the chunk options of elem_chunk_opts.
+  for (i in seq_along(elem_chunk_opts)) {
+    not_r_chunk_opts <- not_r_chunk_opts(names(elem_chunk_opts[[i]]))
+    if (length(not_r_chunk_opts) > 0) {
+      stop(red("Unrecognized options for element type", 
+               names(elem_chunk_opts)[i], ":\n\t",
+               paste(not_r_chunk_opts, collapse = "\n\t"),
+               "\n", sep = ""))
+    }
+  }
[…]

### 2020-04-28 R/depth-first-pres-list-visitor.r

@@ -15,36 +15,48 @@ list_loc_list_string <- function(ll) {
   }
 }
 
-make_chunk_option_string <- function(ld, pres_obj = NULL) {
-  chunk_option_string <- ""
-  if (!is.null(pres_obj) && "listdown" %in% names(attributes(pres_obj))) {
-    lda <- attributes(pres_obj)$listdown
-    name_ind <- which(names(lda) == "chunk_name")
-    chunk_name <- NULL
-    if (length(name_ind)) {
-      chunk_name <- lda[[name_ind]]
-      lda <- lda[-name_ind]
-    } 
-    chunk_option_string <-
-      if (length(lda) > 0 && !is.null(chunk_name)) {
-        paste0(" ", paste(chunk_name,
-               paste(names(lda), "=", as.character(lda), collapse = ", ")))
-      } else if (length(lda) > 0) {
-        paste(chunk_name,
-              paste(names(lda), "=", as.character(lda), collapse = ", "))
-    
-      } else {
-        paste0(" ", chunk_name) 
-      }
-  } else {
-    # Use the default chunk options.
-    if (length(ld$dots) > 0) {
-      chunk_option_string <-
-        paste0(" ", names(ld$dots), "=", as.character(ld$dots), 
-               collapse = ", ")
+list_loc_ind_to_name <- function(pl, env = parent.frame(n = 2)) {
+  ret <- gsub("\\[\\[[0-9]\\]\\]", "", pl)
+  re <- gregexpr('\\[\\[[0-9]+\\]\\]', pl)[[1]]
+  re_len <- attr(re, "match.length")
+  for (i in seq_along(re)) {
+    idx <- substr(pl, re[i], re[i] + re_len[i] - 1)
+    idx_name <- names(epp(ret, last_index_as_list(idx)))
+    # Wrap in backticks if the names isn't a valid variable name.
+    if (idx_name != make.names(idx_name)) {
+      idx_name <- paste0("`", idx_name, "`")
     }
+    ret <- paste0(
+      ret, 
+      ifelse(!is.null(idx_name), 
+             paste0("$", idx_name),
+             idx))
   }
-  chunk_option_string
+  ret
+}
+
+get_attribute_options <- function(ld, pres_obj = NULL) {
+  ret <- list()
+  if (!is.null(pres_obj) && "listdown" %in% names(attributes(pres_obj))) {
+    ret <- attributes(pres_obj)$listdown
+  }
+  ret
[…]

### 2020-04-28 R/headers.r

@@ -1,18 +1,56 @@
+#' @title Create an R Markdown Header
+#' @description Output an R Markdown header with specified parameters.
+#' @param title the title of the page.
+#' @param author the author of the page. The default is NULL - no author.
+#' @param date the date for the page. The default is NULL - no date.
+#' @param output the output format of the page. If NULL then no output format.
+#' The default is an html document.
+#' @export
+ld_rmarkdown_header <- function(title,
+                                author = NULL,
+                                date = NULL,
+                                output = c("html_document",
+                                           "pdf_document",
+                                           "word_document")) {
+  ret <- list(title = title)
+  if (!is.null(author)) {
+    ret$author <- author
+  }
+  if (!is.null(date)) {
+    ret$date <- date
+  }
+  ret$output <- output[1]
+  class(ret) <- c("listdown_header", "list")
+  ret
+}
+
 #' @title Create a workflowr Header
 #' @description Output a workflowr R Markdown header with specified title.
 #' @param title the title of the page.
 #' @param toc should the table of contents be generated? Default FALSE.
-#' @importFrom ymlthis yml yml_title
 #' @export
 ld_workflowr_header <- function(title, toc = FALSE) {
-  yml(
-    list(title = title,
-         site = "workflowr::wflow_site",
-         output = 
-           list(`workflowr::wflow_html` = 
-                list(toc = toc)),
-         editor_options = list(chunk_output_type = "console")),
-    author = FALSE,
-    date = FALSE)
+  ret <- list(title = title,
+       site = "workflowr::wflow_site",
+       output = 
+         list(`workflowr::wflow_html` = 
+              list(toc = toc)),
+       editor_options = list(chunk_output_type = "console"))
+  class(ret) <- c("listdown_header", "list")
+  ret
 }
 
+#' @export
+print.listdown_header <- function(x, ...) {
+  ret <- as.character(x)
+  cat(ret, "\n", sep = "")
+  invisible(ret)
+}
+
+#' @export
+#' @importFrom yaml as.yaml
+as.character.listdown_header <- function(x, ...) {
+  paste0("---\n",
+         as.yaml(x, ...),
+         "---", collapse = "\n")
+}

### 2020-04-28 tests/testthat/test-add-chunk-option.r

@@ -77,7 +77,8 @@ test_that("Options can be NULL", {
 })
 
 test_that("Arg liststs can be created.", {
-  arg_list = list(echo = FALSE, eval = TRUE)
-  plt <- ld_chunk_opts(pres_list$iris, arg_list = arg_list)
-  expect_equal(attributes(plt)$listdown, arg_list)
+  chunk_opts <- list(echo = FALSE, eval = TRUE)
+  plt <- ld_chunk_opts(pres_list$iris, chunk_opts = chunk_opts)
+  attributes(plt)$listdown$chunk_name <- NULL
+  expect_equal(attributes(plt)$listdown, chunk_opts)
 })

### 2020-04-28 tests/testthat/test-make-chunks.r

@@ -63,7 +63,8 @@ ld2 <- listdown(load_cc_expr = readRDS("reference-data/test_list.rds"),
                 decorator = list(data.frame = datatable),
                 init_expr = {
                   datatable <- partial(DT::datatable,
-                                       options = list(ordering = FALSE))},
+                                       options = list(ordering = FALSE))
+                },
                 echo = FALSE,
                 warning = FALSE,
                 message = FALSE)

### 2020-04-28 R/cc-dendro.r
Added testing.

@@ -51,6 +51,6 @@ ld_cc_dendro <- function(x) {
 
 #' @export
 print.ld_cc_dendro <- function(x, ...) {
-  cat("\n", paste(x, collapse = "\n"), "\n", "\n")
-
+  cat("\n", paste(x, sep = "", collapse = "\n"), "\n", "\n", sep = "")
+  invisible(x)
 }

### 2020-04-28 R/chunk-options.r

@@ -86,16 +86,16 @@ ld_chunk_opts <- function(pres_obj, chunk_name = NULL, ..., chunk_opts = NULL) {
   }
   if (length(chunk_opts) > 0) {
     for (i in seq_along(chunk_opts)) {
-      val <- chunk_opts[[i]]
-      if (is.character(val)) {
-        val <- sprintf('"%s"', val)
-      } else if (is.null(val)) {
-        val <- "NULL"
-      } else if (is.logical(val)) {
-        val <- val
-      } else {
-        val <- as.character(val)
-      }
+      val <- deparse(chunk_opts[[i]])
+#      if (is.character(val)) {
+#        val <- sprintf('"%s"', val)
+#      } else if (is.null(val)) {
+#        val <- "NULL"
+#      } else if (is.logical(val)) {
+#        val <- val
+#      } else {
+#        val <- as.character(val)
+#      }
       name <- names(chunk_opts)[i]
       a$listdown[name] <- list(val)
     }

### 2020-04-28 tests/testthat/test-add-chunk-elem-option.r

@@ -1,0 +1,35 @@
+context("Chunk Element Option")
+
+source("make-reference.r")
+
+if (make_reference) {
+  dir.create("reference-data", showWarnings = FALSE)
+}
+
+pres_list <- list(iris = iris, 
+                  mtcars = mtcars)
+
+saveRDS(pres_list, "reference-data/option-element-check.rds")
+
+expect_error(
+  listdown(readRDS("reference-data/option-check.rds"),
+           package = "knitr",
+           decorator = list(data.frame = kable),
+           elem_chunk_opts = 
+             list(data.frame = list("test_chunk", bunk= FALSE))))
+
+ld <- listdown(readRDS("reference-data/option-check.rds"),
+               package = "knitr",
+               decorator = list(data.frame = kable),
+               elem_chunk_opts = 
+                 list(data.frame = list("test_chunk", echo = FALSE, 
+                                        results = "as.is")))
+
+
+if (make_reference) {
+  saveRDS(ld_make_chunks(ld),
+          file.path("reference-data", "chunk-elem-option-1.rds"))
+}
+
+expect_equal(ld_make_chunks(ld), 
+             readRDS(file.path("reference-data", "chunk-elem-option-1.rds")))

### 2020-04-28 tests/testthat/test-add-chunk-option.r

@@ -80,5 +80,5 @@ test_that("Arg liststs can be created.", {
   chunk_opts <- list(echo = FALSE, eval = TRUE)
   plt <- ld_chunk_opts(pres_list$iris, chunk_opts = chunk_opts)
   attributes(plt)$listdown$chunk_name <- NULL
-  expect_equal(attributes(plt)$listdown, chunk_opts)
+  expect_equal(attributes(plt)$listdown, list(echo = "FALSE", eval = "TRUE"))
 })

### 2020-04-28 tests/testthat/test-as-yml.r

@@ -1,0 +1,24 @@
+context("As YAML")
+
+library(ggplot2)
+
+source("make-reference.r")
+
+if (make_reference) {
+  dir.create("reference-data", showWarnings = FALSE)
+}
+
+cc_list <- list(
+  Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+  `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
+  `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
+  `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + geom_point(),
+  a = list(b = 3, 4))
+
+if (make_reference) {
+  saveRDS(as_ld_yml(cc_list),
+          file.path("reference-data", "as-yml.rds"))
+}
+
+expect_equal(as_ld_yml(cc_list),
+             readRDS(file.path("reference-data", "as-yml.rds")))

### 2020-04-28 tests/testthat/test-cc-dendro.r

@@ -1,0 +1,33 @@
+context("Dendrogram")
+
+library(ggplot2)
+
+if (make_reference) {
+  dir.create("reference-data", showWarnings = FALSE)
+}
+
+cc_list <- 
+  list(
+    Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+    `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
+    `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
+    `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + geom_point()  )
+
+if (make_reference) {
+  saveRDS(ld_cc_dendro(cc_list),
+          file.path("reference-data", "cc-dendro.rds"))
+}
+
+expect_equal(ld_cc_dendro(cc_list), 
+             readRDS(file.path("reference-data", "cc-dendro.rds")))
+
+expect_error(ld_cc_dendro(exp))
+
+ldc <- ld_cc_dendro(cc_list)
+
+pldc <- capture.output(print(ldc))
+
+expect_equal(unclass(pldc), c("", unclass(ldc), ""))
+
+pldc <- capture.output(ld_cc_dendro(list(3)))
+

### 2020-04-28 tests/testthat/test-headers.r

@@ -10,13 +10,30 @@ if (make_reference) {
 }
 
 if (make_reference) {
+  saveRDS(ld_rmarkdown_header("Workflow R", author = "Some Dude",
+                              date = "2020"),
+          file.path("reference-data", "test-rmarkdown-header.rds"))
+}
+
+mdh <- ld_rmarkdown_header("Workflow R", author = "Some Dude", date = "2020")
+test_that("The R Markdown header hasn't changed.", {
+  expect_equal(mdh,
+               readRDS(file.path("reference-data", 
+                       "test-rmarkdown-header.rds")))
+})
+
+capture.output(mdh)
+
+if (make_reference) {
   saveRDS(ld_workflowr_header("Workflow R"),
           file.path("reference-data", "test-workflowr-header.rds"))
 }
 
-test_that("The workflowr header hasn't changed.", {
-  expect_equal(ld_workflowr_header("Workflow R"),
+wfr <- ld_workflowr_header("Workflow R")
+test_that("The workflowrheader hasn't changed.", {
+  expect_equal(wfr,
                readRDS(file.path("reference-data", 
                        "test-workflowr-header.rds")))
 })
+
 

### 2020-04-28 R/as-yml.r
Fixed yaml dependency.

@@ -15,12 +15,12 @@ last_index_as_list <- function(loc) {
 
 #' @title Turn a Computational Component List into YAML with Class Information
 #'
-#' @description Create an object of type ymlthis::yml from a list of
+#' @description Create an object of type yaml::yml from a list of
 #' computational components. The function recursively descends into the list
 #' and when an element type is not a list the class information substituted
 #' for the object.
 #' @param x a named list of computational components.
-#' @importFrom ymlthis as_yml
+#' @importFrom yaml as.yaml
 #' @examples
 #'  library(ggplot2)
 #'  cc_list <- list(
@@ -58,6 +58,6 @@ as_ld_yml <- function(x) {
     }
   }
   depth_first_copy()
-  as_yml(x)
+  as.yaml(x)
 }
 

### 2020-04-28 R/depth-first-pres-list-visitor.r

@@ -59,6 +59,7 @@ make_chunk_option_string <- function(chunk_opts) {
   ret
 }
 
+#' @importFrom crayon yellow
 depth_first_concat <- function(cc_list, ld, heading = "#",
                                list_location = c()) {
 

### 2020-04-29 README.rmd
Updated README.

--- 2020-03-08 README.Rmd
@@
 ld <- listdown(load_cc_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
-               package = "ggplot2",                     # The packges needed to render plots.
-               decorator = list(ggplot = identity))     # What to do with the pres_list elements.
+               package = "ggplot2"))                    # The packges needed to render plots.
 
@@
 doc <- c(
+  as.character(
     ld_rmarkdown_header("Anscombe's Quartet",
                         author = "Francis Anscombe",
-                     date = "1973"),
-  ld_make_chunks(pres_list, ld))
+                        date = "1973")),
+  ld_make_chunks(ld))
 
-doc
+cat(paste(doc, collapse = "\n"))
 ```
@@
 ld <- listdown(load_cc_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
-               package = "ggplot2",                     # The packges needed to render plots.
-               decorator = list(ggplot = identity))     # What to do with the plot types.
+               package = "ggplot2")                     # The packges needed to render plots.
 
@@
 doc <- c(
+  as.character(
     ld_rmarkdown_header("Anscombe's Quartet",
                         author = "Francis Anscombe",
-                      date = "1973"),
+                        date = "1973")),
   ld_make_chunks(ld))
 
-doc
+cat(paste(doc, collapse = "\n"))
 ```

### 2020-04-29 R/as-yml.r
Styled.

@@ -29,35 +29,33 @@ last_index_as_list <- function(loc) {
 #'   `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
 #'   `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) +
 #'     geom_point())
-#' 
+#'
 #'  as_ld_yml(cc_list)
 #' @export
 as_ld_yml <- function(x) {
 
   depth_first_copy <- function(loc = "") {
-    elem <- epp("x", loc) 
+    elem <- epp("x", loc)
     locs <- vapply(seq_along(elem),
                   function(i) paste0(loc, "[[", i, "]]"), NA_character_)
     for (loc in locs) {
-      elem <- epp("x", loc) 
+      elem <- epp("x", loc)
 
       if (inherits(elem, "list")) {
         depth_first_copy(loc)
       } else {
         loc_list <- last_index_as_list(loc)
         if (is.null(names(epp("x", loc_list)))) {
-          eval(parse(text = paste("x", loc, " <<- paste(", 
+          eval(parse(text = paste("x", loc, " <<- paste(",
                      deparse(class(elem)), ", collapse = \":\")")))
         } else {
           # Wrap in a list for formatting.
-          eval(parse(text = paste("x", loc, " <<- list(paste(", 
+          eval(parse(text = paste("x", loc, " <<- list(paste(",
                      deparse(class(elem)), ", collapse = \":\"))")))
         }
-      
       }
     }
   }
   depth_first_copy()
   as.yaml(x)
 }
-

### 2020-04-29 R/cc-dendro.r

@@ -1,7 +1,7 @@
 
 #' @title Show the list of Computational Components as a Dendrogram
-#' 
-#' @description This function creates text dendrograms from 
+#'
+#' @description This function creates text dendrograms from
 #' a list of computational components. It is useful for
 #' creating a dendrogram of the the computational components of a listdown
 #' object allowing the user to view the components hierarchically.
@@ -9,12 +9,12 @@
 #' @importFrom crayon red
 #' @examples
 #' library(ggplot2)
-#' 
+#'
 #' cc_list <- list(
 #'   Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
 #'  `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
 #'  `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
-#'  `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + 
+#'  `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) +
 #'    geom_point())
 #'
 #' ld_cc_dendro(cc_list)
@@ -34,9 +34,9 @@ ld_cc_dendro <- function(x) {
       tree_str <<- c(tree_str, paste0(prefix_string, vert_sep, list_name))
       if (!class(x[[i]])[1] == "list") {
         in_sep <- ifelse(i == length(x), "  ", " |")
-        tree_str <<- c(tree_str, 
+        tree_str <<- c(tree_str,
                        paste0(prefix_string, in_sep, "  o-- ",
-                             "object of type(s):", 
+                             "object of type(s):",
                              paste0(class(x[[i]]), collapse = " ")))
       } else {
         tdt_impl(x[[i]], paste0(prefix_string, " "))

### 2020-04-29 R/chunk-options.r

@@ -63,12 +63,12 @@ not_r_chunk_opts <- function(x) {
 }
 
 #' @title Apply Chunk Options to a Presentation Object
-#' @description This function allows the user to set chunk options for 
+#' @description This function allows the user to set chunk options for
 #' individual elements of a presentation list.
 #' @param pres_obj the presentation list element whose chunk options should
 #' be modified.
-#' @param chunk_name the name of the chunk. By default this is NULL, 
-#' correpsonding to no chunk name.
+#' @param chunk_name the name of the chunk. By default this is NULL,
+#' corresponding to no chunk name.
 #' @param ... named chunk options and their values.
 #' @param chunk_opts list of chunk options can be specified. Takes priority
 #' over arguments provided to ...
@@ -87,15 +87,6 @@ ld_chunk_opts <- function(pres_obj, chunk_name = NULL, ..., chunk_opts = NULL) {
   if (length(chunk_opts) > 0) {
     for (i in seq_along(chunk_opts)) {
       val <- deparse(chunk_opts[[i]])
-#      if (is.character(val)) {
-#        val <- sprintf('"%s"', val)
-#      } else if (is.null(val)) {
-#        val <- "NULL"
-#      } else if (is.logical(val)) {
-#        val <- val
-#      } else {
-#        val <- as.character(val)
-#      }
       name <- names(chunk_opts)[i]
       a$listdown[name] <- list(val)
     }
@@ -111,5 +102,3 @@ ld_chunk_opts <- function(pres_obj, chunk_name = NULL, ..., chunk_opts = NULL) {
   }
   pres_obj
 }
-
-

### 2020-04-29 R/chunk-writer.r

@@ -4,7 +4,7 @@
 #' list should be used to create an R Markdown document. It requires an
 #' unquoted expression indicating how the presentation list will be loaded.
 #' In addition, libraries required by the outputted document and other
-#' paraeters can be specified.
+#' parameters can be specified.
 #' @param load_cc_expr an unquoted expression to load the presentation list.
 #' @param package a quoted list of package required by the outputted document.
 #' @param decorator a named list mapping the potential types of list elements
@@ -13,10 +13,10 @@
 #' document after the libraries have been called.
 #' @param elem_chunk_opts a named list mapping the potential types of list
 #' elements to chunk options that should be included for those types.
-#' @param default_decorator the decorator to use for list elements whos type
+#' @param default_decorator the decorator to use for list elements whose type
 #' is not inherited from the decorator list. If NULL then the those
 #' elements will not be included when the chunks are written. By default
-#' this is identity, meaning that the elements will be passed directly 
+#' this is identity, meaning that the elements will be passed directly
 #' (through the identity() function).
 #' @param ... default options sent to the chunks of the outputted document.
 #' @param chunk_opts a named list of options sent to the chunks of outputted
@@ -33,15 +33,15 @@ listdown <- function(load_cc_expr,
                      chunk_opts = NULL) {
 
   if ( !("default_decorator" %in% names(as.list(match.call))) ) {
-    default_decorator = as.symbol("identity")
+    default_decorator <- as.symbol("identity")
   } else {
-    default_decorator = as.list(match.call()$default_decorator)
+    default_decorator <- as.list(match.call()$default_decorator)
   }
 
   if (is.null(chunk_opts)) {
-    chunk_opts <- list(...) 
+    chunk_opts <- list(...)
   }
- 
+
   not_r_chunk_opts <- not_r_chunk_opts(names(chunk_opts))
   if (length(not_r_chunk_opts) > 0) {
     stop(red("Unrecognized options:\n\t",
@@ -53,7 +53,7 @@ listdown <- function(load_cc_expr,
   for (i in seq_along(elem_chunk_opts)) {
     not_r_chunk_opts <- not_r_chunk_opts(names(elem_chunk_opts[[i]]))
     if (length(not_r_chunk_opts) > 0) {
-      stop(red("Unrecognized options for element type", 
+      stop(red("Unrecognized options for element type",
                names(elem_chunk_opts)[i], ":\n\t",
[…]

### 2020-04-29 R/depth-first-pres-list-visitor.r

@@ -17,7 +17,7 @@ list_loc_list_string <- function(ll) {
 
 list_loc_ind_to_name <- function(pl, env = parent.frame(n = 2)) {
   ret <- gsub("\\[\\[[0-9]\\]\\]", "", pl)
-  re <- gregexpr('\\[\\[[0-9]+\\]\\]', pl)[[1]]
+  re <- gregexpr("\\[\\[[0-9]+\\]\\]", pl)[[1]]
   re_len <- attr(re, "match.length")
   for (i in seq_along(re)) {
     idx <- substr(pl, re[i], re[i] + re_len[i] - 1)
@@ -27,8 +27,8 @@ list_loc_ind_to_name <- function(pl, env = parent.frame(n = 2)) {
       idx_name <- paste0("`", idx_name, "`")
     }
     ret <- paste0(
-      ret, 
-      ifelse(!is.null(idx_name), 
+      ret,
+      ifelse(!is.null(idx_name),
              paste0("$", idx_name),
              idx))
   }
@@ -52,7 +52,7 @@ make_chunk_option_string <- function(chunk_opts) {
   }
   for (i in seq_along(named_elements)) {
     ret <- paste(
-      ret, 
+      ret,
       paste(names(named_elements)[i], "=", deparse(named_elements[[i]])),
       collapse = " ")
   }
@@ -84,7 +84,7 @@ depth_first_concat <- function(cc_list, ld, heading = "#",
       }
 
       decorator_index <- which(
-        vapply(names(ld$decorator), 
+        vapply(names(ld$decorator),
                function(x) inherits(eval(parse(text = pl)), x), NA))
 
       if (length(decorator_index) > 1) {
@@ -94,7 +94,7 @@ depth_first_concat <- function(cc_list, ld, heading = "#",
       }
 
       chunk_opts <- ld$chunk_opts
-      
+
       chunk_option_index <- which(
         vapply(names(ld$elem_chunk_opts),
                function(x) inherits(eval(parse(text = pl)), x), NA))
@@ -104,7 +104,7 @@ depth_first_concat <- function(cc_list, ld, heading = "#",
                        paste(names(decorator_index), collapse = " "),
                        ".\n\nUsing the first.", sep = " "))
       }
-      
+
       if (length(chunk_option_index) == 1) {
         new_chunk_opts <- ld$elem_chunk_opts[[chunk_option_index]]
         for (i in seq_along(new_chunk_opts)) {
[…]

### 2020-04-29 R/headers.r

@@ -32,8 +32,8 @@ ld_rmarkdown_header <- function(title,
 ld_workflowr_header <- function(title, toc = FALSE) {
   ret <- list(title = title,
        site = "workflowr::wflow_site",
-       output = 
-         list(`workflowr::wflow_html` = 
+       output =
+         list(`workflowr::wflow_html` =
               list(toc = toc)),
        editor_options = list(chunk_output_type = "console"))
   class(ret) <- c("listdown_header", "list")

### 2020-04-29 tests/testthat/test-add-chunk-elem-option.r

@@ -6,7 +6,7 @@ if (make_reference) {
   dir.create("reference-data", showWarnings = FALSE)
 }
 
-pres_list <- list(iris = iris, 
+pres_list <- list(iris = iris,
                   mtcars = mtcars)
 
 saveRDS(pres_list, "reference-data/option-element-check.rds")
@@ -15,14 +15,14 @@ expect_error(
   listdown(readRDS("reference-data/option-check.rds"),
            package = "knitr",
            decorator = list(data.frame = kable),
-           elem_chunk_opts = 
-             list(data.frame = list("test_chunk", bunk= FALSE))))
+           elem_chunk_opts =
+             list(data.frame = list("test_chunk", bunk = FALSE))))
 
 ld <- listdown(readRDS("reference-data/option-check.rds"),
                package = "knitr",
                decorator = list(data.frame = kable),
-               elem_chunk_opts = 
-                 list(data.frame = list("test_chunk", echo = FALSE, 
+               elem_chunk_opts =
+                 list(data.frame = list("test_chunk", echo = FALSE,
                                         results = "as.is")))
 
 
@@ -31,5 +31,5 @@ if (make_reference) {
           file.path("reference-data", "chunk-elem-option-1.rds"))
 }
 
-expect_equal(ld_make_chunks(ld), 
+expect_equal(ld_make_chunks(ld),
              readRDS(file.path("reference-data", "chunk-elem-option-1.rds")))

### 2020-04-29 tests/testthat/test-add-chunk-option.r

@@ -7,7 +7,7 @@ if (make_reference) {
   dir.create("reference-data", showWarnings = FALSE)
 }
 
-pres_list <- list(iris = iris, 
+pres_list <- list(iris = iris,
                   mtcars = mtcars)
 
 saveRDS(pres_list, "reference-data/option-check.rds")
@@ -30,7 +30,7 @@ test_that("Output with no options works.", {
                readRDS(file.path("reference-data", "chunk-option-1.rds")))
 })
 
-pres_list$mtcars <- ld_chunk_opts(pres_list$mtcars, 
+pres_list$mtcars <- ld_chunk_opts(pres_list$mtcars,
                                   echo = FALSE, results = "as.is")
 
 if (make_reference) {

### 2020-04-29 tests/testthat/test-as-yml.r

@@ -11,7 +11,7 @@ if (make_reference) {
 cc_list <- list(
   Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
   `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
-  `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
+  `Outlier Vertical` = ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
   `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + geom_point(),
   a = list(b = 3, 4))
 

### 2020-04-29 tests/testthat/test-cc-dendro.r

@@ -6,19 +6,20 @@ if (make_reference) {
   dir.create("reference-data", showWarnings = FALSE)
 }
 
-cc_list <- 
+cc_list <-
   list(
     Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
     `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
-    `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
-    `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + geom_point()  )
+    `Outlier Vertical` = ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
+    `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + geom_point()
+  )
 
 if (make_reference) {
   saveRDS(ld_cc_dendro(cc_list),
           file.path("reference-data", "cc-dendro.rds"))
 }
 
-expect_equal(ld_cc_dendro(cc_list), 
+expect_equal(ld_cc_dendro(cc_list),
              readRDS(file.path("reference-data", "cc-dendro.rds")))
 
 expect_error(ld_cc_dendro(exp))
@@ -30,4 +31,3 @@ pldc <- capture.output(print(ldc))
 expect_equal(unclass(pldc), c("", unclass(ldc), ""))
 
 pldc <- capture.output(ld_cc_dendro(list(3)))
-

### 2020-04-29 tests/testthat/test-chunk-opts.r

@@ -13,4 +13,3 @@ test_that("Bad chunk options fail.", {
                decorators = list(data.frame = kable),
                bunk = letters))
 })
-

### 2020-04-29 tests/testthat/test-headers.r

@@ -18,7 +18,7 @@ if (make_reference) {
 mdh <- ld_rmarkdown_header("Workflow R", author = "Some Dude", date = "2020")
 test_that("The R Markdown header hasn't changed.", {
   expect_equal(mdh,
-               readRDS(file.path("reference-data", 
+               readRDS(file.path("reference-data",
                        "test-rmarkdown-header.rds")))
 })
 
@@ -32,8 +32,6 @@ if (make_reference) {
 wfr <- ld_workflowr_header("Workflow R")
 test_that("The workflowrheader hasn't changed.", {
   expect_equal(wfr,
-               readRDS(file.path("reference-data", 
+               readRDS(file.path("reference-data",
                        "test-workflowr-header.rds")))
 })
-
-

### 2020-06-09 inst/jss/kane-listdown/kane-listdown.Rmd
JSS Initial commit.

--- 2020-04-28 inst/r-journal/listdown-article.rmd
@@
 ---
-title: Programmatic Generation of R Markdown Documents with \pkg{listdown}
+documentclass: jss
 author:
@@
     email:  michael.kane@yale.edu
+title:
+  formatted: "On the Programmatic Generation of Reproducible Documents"
+  # If you use tex in the formatted title, also supply version without
+  plain:     "On the Programmatic Generation of Reproducible Documents"
+  # For running headers, if needed
+  short:     "Programmatic Generation of Reproducible Documents"
 abstract: >
-  An abstract of less than 150 words.
-preamble: |
-  % Any extra LaTeX you need in the preamble
-output: rticles::rjournal_article
+  The abstract of the article.
+keywords:
+  # at least one keyword must be supplied
+  formatted: [reproducibility, data presentation]
+  plain:     [reproducibility, data presentation]
+preamble: >
+  \usepackage{amsmath}
+output: rticles::jss_article
 ---

### 2020-06-11 inst/jss/kane-listdown/supplemental-material/kane-listdown.Rmd
JSS Draft.

--- 2020-04-28 inst/r-journal/listdown-article.rmd
@@
     email:  michael.kane@yale.edu
+title:
+  formatted: "On the Programmatic Generation of Reproducible Documents"
+  # If you use tex in the formatted title, also supply version without
+  plain:     "On the Programmatic Generation of Reproducible Documents"
+  # For running headers, if needed
+  short:     "On the Programmatic Generation of Reproducible Documents"
 abstract: >
-  An abstract of less than 150 words.
-preamble: |
-  % Any extra LaTeX you need in the preamble
-output: rticles::rjournal_article
+  Reproducible document standards, like \proglang{R} Markdown, facilitate the programmatic creation of documents whose content is itself programmatically generated.
+While these documents are generally not complete in the sense that they will not include prose content, generated by an author to provide context, a narrative, etc., programmatic generation can provide substantial efficiencies for structuring and constructing documents.
+This paper explores the programmatic generation of reproducible by distinguishing components than can be created by computational means from those requiring human-generated prose, providing guidelines for the generation of these documents, and identifying a use case in clinical trial reporting.
+These concepts and use case are illustrated through the \pkg{listdown} package for the \proglang{R} programming environment, which is is currently available on the Comprehensive R Archive Network (CRAN).
+keywords:
+  # at least one keyword must be supplied
+  formatted: [reproducibility, reproducible documents, data presentation]
+  plain:     [reproducibility, reproducible documents, data presentation]
+preamble: >
+  \usepackage{amsmath}
+output: rticles::jss_article
 ---
@@
 
-R Markdown documents support the construction of reproducible documents by allowing authors to insert R code for data processing, exploration, analysis, table-making, and visualization directly into structured, prose documents.
-In the context of this document, we will refer to the R code in these documents as _computational components_ since they are generated by computational means (namely the R interpreter).
-The prose in these documents will be referred to as _narrative components_.
-They may serve to help a reader understand the background, goal, theme, and results of the paper as well as contextualizing the computational components.
+\proglang{R} Markdown [@baumer2014] facilitates the construction of computationally reproducible documents by allowing authors to insert \proglang{R} code for data processing, exploration, analysis, table-making, and visualization directly into structured, electronic documents.
+The resulting documents are made up of these chunks of \proglang{R} code, which we will refer to as _computational components_ since they are generated by computational means, as well as _narrative components_, which (in scientific writing) is prose intended to contextualize computational components, provide background, define goals, establish themes, and convey the results of the document.
+The integration of narrative and computational components was identified as "Literate Programming" by @knuth1984 and software tools, like Sweave [@leisch2002], have supported this functionality for almost two decades.
 
-R Markdown [@baumer2014] integrates the process of integrating the computational and narrative components of a document.
-By itself this is not novel.
-It was identified as "Literate Programming" by @knuth1984 and software tools, like Sweave [@leisch2002] have supported this functionality for almost two decades.
-R Markdown's popularity has likely been driven by two factors.
+\proglang{R} Markdown is particularly popular with its success likely being driven by two factors.
 The first is the relative ease with which these documents can be constructed.
-While it is more expressive, \LaTeX is relatively technical and requires an investment in time to become proficient.
-By contrast R Markdown documents are easier to create and format and, when the document is used to create \LaTeX formatting can be passed through to the underlying .tex file.
-The second factor driving adoption is likely its support for creating _modifiable_ documents, Microsoft Word in particular.
+While \LaTeX \ is more expressive, it is relatively technical and requires an investment in time to become proficient.
+By contrast \proglang{R} Markdown documents are easier to create and format and, when the document is used to create \LaTeX, formatting can be passed through to the underlying .tex file.
+The second factor driving adoption is likely its support for creating _modifiable_ documents, namely Microsoft Word documents.
 Researchers and analysts, especially those creating applied statistical analyses, often collaborate with domain experts with less technical knowledge.
@@
 
-Since computational components are, by definition, computationally derived objects and R Markdown is a well-defined standard it is possible to programmatically create R Markdown documents with computational components.
-This is the focus of this paper.
+Since computational components are, by definition, computationally derived objects and R Markdown is a well-defined standard, it is possible to programmatically create \proglang{R} Markdown documents with computational components, which is the focus of this paper.
 However, before proceeding down this avenue, we would like to highlight two fundamental limitations to automated R Markdown document construction.
-First and foremost, without narrative components a document has no context.
+First and foremost, without narrative components a document has very little context.
 Quantitative analyses require research questions, hypotheses, reviews, interpretations, and conclusions.
-Computational components are necessary but not sufficient for constructing an analysis.
-Second, it is not possible to construct computational components for an arbitary analyses.
+Computational components are necessary but generally not sufficient for constructing an analysis.
+Second, it is difficult if not impossible to construct computational components for an arbitary analyses.
 Analyses themselves have context and are built with a set of assumptions and goals.
-Computational components are constructed for a narrow class of problems.
 
-However, this is not to say the programmatic creation of R Markdown documents is unwarranted or not useful.
+This is not to say the programmatic creation of \proglang{R} Markdown documents is unwarranted or not useful.
 In fact, it has at least two appealing characteristics.
-The first is that it allows us to distinguish the presentation of analytical results from other steps in a data science or data processing pipeline.
+First, it allows us to distinguish the presentation of analytical results from other steps in a data science or data processing pipeline.
 These other steps including cleaning and analysis often require their own environment and configuration with requirements very different than the computational needs of creating a presentation.
 By separating these components each can be developed independently.
-At the same time, by specifying that the output of those objects are organized hierarchically, we are essentially creating a contract by which processed data can be passed to the presentation as well as providing a way to organize the results.
+At the same time, by specifying a contract for the output of those objects, we can establish a consistent means by which processed data can be passed to systems for presentating those data in a structured way.
 The second reason for programmatic creation of R Markdown documents is convenience.
 In collaborative environments, especially in the early stages, large numbers of graphs and tables are generated and discussed.
-By collecting these artifacts hierarchicaly as a list, they can be quickly iterated upon and restructured to more clearly present the data without needing to spend time on the creation of the presentation document.
+By collecting these artifacts and structuring them consistently, we can quickly iterate upon and restructure the resulting documents to more clearly present the data without needing to spend time on the creation of the presentation document.
 
-The \pkg{listdown} package provides functions to programmatically create R Markdown files from 
-named lists. It is intended for data analysis pipelines where the presentation of the results
+The \pkg{listdown} package provides functions to programmatically create \proglang{R} Markdown files from named lists. It is intended for data analysis pipelines where the presentation of the results
 is separated from their creation. For this use case, a data processing (or analysis) is performed
 and the results are provided in a single named list, organized heirarchically.
-With the list and a \pkg{listdown} object a \pkg{workflowr} [@blischak2019], pdf, word, or html page.
-List element names denote sections, subsections,
-subsubsection, etc. and the list elements contain the data structure to be presented including
-graphs and tables.
-The goal of the package is not to provide a finished, readable document.
-It is to provide a document with all tables and visualization that will appear (_computational_ components).
-This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions (_narrative_ components).
+List element names denote sections, subsections, subsubsection, etc.
+and the list elements contain the data structure to be presented including graphs and tables.
+The package has native support for \pkg{workflowr} [@blischak2019], pdf, word, or html document along with functions allowing a user to easily extend to other types of supported documents.
+The goal of the package is to create a documents with all tables and visualization that will appear (computational components).
+This serves as a starting point from which a user can organize outputs, describe a study, discuss results, and provide conclusions (narrative components).
 
-\pkg{listdown} provides a reproducible means for producing a document with specified computational components.
-It is most compatible with data analysis pipelines where the data format is fixed but the analyses are either being updated, which may affect narrative components including the result discussion and conclusion, or where the experiment is different, which affects all narrative components If the narrative components are not changing with the data being pushed through your analysis pipeline, then you may be better off writing the R Markdown code manually.
+\pkg{listdown} therefore provides a reproducible means for producing a document with specified computational components.
+It is most compatible with data analysis pipelines where the data format is fixed but the analyses are either being updated, which may affect narrative components including the result discussion and conclusion, or where the experiment is different, which affects all narrative components, but the data format and processing is consistent.
+An example of the former is provided later in this paper.
 
@@
 The associated presentations require very little context - clinicians often have a better understanding of the data collected than the statistician - often eliminating the need for narrative components.
-At the same time, a large number of hierarchical, heterogenous artifacts (tables and multiple types of plots) need to be conveyed thereby making the manual creation of R Markdown documents inconvenient.
+At the same time, a large number of hierarchical, heterogenous artifacts (tables and multiple types of plots) need to be conveyed thereby making the manual creation of \proglang{R} Markdown documents inconvenient.
 
-Furthermore, data processing can be fixed across trials.
+In this case, data presentation can be fixed across trials.
 This is especially true in the initial stages, which focus on patient demographics and enrollment.
-This has made it convenient for our group to quickly generate standardize and complete reports for multiple trials concurrently.
+This approach has made it convenient for our group to quickly generate standardize and complete reports for multiple trials concurrently.
 To date, we have used listdown to report on five clinical trials, with another two currently in process.
@@
     `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
-    `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
-    `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + geom_point())
+    `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + 
+      geom_point(),
+    `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + 
+      geom_point())
 
@@
 
-## Creating a document with \pkg{listdown}
+## Creating a document with listdown
 
-Creating a document from the `computational_components` will require two steps.
+Creating a document from the `computational_components` requires two steps.
 First, we will create a `listdown` object that specifies how the `computational_components` object will be loaded into the document,  which libraries and code needs to be included, and how the list elements will be presented in the output R markdown document.
@@
 A complete document can then be written to the console using the code shown below.
-It could easily be written to a file for rendering using the `writeLines()` as in the following example.
+It could easily be written to a file for rendering using the `writeLines()` function.
 
@@
 doc <- c(
-  as.character(
-    ld_rmarkdown_header("Anscombe's Quartet",
+  unlist(strsplit(as.character(ld_rmarkdown_header("Anscombe's Quartet",
                                author = "Francis Anscombe",
                                date = "1973")),
+                  "\n", fixed = TRUE)),
   ld_make_chunks(ld))
 
-cat(paste(doc, collapse = "\n"))
+doc
 ```
@@
 The chunk options are exactly the same as those in the R markdown document and can be used to tailor the default presentation for a variety of needs.
-The complete set of options can be found in the [R Markdown Reference Guide](https://rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf).
+The complete set of options can be found in the R Markdown Reference Guide [@rmarkdownref].
 As a concrete example, the code used to create present the plots could be hidden in the output document using the following code.
@@
 
-cat(paste(ld_make_chunks(ld)[1:7], collapse = "\n"))
+#cat(paste(ld_make_chunks(ld)[1:7], collapse = "\n"))
+ld_make_chunks(ld)[1:7]
 ```
@@
 
-The first example is simple in part because the ggplot objects both contain the data we want to display and, at the same time, provide the mechanism for presenting them - rendering them in a graph.
+The first example is simple in part because the ggplot objects both contains the data we want to display and, at the same time, provides the mechanism for presenting them - rendering them in a graph.
 However, this is not always the case.
@@
 
-```{r}
+```{r results="as.is"}
 computational_components$Data <- anscombe
 saveRDS(computational_components, "comp-comp.rds")
-cat(paste(ld_make_chunks(ld)[32:36], collapse = "\n"))
+ld_make_chunks(ld)[32:36]
 ```
@@
 This is common, especially when the data set is large and requires too much vertical space in the outputted document resulting in too much or irrelevant data being shown.
-Instead, we would like to output to an html document where the data is shown in a datatable thereby controlling the amount of real-estate needed to present the data and, at the same time, providing the user with interactivity to sort and search the data set.
+Instead, we would like to output to an html document where the data is shown in a `datatable` thereby controlling the amount of real-estate needed to present the data and, at the same time, providing the user with interactivity to sort and search the data set.
 
@@
                decorator = list(data.frame = datatable))
-cat(paste(ld_make_chunks(ld)[33:37], collapse = "\n"))
+
+ld_make_chunks(ld)[33:37]
 ```
@@
   Sepal.Length = list(
-    Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + geom_point(),
-    Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + geom_point(),
+    Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + 
+      geom_point(),
+    Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + 
+      geom_point(),
     Colored = list(
-      Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) + 
-        geom_point(),
-      Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) + 
-        geom_point())))
+      Sepal.Width = ggplot(iris, 
+                          aes(x = Sepal.Length, y = Sepal.Width, 
+                              color = Species)) + geom_point(),
+      Petal.Length = ggplot(iris,
+                            aes(x = Sepal.Length, y = Petal.Length, 
+                                color = Species)) + geom_point())))
 
@@
 
-# R code chunk customization
-
-Along with the basic usage, the \pkg{listdown} package supports two other capabilities to further customize the presentation.
-The first is where custom code is required either to modify decorators or even define a decorators.
-In this case, we would to add a small portion of code, immediately after loading required libraries.
-In the second case, rather than changing the R code inside of a chunk, we would like to change the options for an individual chunk.
-Both of these features are supported in the package and are presented below.
-
-## Initialization code
+# Initialization code
 
@@
 Code is inserted immediately after the libraries are loaded in the R Markdown document.
-In general, it is suggested that the number of initial expressions be kept small so that the R Markdown document is easy to read.
-If a large number of functions are required by the target R Markdown document then they can be put into a file and sourced using the initial expression.
+In general, it is suggested that the number of initial expressions be kept small so that the \proglang{R} Markdown document is easy to read.
+If a large number of functions are required by the target \proglang{R} Markdown document then they can be put into a file and sourced using the initial expression.
 As an example, suppose we are creating an html document and presenting data using the `datatable()` function.
@@
 
-cat(paste(ld_make_chunks(ld)[1:13], collapse = "\n"))
+ld_make_chunks(ld)[2:10]
+```
+
+# R code chunk customization
+
+The \pkg{listdown} package supports also supports capabilities to further customize the presentation by specifying \proglang{R} code chunk options in the \proglang{R} Markdown document in two distinct ways.
+The first is used when the options we would like to specify is tied to type of the object being presented.
+This can be though of as a chunk-option decorator.
+The second is use for changing the options for an individual chunk in an ad-hoc manner.
+
+With three different modes of chunk customization it should be noted that the increasing priority of the chunk options specification is document-wide, decorator-wide, and ad hoc.
+That is, decorator-wide chunk options take priority over document-wide chunk options and ad-hod options take priority over decorator-wide options.
+In addition, it should be noted that the use of the lowest priority scheme that accomplishes the presentation goals is preferred because it lends itself to greater code and maintenance efficiency.
+
+## Controlling options associated with a decorator
+
+The document-wide chunk option specification provides the default chunk options for output documents generated using \pkg{listdown}.
+However, the presentation of a data object often varies by type.
+For example, we may want to specify the height and width of a graph, but not a table.
+This is accomplished in the \pkg{listdown} package when a `listdown` object is created using the `decorator_chunk_opts` option in the `listdown()` function.
+For example, associating all `ggplot` objects with \proglang{R} chunks having a width of 100 and a height of 200 can be accomplished with the following code and it can be seen that only chunk options associated with a plot are modified.
+
+```{r}
+ld <- listdown(load_cc_expr = readRDS("comp-comp2.rds"),
+               package = c("ggplot2", "DT", "purrr"),
+               decorator_chunk_opts = 
+                 list(ggplot = list(fig.width = 100,
+                                    fig.height = 200)),
+               init_expr = {
+                 datatable_no_search <- partial(datatable,
+                                                options = list(dom = 't'))
+                 },
+               echo = FALSE)
+
+ld_make_chunks(ld)[c(12:16, 19:24)]
 ```
@@
 
-Along with providing document-wide chunk options, it is also possible to control individual chunk options
+Along with providing decorator-wide chunk options, it is also possible to control individual chunk options.
+The capability is distinct from the document-wide and decorator-wide specification of options in that it must be applied to the computational component list element whose associated options will be modified, rather than the `listdown` object.
+This is because the `listdown` only specifies how classes of objects should be presented.
+To modify the chunk options associated with a specific list element the list element is provided with a set of attributes that can be queried by the `ld_chunk_opts()` function as the output document is being generated.
+Because of the ad hoc nature of this capability, its use is discouraged.
+A better solution, that maintains the behavior is to add class information to the list element and specify decorator-wide chunk options for the new class.
+This maintains the separation of the computational component list, which maintains the document structure and data for presentation from the specification of how the document will be created and rendered.
 
@@
 saveRDS(comp_comp2, "comp-comp2.rds")
-cat(paste(ld_make_chunks(ld)[1:19], collapse = "\n"))
+ld_make_chunks(ld)[12:16]
 ```
 
-# A simple example: Reporting on the `gtsummary::trial` dataset
-
+# A simple example: Reporting on the gtsummary::trial dataset
 \label{sect:simple-example}
 
-```{r, eval = FALSE}
+As mentioned before, we have found the \pkg{listdown} package particularly helpful for reporting the results of clinical trials thereby creating a basis for discussion and collaboration between (bio)statisticians and the clinicians running the trials.
+For this use case, the context and data collection procedures are well-understood and as a result very few narrative components are needed.
+It is also the case that the modes of presentation (tables, scatterplots, survivalplots, consort diagrams, etc.) are standardized.
+The goal in presenting the trial characteristics is to identify problems in the data, monitor trial enrollment and response, quantify known relationships among the data, and test hypotheses about a therapy's efficacy.
+
+In practice we generally separate the data cleaning, exploration, analysis, monitoring, and presentation components.
+The computational component list has tens of elements with thousands of visualizations.
+These facts, coupled with the privacy constraints make a complete example difficult for the purposes of this paper.
+So, below we provide a simple example of the types of documents we provide using the `gtsummary::trial` dataset.
+While it is not complete, it does convey they types of reports we are currently generating for completed and ongoing clinical trials.
+
+The code creates a computational component list containing a table of the patient characteristics along with survival plots by overall survival, survival by stage, and survival by grade.
+The table is an element of a named list called "Table 1" and then survival plots are elements of named lists indicating the conditioning variable.
+The structure can be seen in the dendrogram below.
+
+```{r, eval = TRUE, message=FALSE, warning=FALSE}
 library(gtsummary)
@@
 # Create the computational components and write to surv-cc.rds.
-make_surv_cc(trial, treat = "trt",
-             surv_cond_chars = c("stage", "grade")) %>%
-  saveRDS("surv-cc.rds")
+surv_cc <- make_surv_cc(trial, treat = "trt",
+                        surv_cond_chars = c("stage", "grade"))
+
+ld_cc_dendro(surv_cc)
+```
+
+As shown before, the report is created by saving the computational components, creating a listdown object, writing the \proglang{R} Markdown document, and rendering it.
+The resulting document, trial-report.html, can then be placed in a shared space where it can be viewed and interpreted by stakeholders in the clincial trial.
+The \proglang{R} Markdown document created by this code is shown in Appendix 1.
+
+```{r eval = FALSE}
+saveRDS(surv_cc, "surv-cc.rds")
 
@@
 ld_surv <- listdown(load_cc_expr = readRDS("surv-cc.rds"),
-                    package = c("gtsummary", "survminer"),
-                    decorator = list(ggsurvplot = identity,
-                                     tbl_summary = identity),
+                    package = c("gtsummary", "survminer", "flextable"),
+                    decorator_chunk_opts = 
+                      list(ggsurvplot = list(fig.width = 100,
+                                             fig.height = 200)),
                     echo = FALSE,
@@
 
-# Render the RMarkdown file to html.
-render("trial-report.rmd", quiet = TRUE, pdf_document(keep_tex = TRUE))  
+# Render the RMarkdown file to html
+render("trial-report.rmd", quiet = TRUE, html_document(keep_tex = TRUE))  
 ```
 
-# Using \pkg{listdown} in practice for clinical trial reporting
+\bibliography{../references}
 
-\pagebreak
-
-# Appendix 1: RMarkdown produced in the simple example
+\section*{Appendix 1: R Markdown produced in the simple example}
+\label{appendix}
 
@@
 
-\```{r echo=FALSE}
+\```{r echo = FALSE, message = FALSE, warning = FALSE}
 library(gtsummary)
 library(survminer)
+library(flextable)
 
@@
 
-\```{r echo=FALSE}
+\```{r echo = FALSE, message = FALSE, warning = FALSE}
 cc_list$`Table 1`
@@
 
-\```{r echo=FALSE}
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
+     fig.height = 4.5}
 cc_list$`Survival Plots`$Overall
@@
 
-\```{r echo=FALSE}
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
+     fig.height = 4.5}
 cc_list$`Survival Plots`$Stage
@@
 
-\```{r echo=FALSE}
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
+     fig.height = 4.5}
 cc_list$`Survival Plots`$Grade
@@
 ```
-
-\pagebreak
-
-# Appendix 2: The document produced by the simple example
-
-\bibliography{RJreferences}

### 2020-06-11 R/chunk-writer.r

@@ -11,7 +11,7 @@
 #' to a decorator function.
 #' @param init_expr an initial expression that will be added to the outputted
 #' document after the libraries have been called.
-#' @param elem_chunk_opts a named list mapping the potential types of list
+#' @param decorator_chunk_opts a named list mapping the potential types of list
 #' elements to chunk options that should be included for those types.
 #' @param default_decorator the decorator to use for list elements whose type
 #' is not inherited from the decorator list. If NULL then the those
@@ -27,7 +27,7 @@ listdown <- function(load_cc_expr,
                      package = NULL,
                      decorator = list(),
                      init_expr = NULL,
-                     elem_chunk_opts = list(),
+                     decorator_chunk_opts = list(),
                      default_decorator = identity,
                      ...,
                      chunk_opts = NULL) {
@@ -49,21 +49,26 @@ listdown <- function(load_cc_expr,
              "\n", sep = ""))
   }
 
-  # Check the chunk options of elem_chunk_opts.
-  for (i in seq_along(elem_chunk_opts)) {
-    not_r_chunk_opts <- not_r_chunk_opts(names(elem_chunk_opts[[i]]))
+  # Check the chunk options of decorator_chunk_opts.
+  for (i in seq_along(decorator_chunk_opts)) {
+    not_r_chunk_opts <- not_r_chunk_opts(names(decorator_chunk_opts[[i]]))
     if (length(not_r_chunk_opts) > 0) {
       stop(red("Unrecognized options for element type",
-               names(elem_chunk_opts)[i], ":\n\t",
+               names(decorator_chunk_opts)[i], ":\n\t",
                paste(not_r_chunk_opts, collapse = "\n\t"),
                "\n", sep = ""))
     }
   }
+  if ( !("decorator" %in% names(match.call())) ) {
+    decorator <- NULL
+  } else {
+    decorator <- as.list(match.call()$decorator)[-1]
+  }
   ret <- list(load_cc_expr = match.call()$load_cc_expr,
-              decorator = as.list(match.call()$decorator)[-1],
+              decorator = decorator,
               package = package,
               init_expr = match.call()$init_expr,
-              elem_chunk_opts = elem_chunk_opts,
+              decorator_chunk_opts = decorator_chunk_opts,
               default_decorator = default_decorator,
               chunk_opts = chunk_opts)
 
@@ -117,7 +122,7 @@ ld_make_chunks.listdown <- function(ld) {
[…]

### 2020-06-11 R/depth-first-pres-list-visitor.r

@@ -103,7 +103,7 @@ depth_first_concat <- function(cc_list, ld, heading = "#",
       chunk_opts <- ld$chunk_opts
 
       chunk_option_index <- which(
-        vapply(names(ld$elem_chunk_opts),
+        vapply(names(ld$decorator_chunk_opts),
                function(x) inherits(eval(parse(text = pl)), x), NA))
 
       if (length(chunk_option_index) > 1) {
@@ -113,7 +113,7 @@ depth_first_concat <- function(cc_list, ld, heading = "#",
       }
 
       if (length(chunk_option_index) == 1) {
-        new_chunk_opts <- ld$elem_chunk_opts[[chunk_option_index]]
+        new_chunk_opts <- ld$decorator_chunk_opts[[chunk_option_index]]
         for (i in seq_along(new_chunk_opts)) {
           chunk_opts[[names(new_chunk_opts)[i]]] <- new_chunk_opts[[i]]
         }

### 2020-06-11 R/ld-write-file.r

@@ -10,7 +10,7 @@
 #' output.
 #' @param file_name the output file to write to.
 #' @examples
-#' \donttest{
+#' \dontrun{
 #' library(ggplot2)
 #'
 #' cc_list <- list(

### 2020-06-11 tests/testthat/test-add-chunk-elem-option.r

@@ -1,4 +1,4 @@
-context("Chunk Element Option")
+context("Decorator Chunk Option")
 
 source("make-reference.r")
 
@@ -9,27 +9,28 @@ if (make_reference) {
 pres_list <- list(iris = iris,
                   mtcars = mtcars)
 
-saveRDS(pres_list, "reference-data/option-element-check.rds")
+saveRDS(pres_list, "reference-data/option-chunk-check.rds")
 
 expect_error(
   listdown(readRDS("reference-data/option-check.rds"),
            package = "knitr",
            decorator = list(data.frame = kable),
-           elem_chunk_opts =
+           decorator_chunk_opts =
              list(data.frame = list("test_chunk", bunk = FALSE))))
 
 ld <- listdown(readRDS("reference-data/option-check.rds"),
                package = "knitr",
                decorator = list(data.frame = kable),
-               elem_chunk_opts =
+               decorator_chunk_opts =
                  list(data.frame = list("test_chunk", echo = FALSE,
                                         results = "as.is")))
 
 
 if (make_reference) {
   saveRDS(ld_make_chunks(ld),
-          file.path("reference-data", "chunk-elem-option-1.rds"))
+          file.path("reference-data", "chunk-decorator-option-1.rds"))
 }
 
 expect_equal(ld_make_chunks(ld),
-             readRDS(file.path("reference-data", "chunk-elem-option-1.rds")))
+             readRDS(file.path("reference-data", 
+                               "chunk-decorator-option-1.rds")))

### 2020-06-23 inst/jss/kane-listdown/supplemental-material/kane-listdown.Rmd
JSS paper supp-materials.

@@
     email: michael.kane@yale.edu
+  - name: Simon Urbanek
+    affiliation: The University of Aukland
+    address:
+    - 38 Princes Street
+    - Auckland Central, Aukland 1010, NZ
+    email: s.urbanek@auckland.ac.nz
 title:
@@
 
-Since computational components are, by definition, computationally derived objects and R Markdown is a well-defined standard, it is possible to programmatically create \proglang{R} Markdown documents with computational components, which is the focus of this paper.
-However, before proceeding down this avenue, we would like to highlight two fundamental limitations to automated R Markdown document construction.
-First and foremost, without narrative components a document has very little context.
-Quantitative analyses require research questions, hypotheses, reviews, interpretations, and conclusions.
-Computational components are necessary but generally not sufficient for constructing an analysis.
-Second, it is difficult if not impossible to construct computational components for an arbitary analyses.
-Analyses themselves have context and are built with a set of assumptions and goals.
-
-This is not to say the programmatic creation of \proglang{R} Markdown documents is unwarranted or not useful.
-In fact, it has at least two appealing characteristics.
+Since computational components are, by definition, computationally derived objects and \proglang{R} Markdown is a well-defined standard, it is possible to programmatically create \proglang{R} Markdown documents with computational components, which is the focus of this paper.
+Generating documents in this manner has two appealing characteristics.
 First, it allows us to distinguish the presentation of analytical results from other steps in a data science or data processing pipeline.
@@
 Section 4 goes over advanced usage of the package including adding initialization code to and outputted document as well as how to control chunk-level options.
-Section 5 concludes the paper with a few final remarks.
+Section 5 provides a simplified case study of how the package is currently being used in clinical trial reporting.
+Section 6 concludes the paper with a few final remarks on the general types of applications where \pkg{listdown} has been shown effective.
 
@@
 doc <- c(
-  unlist(strsplit(as.character(ld_rmarkdown_header("Anscombe's Quartet",
+  as.character(ld_rmarkdown_header("Anscombe's Quartet",
                                    author = "Francis Anscombe",
                                    date = "1973")),
-                  "\n", fixed = TRUE)),
   ld_make_chunks(ld))
@@
 
-# Initialization code
+# Advanced usage
+
+## Initialization code
 
@@
 
-# R code chunk customization
+## R code chunk customization
 
@@
 library(dplyr)
-library(glue)
 library(survival)
@@
                 function(sc) {
-                  glue("Surv(ttdeath, death) ~ {treat} + {sc}") %>%
+                  sprintf("Surv(ttdeath, death) ~ %s + %s", treat, sc) %>%
                     as.formula() %>%
@@
 
-```{r eval = FALSE}
+```{r eval = TRUE, message = FALSE, warning = FALSE}
+# Turn the survplots into a list to show the individual components.
+class(surv_cc$`Survival Plots`$Overall) <- 
+  class(surv_cc$`Survival Plots`$Stage) <-
+  class(surv_cc$`Survival Plots`$Grade) <- "list"
+
+# Create a tab for each element of the survplot.
+names(surv_cc$`Survival Plots`) <- 
+  paste(names(surv_cc$`Survival Plots`), "{.tabset}")
+
+# Rename the elements
+names(surv_cc$`Survival Plots`$`Overall {.tabset}`) <- 
+  names(surv_cc$`Survival Plots`$`Stage {.tabset}`) <- 
+  names(surv_cc$`Survival Plots`$`Grade {.tabset}`) <- 
+  c("Plot", "Data", "Table")
+
+# Save the updated object for presentation.
 saveRDS(surv_cc, "surv-cc.rds")
@@
 ld_surv <- listdown(load_cc_expr = readRDS("surv-cc.rds"),
-                    package = c("gtsummary", "survminer", "flextable"),
+                    package = c("gtsummary", "flextable", "DT", 
+                                "ggplot2"),
                     decorator_chunk_opts = 
-                      list(ggsurvplot = list(fig.width = 100,
-                                             fig.height = 200)),
+                      list(gg = list(fig.width = 8,
+                                     fig.height = 6)),
+                    decorator = list(data.frame = datatable),
                     echo = FALSE,
@@
 
-# Render the RMarkdown file to html
-render("trial-report.rmd", quiet = TRUE, html_document(keep_tex = TRUE))  
+# Render the RMarkdown file to html and show it.
+render("trial-report.rmd", quiet = TRUE)
+browseURL("trial-report.html")
+
 ```
+
+# Conclusion
+
+While the programmtic generation of reproducible documents has appealing qualities, it also has fundamental limitations that should be kept in mind when deciding if tools like \pkg{listdown} should be employed.
+First and foremost, without narrative components a document has very little context.
+Quantitative analyses require research questions, hypotheses, reviews, interpretations, and conclusions.
+Computational components are necessary but generally not sufficient for constructing an analysis.
+This means that if narrative components must be conveyed in a document, then \pkg{listdown} may make the generation of their presentation more convenient.
+However, it does not relieve the burden of the author to create prose developing a narrative.
+
+Second, it is difficult if not impossible to construct computational components for an arbitary analyses.
+Analyses themselves have context and are built with a set of assumptions and goals.
+Our experience shows that \pkg{listdown} is easiest to used for a fixed data format.
+This means a standard set of table and visualizations for similarly formatted data.
+In particular, data that is periodicaly updated, without changes to the format, is a case that is particularly amenable to document generation reuse.
+
+Keeping these limitations in mind, \pkg{listdown} can be used to effectively reduce the the difficulty of generating documents in a variety of contexts and fits readily in data processing and analysis pipelines.
 
@@
 
-\```{r echo = FALSE, message = FALSE, warning = FALSE}
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
 library(gtsummary)
-library(survminer)
 library(flextable)
+library(DT)
+library(ggplot2)
 
@@
 
-\```{r echo = FALSE, message = FALSE, warning = FALSE}
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
 cc_list$`Table 1`
@@
 
-## Overall
+## Overall {.tabset}
 
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-     fig.height = 4.5}
-cc_list$`Survival Plots`$Overall
+### Plot
+
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 6}
+cc_list$`Survival Plots`$`Overall {.tabset}`$Plot
 \```
 
-## Stage
+### Data
 
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-     fig.height = 4.5}
-cc_list$`Survival Plots`$Stage
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+datatable(cc_list$`Survival Plots`$`Overall {.tabset}`$Data)
 \```
 
-## Grade
+### Table
 
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-     fig.height = 4.5}
-cc_list$`Survival Plots`$Grade
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+datatable(cc_list$`Survival Plots`$`Overall {.tabset}`$Table)
+\```
+
+## Stage {.tabset}
+
+### Plot
+
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 6}
+cc_list$`Survival Plots`$`Stage {.tabset}`$Plot
+\```
+
+### Data
+
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+datatable(cc_list$`Survival Plots`$`Stage {.tabset}`$Data)
+\```
+
+### Table
+
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+datatable(cc_list$`Survival Plots`$`Stage {.tabset}`$Table)
+\```
+
+## Grade {.tabset}
+
+### Plot
+
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 6}
+cc_list$`Survival Plots`$`Grade {.tabset}`$Plot
+\```
+
+### Data
+
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+datatable(cc_list$`Survival Plots`$`Grade {.tabset}`$Data)
+\```
+
+### Table
+
+\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+datatable(cc_list$`Survival Plots`$`Grade {.tabset}`$Table)
 \```

### 2020-06-23 R/headers.r

@@ -50,7 +50,7 @@ print.listdown_header <- function(x, ...) {
 #' @export
 #' @importFrom yaml as.yaml
 as.character.listdown_header <- function(x, ...) {
-  paste0("---\n",
-         as.yaml(x, ...),
-         "---", collapse = "\n")
+  c("---",
+    unlist(strsplit(as.yaml(x, ...), "\n")),
+    "---")
 }

### 2020-06-23 tests/testthat/test-headers.r

@@ -9,6 +9,9 @@ if (make_reference) {
   dir.create("reference-data", showWarnings = FALSE)
 }
 
+as.character(ld_rmarkdown_header("Workflow R", author = "Some Dude",
+                              date = "2020"))
+
 if (make_reference) {
   saveRDS(ld_rmarkdown_header("Workflow R", author = "Some Dude",
                               date = "2020"),

### 2020-06-23 inst/jss/kane-listdown/listdown-jss.tex
Renaming.

--- 2020-06-11 inst/jss/kane-listdown/supplemental-material/kane-listdown.Rmd
@@
----
-documentclass: jss
-author:
-  - name: Michael Kane
-    affiliation: Yale University
-    address:
-    - 60 College Street
-    - New Haven, CT 06510, USA
-    email:  michael.kane@yale.edu
-title:
-  formatted: "On the Programmatic Generation of Reproducible Documents"
-  # If you use tex in the formatted title, also supply version without
-  plain:     "On the Programmatic Generation of Reproducible Documents"
-  # For running headers, if needed
-  short:     "On the Programmatic Generation of Reproducible Documents"
-abstract: >
-  Reproducible document standards, like \proglang{R} Markdown, facilitate the programmatic creation of documents whose content is itself programmatically generated.
-While these documents are generally not complete in the sense that they will not include prose content, generated by an author to provide context, a narrative, etc., programmatic generation can provide substantial efficiencies for structuring and constructing documents.
-This paper explores the programmatic generation of reproducible by distinguishing components than can be created by computational means from those requiring human-generated prose, providing guidelines for the generation of these documents, and identifying a use case in clinical trial reporting.
-These concepts and use case are illustrated through the \pkg{listdown} package for the \proglang{R} programming environment, which is is currently available on the Comprehensive R Archive Network (CRAN).
-keywords:
-  # at least one keyword must be supplied
-  formatted: [reproducibility, reproducible documents, data presentation]
-  plain:     [reproducibility, reproducible documents, data presentation]
-preamble: >
+\documentclass[
+]{jss}
+
+\usepackage[utf8]{inputenc}
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\author{
+Michael Kane\\Yale University
+}
+\title{On the Programmatic Generation of Reproducible Documents}
+
+\Plainauthor{Michael Kane}
+\Plaintitle{On the Programmatic Generation of Reproducible Documents}
+\Shorttitle{Programmatic Generation of Reproducible Documents}
+
+\Abstract{
+The abstract of the article.
+}
+
+\Keywords{reproducibility, reproducible documents, data presentation}
+\Plainkeywords{reproducibility, reproducible documents, data
+presentation}
+
+%% publication information
+%% \Volume{50}
+%% \Issue{9}
+%% \Month{June}
+%% \Year{2012}
+%% \Submitdate{}
+%% \Acceptdate{2012-06-04}
+
+\Address{
+    Michael Kane\\
+  Yale University\\
+  60 College StreetNew Haven, CT 06510, USA\\
+  E-mail: \href{mailto:michael.kane@yale.edu}{\nolinkurl{michael.kane@yale.edu}}\\
+
+  }
+
+% Pandoc header
+
 \usepackage{amsmath}
-output: rticles::jss_article
----
 
-# Background and concepts
+\begin{document}
 
-\proglang{R} Markdown [@baumer2014] facilitates the construction of computationally reproducible documents by allowing authors to insert \proglang{R} code for data processing, exploration, analysis, table-making, and visualization directly into structured, electronic documents.
-The resulting documents are made up of these chunks of \proglang{R} code, which we will refer to as _computational components_ since they are generated by computational means, as well as _narrative components_, which (in scientific writing) is prose intended to contextualize computational components, provide background, define goals, establish themes, and convey the results of the document.
-The integration of narrative and computational components was identified as "Literate Programming" by @knuth1984 and software tools, like Sweave [@leisch2002], have supported this functionality for almost two decades.
+\hypertarget{background-and-concepts}{%
+\section{Background and concepts}\label{background-and-concepts}}
 
-\proglang{R} Markdown is particularly popular with its success likely being driven by two factors.
-The first is the relative ease with which these documents can be constructed.
-While \LaTeX \ is more expressive, it is relatively technical and requires an investment in time to become proficient.
-By contrast \proglang{R} Markdown documents are easier to create and format and, when the document is used to create \LaTeX, formatting can be passed through to the underlying .tex file.
-The second factor driving adoption is likely its support for creating _modifiable_ documents, namely Microsoft Word documents.
-Researchers and analysts, especially those creating applied statistical analyses, often collaborate with domain experts with less technical knowledge.
-In these cases, the analyst focuses on creating the computational components and narrative components related to results and interpretation.
-After this initial document is created, the domain expert is free to develop narrative components directly in the document without needing to go through the analyst.
+\proglang{R} Markdown \citep{baumer2014} facilitates the construction of
+computationally reproducible documents by allowing authors to insert
+\proglang{R} code for data processing, exploration, analysis,
+table-making, and visualization directly into structured, electronic
+documents. The resulting documents are made up of these chunks of
+\proglang{R} code, which we will refer to as \emph{computational
+components} since they are generated by computational means, as well as
+\emph{narrative components}, which (in scientific writing) is prose
+intended to contextualize computational components, provide background,
+define goals, establish themes, and convey the results of the document.
+The integration of narrative and computational components was identified
+as ``Literate Programming'' by \citet{knuth1984} and software tools,
+like Sweave \citep{leisch2002}, have supported this functionality for
+almost two decades.
 
-Since computational components are, by definition, computationally derived objects and R Markdown is a well-defined standard, it is possible to programmatically create \proglang{R} Markdown documents with computational components, which is the focus of this paper.
-However, before proceeding down this avenue, we would like to highlight two fundamental limitations to automated R Markdown document construction.
-First and foremost, without narrative components a document has very little context.
-Quantitative analyses require research questions, hypotheses, reviews, interpretations, and conclusions.
-Computational components are necessary but generally not sufficient for constructing an analysis.
-Second, it is difficult if not impossible to construct computational components for an arbitary analyses.
-Analyses themselves have context and are built with a set of assumptions and goals.
+\proglang{R} Markdown is particularly popular with its success likely
+being driven by two factors. The first is the relative ease with which
+these documents can be constructed. While \LaTeX ~is more expressive, it
+is relatively technical and requires an investment in time to become
+proficient. By contrast \proglang{R} Markdown documents are easier to
+create and format and, when the document is used to create \LaTeX,
+formatting can be passed through to the underlying .tex file. The second
+factor driving adoption is likely its support for creating
+\emph{modifiable} documents, namely Microsoft Word documents.
+Researchers and analysts, especially those creating applied statistical
+analyses, often collaborate with domain experts with less technical
+knowledge. In these cases, the analyst focuses on creating the
+computational components and narrative components related to results and
+interpretation. After this initial document is created, the domain
+expert is free to develop narrative components directly in the document
+without needing to go through the analyst.
 
-This is not to say the programmatic creation of \proglang{R} Markdown documents is unwarranted or not useful.
-In fact, it has at least two appealing characteristics.
-First, it allows us to distinguish the presentation of analytical results from other steps in a data science or data processing pipeline.
-These other steps including cleaning and analysis often require their own environment and configuration with requirements very different than the computational needs of creating a presentation.
-By separating these components each can be developed independently.
-At the same time, by specifying a contract for the output of those objects, we can establish a consistent means by which processed data can be passed to systems for presentating those data in a structured way.
-The second reason for programmatic creation of R Markdown documents is convenience.
-In collaborative environments, especially in the early stages, large numbers of graphs and tables are generated and discussed.
-By collecting these artifacts and structuring them consistently, we can quickly iterate upon and restructure the resulting documents to more clearly present the data without needing to spend time on the creation of the presentation document.
+Since computational components are, by definition, computationally
+derived objects and R Markdown is a well-defined standard, it is
+possible to programmatically create \proglang{R} Markdown documents with
+computational components, which is the focus of this paper. However,
+before proceeding down this avenue, we would like to highlight two
+fundamental limitations to automated R Markdown document construction.
+First and foremost, without narrative components a document has very
+little context. Quantitative analyses require research questions,
+hypotheses, reviews, interpretations, and conclusions. Computational
+components are necessary but generally not sufficient for constructing
+an analysis. Second, it is difficult if not impossible to construct
+computational components for an arbitary analyses. Analyses themselves
+have context and are built with a set of assumptions and goals.
 
-The \pkg{listdown} package provides functions to programmatically create \proglang{R} Markdown files from named lists. It is intended for data analysis pipelines where the presentation of the results
-is separated from their creation. For this use case, a data processing (or analysis) is performed
-and the results are provided in a single named list, organized heirarchically.
-List element names denote sections, subsections, subsubsection, etc.
-and the list elements contain the data structure to be presented including graphs and tables.
-The package has native support for \pkg{workflowr} [@blischak2019], pdf, word, or html document along with functions allowing a user to easily extend to other types of supported documents.
-The goal of the package is to create a documents with all tables and visualization that will appear (computational components).
-This serves as a starting point from which a user can organize outputs, describe a study, discuss results, and provide conclusions (narrative components).
+This is not to say the programmatic creation of \proglang{R} Markdown
+documents is unwarranted or not useful. In fact, it has at least two
+appealing characteristics. First, it allows us to distinguish the
+presentation of analytical results from other steps in a data science or
+data processing pipeline. These other steps including cleaning and
+analysis often require their own environment and configuration with
+requirements very different than the computational needs of creating a
+presentation. By separating these components each can be developed
+independently. At the same time, by specifying a contract for the output
+of those objects, we can establish a consistent means by which processed
+data can be passed to systems for presentating those data in a
+structured way. The second reason for programmatic creation of R
+Markdown documents is convenience. In collaborative environments,
+especially in the early stages, large numbers of graphs and tables are
+generated and discussed. By collecting these artifacts and structuring
+them consistently, we can quickly iterate upon and restructure the
+resulting documents to more clearly present the data without needing to
+spend time on the creation of the presentation document.
 
-\pkg{listdown} therefore provides a reproducible means for producing a document with specified computational components.
-It is most compatible with data analysis pipelines where the data format is fixed but the analyses are either being updated, which may affect narrative components including the result discussion and conclusion, or where the experiment is different, which affects all narrative components, but the data format and processing is consistent.
-An example of the former is provided later in this paper.
+The \pkg{listdown} package provides functions to programmatically create
+\proglang{R} Markdown files from named lists. It is intended for data
+analysis pipelines where the presentation of the results is separated
+from their creation. For this use case, a data processing (or analysis)
+is performed and the results are provided in a single named list,
+organized heirarchically. List element names denote sections,
+subsections, subsubsection, etc. and the list elements contain the data
+structure to be presented including graphs and tables. The package has
+native support for \pkg{workflowr} \citep{blischak2019}, pdf, word, or
+html document along with functions allowing a user to easily extend to
+other types of supported documents. The goal of the package is to create
+a documents with all tables and visualization that will appear
+(computational components). This serves as a starting point from which a
+user can organize outputs, describe a study, discuss results, and
+provide conclusions (narrative components).
 
-One area where we have found \pkg{listdown} is particuarly useful is in the reporting and research of clinical trial data.
-These collaborations tend to be between (bio)statisticians and clinicians either analyzing past trial data to formulate a new trial or in trial monitoring where trial telemetry (enrollment, responses, etc.) is reported and initial analyses are conveyed to a clinician.
-The associated presentations require very little context - clinicians often have a better understanding of the data collected than the statistician - often eliminating the need for narrative components.
-At the same time, a large number of hierarchical, heterogenous artifacts (tables and multiple types of plots) need to be conveyed thereby making the manual creation of \proglang{R} Markdown documents inconvenient.
+\pkg{listdown} therefore provides a reproducible means for producing a
+document with specified computational components. It is most compatible
+with data analysis pipelines where the data format is fixed but the
+analyses are either being updated, which may affect narrative components
+including the result discussion and conclusion, or where the experiment
+is different, which affects all narrative components, but the data
+format and processing is consistent. An example of the former is
+provided later in this paper.
 
-In this case, data presentation can be fixed across trials.
-This is especially true in the initial stages, which focus on patient demographics and enrollment.
-This approach has made it convenient for our group to quickly generate standardize and complete reports for multiple trials concurrently.
-To date, we have used listdown to report on five clinical trials, with another two currently in process.
-Results are disseminated using the \pkg{workflowr} package, usually with nine tabs conveying aspects of the data from collection through several different analyses, and each tab containing approxiately five to thirty tables, plots, or other artifacts including \pkg{trelliscopejs} [@trelliscopejs] environments which may hold hundreds of graphs.
-By generating many presentation artifacts we are able to address data-drive questions and issues during collaborative sessions and by carefully structuring these elements we allowing all members to participate in the process.
+One area where we have found \pkg{listdown} is particuarly useful is in
+the reporting and research of clinical trial data. These collaborations
+tend to be between (bio)statisticians and clinicians either analyzing
+past trial data to formulate a new trial or in trial monitoring where
+trial telemetry (enrollment, responses, etc.) is reported and initial
+analyses are conveyed to a clinician. The associated presentations
+require very little context - clinicians often have a better
+understanding of the data collected than the statistician - often
+eliminating the need for narrative components. At the same time, a large
+number of hierarchical, heterogenous artifacts (tables and multiple
+types of plots) need to be conveyed thereby making the manual creation
+of \proglang{R} Markdown documents inconvenient.
 
-The \pkg{listdown} package itself is relatively simple with 6 distinct methods that can be easily incorporated into existing analysis pipelines for automatically creating documents that can be used for data exploration and reviewing analysis results as well as a starting point for a more formal write up.
-These methods include:
+In this case, data presentation can be fixed across trials. This is
+especially true in the initial stages, which focus on patient
+demographics and enrollment. This approach has made it convenient for
+our group to quickly generate standardize and complete reports for
+multiple trials concurrently. To date, we have used listdown to report
+on five clinical trials, with another two currently in process. Results
+are disseminated using the \pkg{workflowr} package, usually with nine
+tabs conveying aspects of the data from collection through several
+different analyses, and each tab containing approxiately five to thirty
+tables, plots, or other artifacts including \pkg{trelliscopejs}
+\citep{trelliscopejs} environments which may hold hundreds of graphs. By
+generating many presentation artifacts we are able to address data-drive
+questions and issues during collaborative sessions and by carefully
+structuring these elements we allowing all members to participate in the
+process.
+
+The \pkg{listdown} package itself is relatively simple with 6 distinct
+methods that can be easily incorporated into existing analysis pipelines
+for automatically creating documents that can be used for data
+exploration and reviewing analysis results as well as a starting point
+for a more formal write up. These methods include:
 
@@
 
-The rest of this paper is structured as follow.
-The next section goes over basic usage and commentary.
-This section is meant to convey the basic approach used by the package and shows how to describe an output document using \pkg{listdown}, create a document, and change how the presentation of computational components can be specialized using \pkg{listdown} decorators.
-With the user accustomed to the package's basic usage, section 3 describes the design of the package.
-Section 4 goes over advanced usage of the package including adding initialization code to and outputted document as well as how to control chunk-level options.
-Section 5 concludes the paper with a few final remarks.
+The rest of this paper is structured as follow. The next section goes
+over basic usage and commentary. This section is meant to convey the
+basic approach used by the package and shows how to describe an output
+document using \pkg{listdown}, create a document, and change how the
+presentation of computational components can be specialized using
+\pkg{listdown} decorators. With the user accustomed to the package's
+basic usage, section 3 describes the design of the package. Section 4
+goes over advanced usage of the package including adding initialization
+code to and outputted document as well as how to control chunk-level
+options. Section 5 concludes the paper with a few final remarks.
 
-# Basic usage and overview
+\hypertarget{basic-usage-and-overview}{%
+\section{Basic usage and overview}\label{basic-usage-and-overview}}
 
-Suppose we have just completed and analysis and have collected all of the results into a list where the list elements are roughly in the order we would like to present them in a document.
-It may be noted that this is not always how computational components derived from data analyses are collated.
-Often individual components are stored in multiple locations on a single machine or across machines.
-However, it is important to realize that even for analyses on large-scale data, the digital artifacts to be presented are relatively small.
-Centralizing them makes it easier to access them, since they don't need to be found in mulitple locations.
-Also, storing them as a list provides a hierarchical structure that translates directly to a document as we will see below.
+Suppose we have just completed and analysis and have collected all of
+the results into a list where the list elements are roughly in the order
+we would like to present them in a document. It may be noted that this
+is not always how computational components derived from data analyses
+are collated. Often individual components are stored in multiple
+locations on a single machine or across machines. However, it is
+important to realize that even for analyses on large-scale data, the
+digital artifacts to be presented are relatively small. Centralizing
+them makes it easier to access them, since they don't need to be found
+in mulitple locations. Also, storing them as a list provides a
+hierarchical structure that translates directly to a document as we will
+see below.
 
-As a first example, we will consider the a list of visualizations from the anscombe data set.
-The list is composed of four \pkg{ggplot2} [@wickham2016]elements (named Linear, Non Linear, Outlier Vertical, and Outlier Horizontal) each containing a scatter plot from the famous Anscome Quartet - made available in the \pkg{datasets} package [@R].
-From the `computational_components` list, we would like to create a document with four sections with names corresponding to the list names, each containing their respective visualizations.
+As a first example, we will consider the a list of visualizations from
+the anscombe data set. The list is composed of four \pkg{ggplot2}
+\citep{wickham2016}elements (named Linear, Non Linear, Outlier Vertical,
+and Outlier Horizontal) each containing a scatter plot from the famous
+Anscome Quartet - made available in the \pkg{datasets} package
+\citep{R}. From the \texttt{computational\_components} list, we would
+like to create a document with four sections with names corresponding to
+the list names, each containing their respective visualizations.
 
-```{r}
-# Use ggplot2 to create the visualizations.
-library(ggplot2)
+\begin{CodeChunk}
 
-# Load the Anscombe Quartet.
-data(anscombe)
+\begin{CodeInput}
+R> # Use ggplot2 to create the visualizations.
+R> library(ggplot2)
+R> 
+R> # Load the Anscombe Quartet.
+R> data(anscombe)
+R> 
+R> # Create the ggplot objects to display.
+R>   computational_components <- list(
+R+     Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+R+     `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
+R+     `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + 
+R+       geom_point(),
+R+     `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + 
+R+       geom_point())
+R> 
+R> # Save the file to disk to be read by the output R Markdown document.
+R> saveRDS(computational_components, "comp-comp.rds")
+\end{CodeInput}
+\end{CodeChunk}
 
-# Create the ggplot objects to display.
-  computational_components <- list(
-    Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
-    `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
-    `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + 
-      geom_point(),
-    `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + 
-      geom_point())
+\hypertarget{creating-a-document-with-listdown}{%
+\subsection{Creating a document with
+listdown}\label{creating-a-document-with-listdown}}
 
-# Save the file to disk to be read by the output R Markdown document.
-saveRDS(computational_components, "comp-comp.rds")
-```
+Creating a document from the \texttt{computational\_components} requires
+two steps. First, we will create a \texttt{listdown} object that
+specifies how the \texttt{computational\_components} object will be
+loaded into the document, which libraries and code needs to be included,
+and how the list elements will be presented in the output R markdown
+document.
 
-## Creating a document with listdown
+\begin{CodeChunk}
 
-Creating a document from the `computational_components` requires two steps.
-First, we will create a `listdown` object that specifies how the `computational_components` object will be loaded into the document,  which libraries and code needs to be included, and how the list elements will be presented in the output R markdown document.
+\begin{CodeInput}
+R> library(listdown)
+R> 
+R> ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"),
+R+                package = "ggplot2")
+\end{CodeInput}
+\end{CodeChunk}
 
-```{r}
-library(listdown)
+The \texttt{ld} object, along with the computational components in the
+\texttt{comp-comp.rds} file are sufficient to to create the sections,
+subsections, and R chunks of a document. The only other thing requires
+to create the document is the header. The listdown package currently
+supports regular R Markdown and \pkg{workflowr} as \code{yml} objects
+from the \pkg{yaml} package \citep{yaml}. These objects are stored as
+named lists in R and are easily modified to accomodate document
+parameters. A complete document can then be written to the console using
+the code shown below. It could easily be written to a file for rendering
+using the \texttt{writeLines()} function.
 
-ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"),
-               package = "ggplot2")
-```
+\begin{CodeChunk}
 
-The `ld` object, along with the computational components in the `comp-comp.rds` file are sufficient to to create the sections, subsections, and R chunks of a document.
-The only other thing requires to create the document is the header.
-The listdown package currently supports regular R Markdown and \pkg{workflowr} as \code{yml} objects from the \pkg{yaml} package [@yaml].
-These objects are stored as named lists in R and are easily modified to accomodate document parameters.
-A complete document can then be written to the console using the code shown below.
-It could easily be written to a file for rendering using the `writeLines()` function.
+\begin{CodeInput}
+R> doc <- c(
+R+   unlist(strsplit(as.character(ld_rmarkdown_header("Anscombe's Quartet",
+R+                                author = "Francis Anscombe",
+R+                                date = "1973")),
+R+                   "\n", fixed = TRUE)),
+R+   ld_make_chunks(ld))
+R> 
+R> doc
+\end{CodeInput}
 
-```{r}
-doc <- c(
-  unlist(strsplit(as.character(ld_rmarkdown_header("Anscombe's Quartet",
-                               author = "Francis Anscombe",
-                               date = "1973")),
-                  "\n", fixed = TRUE)),
-  ld_make_chunks(ld))
+\begin{CodeOutput}
+ [1] "---"                                  
+ [2] "title: Anscombe's Quartet"            
+ [3] "author: Francis Anscombe"             
+ [4] "date: '1973'"                         
+ [5] "output: html_document"                
+ [6] "---"                                  
+ [7] ""                                     
+ [8] "```{r}"                               
+ [9] "library(ggplot2)"                     
+[10] ""                                     
+[11] "cc_list <- readRDS(\"comp-comp.rds\")"
+[12] "```"                                  
+[13] ""                                     
+[14] "# Linear"                             
+[15] ""                                     
+[16] "```{r}"                               
+[17] "cc_list$Linear"                       
+[18] "```"                                  
+[19] ""                                     
+[20] "# Non Linear"                         
+[21] ""                                     
+[22] "```{r}"                               
+[23] "cc_list$`Non Linear`"                 
+[24] "```"                                  
+[25] ""                                     
+[26] "# Outlier Vertical"                   
+[27] ""                                     
+[28] "```{r}"                               
+[29] "cc_list$`Outlier Vertical`"           
+[30] "```"                                  
+[31] ""                                     
+[32] "# Outlier Horizontal"                 
+[33] ""                                     
+[34] "```{r}"                               
+[35] "cc_list$`Outlier Horizontal`"         
+[36] "```"                                  
+\end{CodeOutput}
+\end{CodeChunk}
 
-doc
-```
+The \texttt{listdown()} function provides \emph{document-wide} R chunk
+options for displaying computational components. The chunk options are
+exactly the same as those in the R markdown document and can be used to
+tailor the default presentation for a variety of needs. The complete set
+of options can be found in the R Markdown Reference Guide
+\citep{rmarkdownref}. As a concrete example, the code used to create
+present the plots could be hidden in the output document using the
+following code.
 
-The `listdown()` function provides _document-wide_ R chunk options for displaying computational components.
-The chunk options are exactly the same as those in the R markdown document and can be used to tailor the default presentation for a variety of needs.
-The complete set of options can be found in the R Markdown Reference Guide [@rmarkdownref].
-As a concrete example, the code used to create present the plots could be hidden in the output document using the following code.
+\begin{CodeChunk}
 
-```{r}
-ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
-               package = "ggplot2",
-               echo = FALSE)
+\begin{CodeInput}
+R> ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
+R+                package = "ggplot2",
+R+                echo = FALSE)
+R> 
+R> #cat(paste(ld_make_chunks(ld)[1:7], collapse = "\n"))
+R> ld_make_chunks(ld)[1:7]
+\end{CodeInput}
 
-#cat(paste(ld_make_chunks(ld)[1:7], collapse = "\n"))
-ld_make_chunks(ld)[1:7]
-```
+\begin{CodeOutput}
+[1] ""                                     
+[2] "```{r echo = FALSE}"                  
+[3] "library(ggplot2)"                     
+[4] ""                                     
+[5] "cc_list <- readRDS(\"comp-comp.rds\")"
+[6] "```"                                  
+[7] ""                                     
+\end{CodeOutput}
+\end{CodeChunk}
 
-## Decorators
+\hypertarget{decorators}{%
+\subsection{Decorators}\label{decorators}}
 
-The first example is simple in part because the ggplot objects both contains the data we want to display and, at the same time, provides the mechanism for presenting them - rendering them in a graph.
-However, this is not always the case.
-The objects being stored in the list of computational components may not translate directly to the presentation in a document.
-In these cases, a function is needed that takes the list component and returns an object to be displayed.
-For example, suppose that, along with showing graphs from the Anscombe Quartet, we would like to include the data themselves.
-We could add the data to the `computational_components` list and then create the document with:
+The first example is simple in part because the ggplot objects both
+contains the data we want to display and, at the same time, provides the
+mechanism for presenting them - rendering them in a graph. However, this
+is not always the case. The objects being stored in the list of
+computational components may not translate directly to the presentation
+in a document. In these cases, a function is needed that takes the list
+component and returns an object to be displayed. For example, suppose
+that, along with showing graphs from the Anscombe Quartet, we would like
+to include the data themselves. We could add the data to the
+\texttt{computational\_components} list and then create the document
+with:
 
-```{r results="as.is"}
-computational_components$Data <- anscombe
-saveRDS(computational_components, "comp-comp.rds")
-ld_make_chunks(ld)[32:36]
-```
+\begin{CodeChunk}
 
-In this case, the \pkg{listdown} package will show the entire data set as is the default specified.
-However, suppose we do not want to show the entire data set in the document.
-This is common, especially when the data set is large and requires too much vertical space in the outputted document resulting in too much or irrelevant data being shown.
-Instead, we would like to output to an html document where the data is shown in a `datatable` thereby controlling the amount of real-estate needed to present the data and, at the same time, providing the user with interactivity to sort and search the data set.
+\begin{CodeInput}
+R> computational_components$Data <- anscombe
+R> saveRDS(computational_components, "comp-comp.rds")
+R> ld_make_chunks(ld)[32:36]
+\end{CodeInput}
 
-In \pkg{listdown}, a function or method that implements the presentation of a computational component is referred to as a _decorator_ since if follows the classic decorator pattern described in @gamma1995.
-A decorator takes the element that will be presented as an argument and returns an object for presentation in the output directory.
-A decorator is specified using the `decorator` parameter of the `listdown()` function using a named list where the name corresponds to the type and the element correspond to the function or method that will decorate an object of that type.
-For example, the `anscombe` data set can be decorated with the `DT::datatable()` function [@xie2020] as:
+\begin{CodeOutput}
+[1] "# Data"              
+[2] ""                    
+[3] "```{r echo = FALSE}"
+[4] "cc_list$Data"        
+[5] "```"                
+\end{CodeOutput}
+\end{CodeChunk}
 
-```{r}
-ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
-               package = c("ggplot2", "DT"),
-               decorator = list(data.frame = datatable))
+In this case, the \pkg{listdown} package will show the entire data set
+as is the default specified. However, suppose we do not want to show the
+entire data set in the document. This is common, especially when the
+data set is large and requires too much vertical space in the outputted
+document resulting in too much or irrelevant data being shown. Instead,
+we would like to output to an html document where the data is shown in a
+\texttt{datatable} thereby controlling the amount of real-estate needed
+to present the data and, at the same time, providing the user with
+interactivity to sort and search the data set.
 
-ld_make_chunks(ld)[33:37]
-```
+In \pkg{listdown}, a function or method that implements the presentation
+of a computational component is referred to as a \emph{decorator} since
+if follows the classic decorator pattern described in \citet{gamma1995}.
+A decorator takes the element that will be presented as an argument and
+returns an object for presentation in the output directory. A decorator
+is specified using the \texttt{decorator} parameter of the
+\texttt{listdown()} function using a named list where the name
+corresponds to the type and the element correspond to the function or
+method that will decorate an object of that type. For example, the
+\texttt{anscombe} data set can be decorated with the
+\texttt{DT::datatable()} function \citep{xie2020} as:
 
-List names in the `decorator` argument provide a key to which a function or method is mapped.
-The underlying decorator resolution is implemented for a given computational component by going through decorator names sequentially to see if the component inherits from the name using the `inherits()` function.
-The function or method is selected from the corresponding name which the element first inherits from.
-This means that when customizing the presentation of objects that inherit from a common class, the more abstract classes should appear at the end of the list.
-This will ensure that specialized classes will be encountered first in the resolution process.
-It should be noted that an object's type is first checked against the decorator name list and then checked to see if it is a list.
-This allows a user to both decorate a list and retain `"list"` in its class attributes.
+\begin{CodeChunk}
 
-A separate argument, `default_decorator`, allows the user to specify the default decorator for an object whose type does not appear in the `decorator` list.
-This allows the user to specify any class name for the decorator and avoids a potential type name collision with a default decorator whose name is determined by convention.
-By default, this argument is set to `identity` but it can be use to not display a computational component by default if the argument is set to `NULL`.
+\begin{CodeInput}
+R> ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
+R+                package = c("ggplot2", "DT"),
+R+                decorator = list(data.frame = datatable))
+R> 
+R> ld_make_chunks(ld)[33:37]
+\end{CodeInput}
 
-# Design
+\begin{CodeOutput}
+[1] "# Data"                  
+[2] ""                       
+[3] "```{r}"                  
+[4] "datatable(cc_list$Data)"
+[5] "```"                    
+\end{CodeOutput}
+\end{CodeChunk}
 
-A \pkg{listdown} object specifies the location of a list of computational components and options for presenting those components in an R Markdown document.
-The list is a hierarchical data structure that also provides the structure of the outputted document.
-A corresponding document has two sections "Iris" and "Sepal.Length".
-The latter has three subsections "Sepal.Width", "Petal.Length", and "Colored".
-The "Colored" subsection has two sub-subsections, "Sepal.Width" and "Petal.Length".
-The structure can be seen using the `ld_cc_dendro()` function.
+List names in the \texttt{decorator} argument provide a key to which a
+function or method is mapped. The underlying decorator resolution is
+implemented for a given computational component by going through
+decorator names sequentially to see if the component inherits from the
+name using the \texttt{inherits()} function. The function or method is
+selected from the corresponding name which the element first inherits
+from. This means that when customizing the presentation of objects that
+inherit from a common class, the more abstract classes should appear at
+the end of the list. This will ensure that specialized classes will be
+encountered first in the resolution process. It should be noted that an
+object's type is first checked against the decorator name list and then
+checked to see if it is a list. This allows a user to both decorate a
+list and retain \texttt{"list"} in its class attributes.
 
-```{r}
-# Create a more hierarchical list of computational components.
-comp_comp2 <- list(
-  Iris = iris,
-  Sepal.Length = list(
-    Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + 
-      geom_point(),
-    Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + 
-      geom_point(),
-    Colored = list(
-      Sepal.Width = ggplot(iris, 
-                          aes(x = Sepal.Length, y = Sepal.Width, 
-                              color = Species)) + geom_point(),
-      Petal.Length = ggplot(iris,
-                            aes(x = Sepal.Length, y = Petal.Length, 
-                                color = Species)) + geom_point())))
+A separate argument, \texttt{default\_decorator}, allows the user to
+specify the default decorator for an object whose type does not appear
+in the \texttt{decorator} list. This allows the user to specify any
+class name for the decorator and avoids a potential type name collision
+with a default decorator whose name is determined by convention. By
+default, this argument is set to \texttt{identity} but it can be use to
+not display a computational component by default if the argument is set
+to \texttt{NULL}.
 
-# Create the dendrogram.
-ld_cc_dendro(comp_comp2)
-```
+\hypertarget{design}{%
+\section{Design}\label{design}}
 
-Both the `ld_cc_dendro()` and `ld_make_chunks()` functions work by recursively descending the computational components list depth-first.
-If the list containing and element has a name, it is written to the output as a section, subsection, subsubsection, etc.
-to a return string.
-If the visited list element is itself a list, then the same procedure is called on the child list through a recursive call.
-If the element is not a list, then it is outputted inside an R Markdown chunk in the return string using the appropropriate decorator.
+A \pkg{listdown} object specifies the location of a list of
+computational components and options for presenting those components in
+an R Markdown document. The list is a hierarchical data structure that
+also provides the structure of the outputted document. A corresponding
+document has two sections ``Iris'' and ``Sepal.Length''. The latter has
+three subsections ``Sepal.Width'', ``Petal.Length'', and ``Colored''.
+The ``Colored'' subsection has two sub-subsections, ``Sepal.Width'' and
+``Petal.Length''. The structure can be seen using the
+\texttt{ld\_cc\_dendro()} function.
 
-# Initialization code
+\begin{CodeChunk}
 
-The `listdown()` function facilitates the insertion of initialization code through the `init_expr` argument.
-Code is inserted immediately after the libraries are loaded in the R Markdown document.
-In general, it is suggested that the number of initial expressions be kept small so that the \proglang{R} Markdown document is easy to read.
-If a large number of functions are required by the target \proglang{R} Markdown document then they can be put into a file and sourced using the initial expression.
-As an example, suppose we are creating an html document and presenting data using the `datatable()` function.
-However, we do not want to include the search capabilities provided.
-This can be easily accomplished by creating a new function, `datatable_no_search()`, created using the `partial()` function \cite{purrr} to partially apply `list(dom = 't')` to the `options` argument of `datatable`.
+\begin{CodeInput}
+R> # Create a more hierarchical list of computational components.
+R> comp_comp2 <- list(
+R+   Iris = iris,
+R+   Sepal.Length = list(
+R+     Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + 
+R+       geom_point(),
+R+     Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + 
+R+       geom_point(),
+R+     Colored = list(
+R+       Sepal.Width = ggplot(iris, 
+R+                           aes(x = Sepal.Length, y = Sepal.Width, 
+R+                               color = Species)) + geom_point(),
+R+       Petal.Length = ggplot(iris,
+R+                             aes(x = Sepal.Length, y = Petal.Length, 
+R+                                 color = Species)) + geom_point())))
+R> 
+R> # Create the dendrogram.
+R> ld_cc_dendro(comp_comp2)
+\end{CodeInput}
 
-```{r}
-saveRDS(comp_comp2, "comp-comp2.rds")
-ld <- listdown(load_cc_expr = readRDS("comp-comp2.rds"),
-               package = c("ggplot2", "DT", "purrr"),
-               decorator = list(ggplot = identity,
-                                data.frame = datatable_no_search),
-               init_expr = {
-                 datatable_no_search <- partial(datatable,
-                                                options = list(dom = 't'))
-                 },
-               echo = FALSE)
+\begin{CodeOutput}
 
-ld_make_chunks(ld)[2:10]
-```
+comp_comp2
+  |-- Iris
+  |  o-- object of type(s):data.frame
+  o-- Sepal.Length
+   |-- Sepal.Width
+   |  o-- object of type(s):gg ggplot
+   |-- Petal.Length
+   |  o-- object of type(s):gg ggplot
+   o-- Colored
+    |-- Sepal.Width
+    |  o-- object of type(s):gg ggplot
+    o-- Petal.Length
+       o-- object of type(s):gg ggplot
+\end{CodeOutput}
+\end{CodeChunk}
 
-# R code chunk customization
+Both the \texttt{ld\_cc\_dendro()} and \texttt{ld\_make\_chunks()}
+functions work by recursively descending the computational components
+list depth-first. If the list containing and element has a name, it is
+written to the output as a section, subsection, subsubsection, etc. to a
+return string. If the visited list element is itself a list, then the
+same procedure is called on the child list through a recursive call. If
+the element is not a list, then it is outputted inside an R Markdown
+chunk in the return string using the appropropriate decorator.
 
-The \pkg{listdown} package supports also supports capabilities to further customize the presentation by specifying \proglang{R} code chunk options in the \proglang{R} Markdown document in two distinct ways.
-The first is used when the options we would like to specify is tied to type of the object being presented.
-This can be though of as a chunk-option decorator.
-The second is use for changing the options for an individual chunk in an ad-hoc manner.
+\hypertarget{initialization-code}{%
+\section{Initialization code}\label{initialization-code}}
 
-With three different modes of chunk customization it should be noted that the increasing priority of the chunk options specification is document-wide, decorator-wide, and ad hoc.
-That is, decorator-wide chunk options take priority over document-wide chunk options and ad-hod options take priority over decorator-wide options.
-In addition, it should be noted that the use of the lowest priority scheme that accomplishes the presentation goals is preferred because it lends itself to greater code and maintenance efficiency.
+The \texttt{listdown()} function facilitates the insertion of
+initialization code through the \texttt{init\_expr} argument. Code is
+inserted immediately after the libraries are loaded in the R Markdown
+document. In general, it is suggested that the number of initial
+expressions be kept small so that the \proglang{R} Markdown document is
+easy to read. If a large number of functions are required by the target
+\proglang{R} Markdown document then they can be put into a file and
+sourced using the initial expression. As an example, suppose we are
+creating an html document and presenting data using the
+\texttt{datatable()} function. However, we do not want to include the
+search capabilities provided. This can be easily accomplished by
+creating a new function, \texttt{datatable\_no\_search()}, created using
+the \texttt{partial()} function \cite{purrr} to partially apply
+\texttt{list(dom\ =\ \textquotesingle{}t\textquotesingle{})} to the
+\texttt{options} argument of \texttt{datatable}.
 
-## Controlling options associated with a decorator
+\begin{CodeChunk}
 
-The document-wide chunk option specification provides the default chunk options for output documents generated using \pkg{listdown}.
-However, the presentation of a data object often varies by type.
-For example, we may want to specify the height and width of a graph, but not a table.
-This is accomplished in the \pkg{listdown} package when a `listdown` object is created using the `decorator_chunk_opts` option in the `listdown()` function.
-For example, associating all `ggplot` objects with \proglang{R} chunks having a width of 100 and a height of 200 can be accomplished with the following code and it can be seen that only chunk options associated with a plot are modified.
+\begin{CodeInput}
+R> saveRDS(comp_comp2, "comp-comp2.rds")
+R> ld <- listdown(load_cc_expr = readRDS("comp-comp2.rds"),
+R+                package = c("ggplot2", "DT", "purrr"),
+R+                decorator = list(ggplot = identity,
+R+                                 data.frame = datatable_no_search),
+R+                init_expr = {
+R+                  datatable_no_search <- partial(datatable,
+R+                                                 options = list(dom = 't'))
+R+                  },
+R+                echo = FALSE)
+R> 
+R> ld_make_chunks(ld)[2:10]
+\end{CodeInput}
 
-```{r}
-ld <- listdown(load_cc_expr = readRDS("comp-comp2.rds"),
-               package = c("ggplot2", "DT", "purrr"),
-               decorator_chunk_opts = 
-                 list(ggplot = list(fig.width = 100,
-                                    fig.height = 200)),
-               init_expr = {
-                 datatable_no_search <- partial(datatable,
-                                                options = list(dom = 't'))
-                 },
-               echo = FALSE)
+\begin{CodeOutput}
+[1] "```{r echo = FALSE}"                                                   
+[2] "library(ggplot2)"                                                      
+[3] "library(DT)"                                                           
+[4] "library(purrr)"                                                        
+[5] ""                                                                      
+[6] "cc_list <- readRDS(\"comp-comp2.rds\")"                                
+[7] ""                                                                      
+[8] "datatable_no_search <- partial(datatable, options = list(dom = \"t\"))"
+[9] "```"                                                                   
+\end{CodeOutput}
+\end{CodeChunk}
 
-ld_make_chunks(ld)[c(12:16, 19:24)]
-```
+\hypertarget{r-code-chunk-customization}{%
+\section{R code chunk customization}\label{r-code-chunk-customization}}
 
-## Controlling chunk-level options
+The \pkg{listdown} package supports also supports capabilities to
+further customize the presentation by specifying \proglang{R} code chunk
+options in the \proglang{R} Markdown document in two distinct ways. The
+first is used when the options we would like to specify is tied to type
+of the object being presented. This can be though of as a chunk-option
+decorator. The second is use for changing the options for an individual
+chunk in an ad-hoc manner.
 
-Along with providing decorator-wide chunk options, it is also possible to control individual chunk options.
-The capability is distinct from the document-wide and decorator-wide specification of options in that it must be applied to the computational component list element whose associated options will be modified, rather than the `listdown` object.
-This is because the `listdown` only specifies how classes of objects should be presented.
-To modify the chunk options associated with a specific list element the list element is provided with a set of attributes that can be queried by the `ld_chunk_opts()` function as the output document is being generated.
-Because of the ad hoc nature of this capability, its use is discouraged.
-A better solution, that maintains the behavior is to add class information to the list element and specify decorator-wide chunk options for the new class.
-This maintains the separation of the computational component list, which maintains the document structure and data for presentation from the specification of how the document will be created and rendered.
+With three different modes of chunk customization it should be noted
+that the increasing priority of the chunk options specification is
+document-wide, decorator-wide, and ad hoc. That is, decorator-wide chunk
+options take priority over document-wide chunk options and ad-hod
+options take priority over decorator-wide options. In addition, it
+should be noted that the use of the lowest priority scheme that
+accomplishes the presentation goals is preferred because it lends itself
+to greater code and maintenance efficiency.
 
-```{r}
-comp_comp2$Iris <- ld_chunk_opts(comp_comp2$Iris, echo = TRUE)
-saveRDS(comp_comp2, "comp-comp2.rds")
-ld_make_chunks(ld)[12:16]
-```
+\hypertarget{controlling-options-associated-with-a-decorator}{%
+\subsection{Controlling options associated with a
+decorator}\label{controlling-options-associated-with-a-decorator}}
 
-# A simple example: Reporting on the gtsummary::trial dataset
+The document-wide chunk option specification provides the default chunk
+options for output documents generated using \pkg{listdown}. However,
+the presentation of a data object often varies by type. For example, we
+may want to specify the height and width of a graph, but not a table.
+This is accomplished in the \pkg{listdown} package when a
+\texttt{listdown} object is created using the
+\texttt{decorator\_chunk\_opts} option in the \texttt{listdown()}
+function. For example, associating all \texttt{ggplot} objects with
+\proglang{R} chunks having a width of 100 and a height of 200 can be
+accomplished with the following code and it can be seen that only chunk
+options associated with a plot are modified.
+
+\begin{CodeChunk}
+
+\begin{CodeInput}
+R> ld <- listdown(load_cc_expr = readRDS("comp-comp2.rds"),
+R+                package = c("ggplot2", "DT", "purrr"),
+R+                decorator_chunk_opts = 
+R+                  list(ggplot = list(fig.width = 100,
+R+                                     fig.height = 200)),
+R+                init_expr = {
+R+                  datatable_no_search <- partial(datatable,
+R+                                                 options = list(dom = 't'))
+R+                  },
+R+                echo = FALSE)
+R> 
+R> ld_make_chunks(ld)[c(12:16, 19:24)]
+\end{CodeInput}
+
+\begin{CodeOutput}
+ [1] "# Iris"                                                
+ [2] ""                                                      
+ [3] "```{r echo = FALSE}"                                   
+ [4] "cc_list$Iris"                                          
+ [5] "```"                                                   
+ [6] ""                                                      
+ [7] "## Sepal.Width"                                        
+ [8] ""                                                      
+ [9] "```{r echo = FALSE, fig.width = 100, fig.height = 200}"
+[10] "cc_list$Sepal.Length$Sepal.Width"                      
+[11] "```"                                                   
+\end{CodeOutput}
+\end{CodeChunk}
+
+\hypertarget{controlling-chunk-level-options}{%
+\subsection{Controlling chunk-level
+options}\label{controlling-chunk-level-options}}
+
+Along with providing decorator-wide chunk options, it is also possible
+to control individual chunk options. The capability is distinct from the
+document-wide and decorator-wide specification of options in that it
+must be applied to the computational component list element whose
+associated options will be modified, rather than the \texttt{listdown}
+object. This is because the \texttt{listdown} only specifies how classes
+of objects should be presented. To modify the chunk options associated
+with a specific list element the list element is provided with a set of
+attributes that can be queried by the \texttt{ld\_chunk\_opts()}
+function as the output document is being generated. Because of the ad
+hoc nature of this capability, its use is discouraged. A better
+solution, that maintains the behavior is to add class information to the
+list element and specify decorator-wide chunk options for the new class.
+This maintains the separation of the computational component list, which
+maintains the document structure and data for presentation from the
+specification of how the document will be created and rendered.
+
+\begin{CodeChunk}
+
+\begin{CodeInput}
+R> comp_comp2$Iris <- ld_chunk_opts(comp_comp2$Iris, echo = TRUE)
+R> saveRDS(comp_comp2, "comp-comp2.rds")
+R> ld_make_chunks(ld)[12:16]
+\end{CodeInput}
+
+\begin{CodeOutput}
+[1] "# Iris"             
+[2] ""                   
+[3] "```{r echo = TRUE}"
+[4] "cc_list$Iris"       
+[5] "```"               
+\end{CodeOutput}
+\end{CodeChunk}
+
+\hypertarget{a-simple-example-reporting-on-the-gtsummarytrial-dataset}{%
+\section{A simple example: Reporting on the gtsummary::trial
+dataset}\label{a-simple-example-reporting-on-the-gtsummarytrial-dataset}}
+
 \label{sect:simple-example}
 
-As mentioned before, we have found the \pkg{listdown} package particularly helpful for reporting the results of clinical trials thereby creating a basis for discussion and collaboration between (bio)statisticians and the clinicians running the trials.
-For this use case, the context and data collection procedures are well-understood and as a result very few narrative components are needed.
-It is also the case that the modes of presentation (tables, scatterplots, survivalplots, consort diagrams, etc.) are standardized.
-The goal in presenting the trial characteristics is to identify problems in the data, monitor trial enrollment and response, quantify known relationships among the data, and test hypotheses about a therapy's efficacy.
+As mentioned before, we have found the \pkg{listdown} package
+particularly helpful for reporting the results of clinical trials
+thereby creating a basis for discussion and collaboration between
+(bio)statisticians and the clinicians running the trials. For this use
+case, the context and data collection procedures are well-understood and
+as a result very few narrative components are needed. It is also the
+case that the modes of presentation (tables, scatterplots,
+survivalplots, consort diagrams, etc.) are standardized. The goal in
+presenting the trial characteristics is to identify problems in the
+data, monitor trial enrollment and response, quantify known
+relationships among the data, and test hypotheses about a therapy's
+efficacy.
 
-In practice we generally separate the data cleaning, exploration, analysis, monitoring, and presentation components.
-The computational component list has tens of elements with thousands of visualizations.
-These facts, coupled with the privacy constraints make a complete example difficult for the purposes of this paper.
-So, below we provide a simple example of the types of documents we provide using the `gtsummary::trial` dataset.
-While it is not complete, it does convey they types of reports we are currently generating for completed and ongoing clinical trials.
+In practice we generally separate the data cleaning, exploration,
+analysis, monitoring, and presentation components. The computational
+component list has tens of elements with thousands of visualizations.
+These facts, coupled with the privacy constraints make a complete
+example difficult for the purposes of this paper. So, below we provide a
+simple example of the types of documents we provide using the
+\texttt{gtsummary::trial} dataset. While it is not complete, it does
+convey they types of reports we are currently generating for completed
+and ongoing clinical trials.
 
-The code creates a computational component list containing a table of the patient characteristics along with survival plots by overall survival, survival by stage, and survival by grade.
-The table is an element of a named list called "Table 1" and then survival plots are elements of named lists indicating the conditioning variable.
-The structure can be seen in the dendrogram below.
+The code creates a computational component list containing a table of
+the patient characteristics along with survival plots by overall
+survival, survival by stage, and survival by grade. The table is an
+element of a named list called ``Table 1'' and then survival plots are
+elements of named lists indicating the conditioning variable. The
+structure can be seen in the dendrogram below.
 
-```{r, eval = TRUE, message=FALSE, warning=FALSE}
-library(gtsummary)
-library(dplyr)
-library(glue)
-library(survival)
-library(survminer)
-library(rmarkdown)
+\begin{CodeChunk}
 
-# Function to create the computational components.
-make_surv_cc <- function(trial, treat, surv_cond_chars) {
-  # Create Table 1 by treatment
-  table_1 <- trial %>%
-    tbl_summary(by = all_of(treat)) %>%
-    gtsummary::as_flextable()
+\begin{CodeInput}
+R> library(gtsummary)
+R> library(dplyr)
+R> library(glue)
+R> library(survival)
+R> library(survminer)
+R> library(rmarkdown)
+R> 
+R> # Function to create the computational components.
+R> make_surv_cc <- function(trial, treat, surv_cond_chars) {
+R+   # Create Table 1 by treatment
+R+   table_1 <- trial %>%
+R+     tbl_summary(by = all_of(treat)) %>%
+R+     gtsummary::as_flextable()
+R+ 
+R+   # Create survival plots base on survival characteristics
+R+   scs <- lapply(c("1", surv_cond_chars),
+R+                 function(sc) {
+R+                   glue("Surv(ttdeath, death) ~ {treat} + {sc}") %>%
+R+                     as.formula() %>%
+R+                     surv_fit(trial) %>%
+R+                     ggsurvplot()
+R+                 })
+R+   names(scs) <- c("Overall", tools::toTitleCase(surv_cond_chars))
+R+   list(`Table 1` = table_1, `Survival Plots` = scs)
+R+ }
+R> 
+R> # Create the computational components and write to surv-cc.rds.
+R> surv_cc <- make_surv_cc(trial, treat = "trt",
+R+                         surv_cond_chars = c("stage", "grade"))
+R> 
+R> ld_cc_dendro(surv_cc)
+\end{CodeInput}
 
-  # Create survival plots base on survival characteristics
-  scs <- lapply(c("1", surv_cond_chars),
-                function(sc) {
-                  glue("Surv(ttdeath, death) ~ {treat} + {sc}") %>%
-                    as.formula() %>%
-                    surv_fit(trial) %>%
-                    ggsurvplot()
-                })
-  names(scs) <- c("Overall", tools::toTitleCase(surv_cond_chars))
-  list(`Table 1` = table_1, `Survival Plots` = scs)
-}
+\begin{CodeOutput}
 
-# Create the computational components and write to surv-cc.rds.
-surv_cc <- make_surv_cc(trial, treat = "trt",
-                        surv_cond_chars = c("stage", "grade"))
+surv_cc
+  |-- Table 1
+  |  o-- object of type(s):flextable
+  o-- Survival Plots
+   |-- Overall
+   |  o-- object of type(s):ggsurvplot ggsurv list
+   |-- Stage
+   |  o-- object of type(s):ggsurvplot ggsurv list
+   o-- Grade
+      o-- object of type(s):ggsurvplot ggsurv list
+\end{CodeOutput}
+\end{CodeChunk}
 
-ld_cc_dendro(surv_cc)
-```
+As shown before, the report is created by saving the computational
+components, creating a listdown object, writing the \proglang{R}
+Markdown document, and rendering it. The resulting document,
+trial-report.html, can then be placed in a shared space where it can be
+viewed and interpreted by stakeholders in the clincial trial. The
+\proglang{R} Markdown document created by this code is shown in Appendix
+1.
 
-As shown before, the report is created by saving the computational components, creating a listdown object, writing the \proglang{R} Markdown document, and rendering it.
-The resulting document, trial-report.html, can then be placed in a shared space where it can be viewed and interpreted by stakeholders in the clincial trial.
-The \proglang{R} Markdown document created by this code is shown in Appendix 1.
+\begin{CodeChunk}
 
-```{r eval = FALSE}
-saveRDS(surv_cc, "surv-cc.rds")
+\begin{CodeInput}
+R> saveRDS(surv_cc, "surv-cc.rds")
+R> 
+R> # Create the listdown object with appropriate dependencies
+R> # and presentation parameters.
+R> ld_surv <- listdown(load_cc_expr = readRDS("surv-cc.rds"),
+R>                     package = c("gtsummary", "survminer", "flextable"),
+R>                     decorator = list(ggsurvplot = identity,
+R>                                      tbl_summary = identity),
+R>                     echo = FALSE,
+R>                     message = FALSE,
+R>                     warning = FALSE,
+R>                     fig.width = 7,
+R>                     fig.height = 4.5)
+R> 
+R> # Write an RMarkdown header and chunks derived from the 
+R> # computational components and listdown object to trial-report.rmd.
+R> writeLines(
+R>   paste(c(
+R>     as.character(ld_rmarkdown_header("Simple Trial Report")),
+R>     ld_make_chunks(ld_surv))),
+R>   "trial-report.rmd")
+R> 
+R> # Render the RMarkdown file to html
+R> render("trial-report.rmd", quiet = TRUE, html_document(keep_tex = TRUE))  
+\end{CodeInput}
+\end{CodeChunk}
 
-# Create the listdown object with appropriate dependencies
-# and presentation parameters.
-ld_surv <- listdown(load_cc_expr = readRDS("surv-cc.rds"),
-                    package = c("gtsummary", "survminer", "flextable"),
-                    decorator_chunk_opts = 
-                      list(ggsurvplot = list(fig.width = 100,
-                                             fig.height = 200)),
-                    echo = FALSE,
-                    message = FALSE,
-                    warning = FALSE,
-                    fig.width = 7,
-                    fig.height = 4.5)
-
-# Write an RMarkdown header and chunks derived from the 
-# computational components and listdown object to trial-report.rmd.
-writeLines(
-  paste(c(
-    as.character(ld_rmarkdown_header("Simple Trial Report")),
-    ld_make_chunks(ld_surv))),
-  "trial-report.rmd")
-
-# Render the RMarkdown file to html
-render("trial-report.rmd", quiet = TRUE, html_document(keep_tex = TRUE))  
-```
-
-\bibliography{../references}
+\bibliography{references}
 
@@
 
-```{r eval = FALSE}
----
-title: Simple Trial Report
-output: html_document
----
+\begin{CodeChunk}
 
-\```{r echo = FALSE, message = FALSE, warning = FALSE}
-library(gtsummary)
-library(survminer)
-library(flextable)
+\begin{CodeInput}
+R> ---
+R> title: Simple Trial Report
+R> output: html_document
+R> ---
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+R> library(gtsummary)
+R> library(survminer)
+R> library(flextable)
+R> 
+R> cc_list <- readRDS("surv-cc.rds")
+R> \```
+R> 
+R> # Table 1
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+R> cc_list$`Table 1`
+R> \```
+R> 
+R> # Survival Plots
+R> 
+R> ## Overall
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+R> cc_list$`Survival Plots`$Overall
+R> \```
+R> 
+R> ## Stage
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+R> cc_list$`Survival Plots`$Stage
+R> \```
+R> 
+R> ## Grade
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+R> cc_list$`Survival Plots`$Grade
+R> \```
+\end{CodeInput}
+\end{CodeChunk}
 
-cc_list <- readRDS("surv-cc.rds")
-\```
-
-# Table 1
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE}
-cc_list$`Table 1`
-\```
-
-# Survival Plots
-
-## Overall
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-     fig.height = 4.5}
-cc_list$`Survival Plots`$Overall
-\```
-
-## Stage
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-     fig.height = 4.5}
-cc_list$`Survival Plots`$Stage
-\```
-
-## Grade
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-     fig.height = 4.5}
-cc_list$`Survival Plots`$Grade
-\```
-```
+\end{document}

### 2020-06-23 inst/jss/kane-listdown/clean.sh

@@ -1,0 +1,8 @@
+#! /bin/sh
+rm *.aux 
+rm *.bbl 
+rm *.blg 
+rm *.log 
+rm *.out 
+rm *.pdf 
+rm -rf kane-listdown_files 

### 2020-06-23 inst/jss/kane-listdown/clean.sh
Moved the directory.

@@ -1,8 +1,0 @@
-#! /bin/sh
-rm *.aux 
-rm *.bbl 
-rm *.blg 
-rm *.log 
-rm *.out 
-rm *.pdf 
-rm -rf kane-listdown_files 

### 2020-06-23 inst/jss/kane-listdown/supplemental-material/clean.sh

@@ -1,7 +1,0 @@
-#! /bin/sh
-rm *.rds 
-rm *.pdf 
-rm *.tex 
-rm *.html 
-rm -rf figure 
-rm trial-report.rmd

### 2020-06-23 inst/jss/listdown-jss.tex
And back.

--- 2020-06-23 inst/jss/kane-listdown/listdown-jss.tex
@@
 \author{
-Michael Kane\\Yale University
+Michael Kane\\Yale University \And Simon Urbanek\\The University of
+Aukland
 }
@@
 
-\Plainauthor{Michael Kane}
+\Plainauthor{Michael Kane, Simon Urbanek}
 \Plaintitle{On the Programmatic Generation of Reproducible Documents}
-\Shorttitle{Programmatic Generation of Reproducible Documents}
+\Shorttitle{On the Programmatic Generation of Reproducible Documents}
 
 \Abstract{
-The abstract of the article.
+Reproducible document standards, like \proglang{R} Markdown, facilitate
+the programmatic creation of documents whose content is itself
+programmatically generated. While these documents are generally not
+complete in the sense that they will not include prose content,
+generated by an author to provide context, a narrative, etc.,
+programmatic generation can provide substantial efficiencies for
+structuring and constructing documents. This paper explores the
+programmatic generation of reproducible by distinguishing components
+than can be created by computational means from those requiring
+human-generated prose, providing guidelines for the generation of these
+documents, and identifying a use case in clinical trial reporting. These
+concepts and use case are illustrated through the \pkg{listdown} package
+for the \proglang{R} programming environment, which is is currently
+available on the Comprehensive R Archive Network (CRAN).
 }
@@
   E-mail: \href{mailto:michael.kane@yale.edu}{\nolinkurl{michael.kane@yale.edu}}\\
+
+      Simon Urbanek\\
+  The University of Aukland\\
+  38 Princes StreetAuckland Central, Aukland 1010, NZ\\
+  E-mail: \href{mailto:s.urbanek@auckland.ac.nz}{\nolinkurl{s.urbanek@auckland.ac.nz}}\\
 
@@
 Since computational components are, by definition, computationally
-derived objects and R Markdown is a well-defined standard, it is
-possible to programmatically create \proglang{R} Markdown documents with
-computational components, which is the focus of this paper. However,
-before proceeding down this avenue, we would like to highlight two
-fundamental limitations to automated R Markdown document construction.
-First and foremost, without narrative components a document has very
-little context. Quantitative analyses require research questions,
-hypotheses, reviews, interpretations, and conclusions. Computational
-components are necessary but generally not sufficient for constructing
-an analysis. Second, it is difficult if not impossible to construct
-computational components for an arbitary analyses. Analyses themselves
-have context and are built with a set of assumptions and goals.
-
-This is not to say the programmatic creation of \proglang{R} Markdown
-documents is unwarranted or not useful. In fact, it has at least two
-appealing characteristics. First, it allows us to distinguish the
-presentation of analytical results from other steps in a data science or
-data processing pipeline. These other steps including cleaning and
-analysis often require their own environment and configuration with
-requirements very different than the computational needs of creating a
-presentation. By separating these components each can be developed
-independently. At the same time, by specifying a contract for the output
-of those objects, we can establish a consistent means by which processed
-data can be passed to systems for presentating those data in a
-structured way. The second reason for programmatic creation of R
-Markdown documents is convenience. In collaborative environments,
-especially in the early stages, large numbers of graphs and tables are
-generated and discussed. By collecting these artifacts and structuring
-them consistently, we can quickly iterate upon and restructure the
-resulting documents to more clearly present the data without needing to
-spend time on the creation of the presentation document.
+derived objects and \proglang{R} Markdown is a well-defined standard, it
+is possible to programmatically create \proglang{R} Markdown documents
+with computational components, which is the focus of this paper.
+Generating documents in this manner has two appealing characteristics.
+First, it allows us to distinguish the presentation of analytical
+results from other steps in a data science or data processing pipeline.
+These other steps including cleaning and analysis often require their
+own environment and configuration with requirements very different than
+the computational needs of creating a presentation. By separating these
+components each can be developed independently. At the same time, by
+specifying a contract for the output of those objects, we can establish
+a consistent means by which processed data can be passed to systems for
+presentating those data in a structured way. The second reason for
+programmatic creation of R Markdown documents is convenience. In
+collaborative environments, especially in the early stages, large
+numbers of graphs and tables are generated and discussed. By collecting
+these artifacts and structuring them consistently, we can quickly
+iterate upon and restructure the resulting documents to more clearly
+present the data without needing to spend time on the creation of the
+presentation document.
 
@@
 code to and outputted document as well as how to control chunk-level
-options. Section 5 concludes the paper with a few final remarks.
+options. Section 5 provides a simplified case study of how the package
+is currently being used in clinical trial reporting. Section 6 concludes
+the paper with a few final remarks on the general types of applications
+where \pkg{listdown} has been shown effective.
 
@@
 R> doc <- c(
-R+   unlist(strsplit(as.character(ld_rmarkdown_header("Anscombe's Quartet",
+R+   as.character(ld_rmarkdown_header("Anscombe's Quartet",
 R+                                    author = "Francis Anscombe",
 R+                                    date = "1973")),
-R+                   "\n", fixed = TRUE)),
 R+   ld_make_chunks(ld))
@@
 
+\hypertarget{advanced-usage}{%
+\section{Advanced usage}\label{advanced-usage}}
+
 \hypertarget{initialization-code}{%
-\section{Initialization code}\label{initialization-code}}
+\subsection{Initialization code}\label{initialization-code}}
 
@@
 \hypertarget{r-code-chunk-customization}{%
-\section{R code chunk customization}\label{r-code-chunk-customization}}
+\subsection{R code chunk
+customization}\label{r-code-chunk-customization}}
 
@@
 R> library(dplyr)
-R> library(glue)
 R> library(survival)
@@
 R+                 function(sc) {
-R+                   glue("Surv(ttdeath, death) ~ {treat} + {sc}") %>%
+R+                   sprintf("Surv(ttdeath, death) ~ %s + %s", treat, sc) %>%
 R+                     as.formula() %>%
@@
 \begin{CodeInput}
+R> # Turn the survplots into a list to show the individual components.
+R> class(surv_cc$`Survival Plots`$Overall) <- 
+R+   class(surv_cc$`Survival Plots`$Stage) <-
+R+   class(surv_cc$`Survival Plots`$Grade) <- "list"
+R> 
+R> # Create a tab for each element of the survplot.
+R> names(surv_cc$`Survival Plots`) <- 
+R+   paste(names(surv_cc$`Survival Plots`), "{.tabset}")
+R> 
+R> # Rename the elements
+R> names(surv_cc$`Survival Plots`$`Overall {.tabset}`) <- 
+R+   names(surv_cc$`Survival Plots`$`Stage {.tabset}`) <- 
+R+   names(surv_cc$`Survival Plots`$`Grade {.tabset}`) <- 
+R+   c("Plot", "Data", "Table")
+R>   
+R> # Save the updated object for presentation.
 R> saveRDS(surv_cc, "surv-cc.rds")
@@
 R> ld_surv <- listdown(load_cc_expr = readRDS("surv-cc.rds"),
-R>                     package = c("gtsummary", "survminer", "flextable"),
-R>                     decorator = list(ggsurvplot = identity,
-R>                                      tbl_summary = identity),
-R>                     echo = FALSE,
-R>                     message = FALSE,
-R>                     warning = FALSE,
-R>                     fig.width = 7,
-R>                     fig.height = 4.5)
+R+                     package = c("gtsummary", "flextable", "DT", 
+R+                                 "ggplot2"),
+R+                     decorator_chunk_opts = 
+R+                       list(gg = list(fig.width = 8,
+R+                                      fig.height = 6)),
+R+                     decorator = list(data.frame = datatable),
+R+                     echo = FALSE,
+R+                     message = FALSE,
+R+                     warning = FALSE,
+R+                     fig.width = 7,
+R+                     fig.height = 4.5)
 R> 
@@
 R> writeLines(
-R>   paste(c(
-R>     as.character(ld_rmarkdown_header("Simple Trial Report")),
-R>     ld_make_chunks(ld_surv))),
-R>   "trial-report.rmd")
+R+   paste(c(
+R+     as.character(ld_rmarkdown_header("Simple Trial Report")),
+R+     ld_make_chunks(ld_surv))),
+R+   "trial-report.rmd")
 R> 
-R> # Render the RMarkdown file to html
-R> render("trial-report.rmd", quiet = TRUE, html_document(keep_tex = TRUE))  
+R> # Render the RMarkdown file to html and show it.
+R> render("trial-report.rmd", quiet = TRUE)
+R> browseURL("trial-report.html")
 \end{CodeInput}
 \end{CodeChunk}
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+While the programmtic generation of reproducible documents has appealing
+qualities, it also has fundamental limitations that should be kept in
+mind when deciding if tools like \pkg{listdown} should be employed.
+First and foremost, without narrative components a document has very
+little context. Quantitative analyses require research questions,
+hypotheses, reviews, interpretations, and conclusions. Computational
+components are necessary but generally not sufficient for constructing
+an analysis. This means that if narrative components must be conveyed in
+a document, then \pkg{listdown} may make the generation of their
+presentation more convenient. However, it does not relieve the burden of
+the author to create prose developing a narrative.
+
+Second, it is difficult if not impossible to construct computational
+components for an arbitary analyses. Analyses themselves have context
+and are built with a set of assumptions and goals. Our experience shows
+that \pkg{listdown} is easiest to used for a fixed data format. This
+means a standard set of table and visualizations for similarly formatted
+data. In particular, data that is periodicaly updated, without changes
+to the format, is a case that is particularly amenable to document
+generation reuse.
+
+Keeping these limitations in mind, \pkg{listdown} can be used to
+effectively reduce the the difficulty of generating documents in a
+variety of contexts and fits readily in data processing and analysis
+pipelines.
 
@@
 R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
+R>      fig.height = 4.5}
 R> library(gtsummary)
-R> library(survminer)
 R> library(flextable)
+R> library(DT)
+R> library(ggplot2)
 R> 
@@
 R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
+R>      fig.height = 4.5}
 R> cc_list$`Table 1`
@@
 R> 
-R> ## Overall
+R> ## Overall {.tabset}
 R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-R> cc_list$`Survival Plots`$Overall
+R> ### Plot
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, 
+R>      fig.height = 6}
+R> cc_list$`Survival Plots`$`Overall {.tabset}`$Plot
 R> \```
 R> 
-R> ## Stage
+R> ### Data
 R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-R> cc_list$`Survival Plots`$Stage
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
+R>      fig.height = 4.5}
+R> datatable(cc_list$`Survival Plots`$`Overall {.tabset}`$Data)
 R> \```
 R> 
-R> ## Grade
+R> ### Table
 R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-R> cc_list$`Survival Plots`$Grade
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
+R>      fig.height = 4.5}
+R> datatable(cc_list$`Survival Plots`$`Overall {.tabset}`$Table)
+R> \```
+R> 
+R> ## Stage {.tabset}
+R> 
+R> ### Plot
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, 
+R>      fig.height = 6}
+R> cc_list$`Survival Plots`$`Stage {.tabset}`$Plot
+R> \```
+R> 
+R> ### Data
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
+R>      fig.height = 4.5}
+R> datatable(cc_list$`Survival Plots`$`Stage {.tabset}`$Data)
+R> \```
+R> 
+R> ### Table
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
+R>      fig.height = 4.5}
+R> datatable(cc_list$`Survival Plots`$`Stage {.tabset}`$Table)
+R> \```
+R> 
+R> ## Grade {.tabset}
+R> 
+R> ### Plot
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, 
+R>      fig.height = 6}
+R> cc_list$`Survival Plots`$`Grade {.tabset}`$Plot
+R> \```
+R> 
+R> ### Data
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
+R>      fig.height = 4.5}
+R> datatable(cc_list$`Survival Plots`$`Grade {.tabset}`$Data)
+R> \```
+R> 
+R> ### Table
+R> 
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
+R>      fig.height = 4.5}
+R> datatable(cc_list$`Survival Plots`$`Grade {.tabset}`$Table)
 R> \```

### 2020-06-23 inst/jss/clean.sh

@@ -1,0 +1,7 @@
+#! /bin/sh
+rm *.aux 
+rm *.bbl 
+rm *.blg 
+rm *.log 
+rm *.out 
+rm -rf kane-listdown_files 

### 2020-06-23 inst/jss/supplemental-material/clean.sh

@@ -1,0 +1,7 @@
+#! /bin/sh
+rm *.rds 
+rm *.pdf 
+rm *.tex 
+rm *.html 
+rm -rf figure 
+rm trial-report.rmd

### 2020-06-29 R/chunk-writer.r
More CRAN revisions.

@@ -5,7 +5,9 @@
 #' unquoted expression indicating how the presentation list will be loaded.
 #' In addition, libraries required by the outputted document and other
 #' parameters can be specified.
-#' @param load_cc_expr an unquoted expression to load the presentation list.
+#' @param load_cc_expr either an unquoted expression or a character string
+#' that will be turned into an unquoted expression via str2lang to load the 
+#' presentation list.
 #' @param package a quoted list of package required by the outputted document.
 #' @param decorator a named list mapping the potential types of list elements
 #' to a decorator function.
@@ -64,7 +66,12 @@ listdown <- function(load_cc_expr,
   } else {
     decorator <- as.list(match.call()$decorator)[-1]
   }
-  ret <- list(load_cc_expr = match.call()$load_cc_expr,
+  if (is.character(match.call()$load_cc_expr)) {
+    load_cc_expr <- str2lang(match.call()$load_cc_expr)
+  } else {
+    load_cc_expr <- match.call()$load_cc_expr
+  }
+  ret <- list(load_cc_expr = load_cc_expr,
               decorator = decorator,
               package = package,
               init_expr = match.call()$init_expr,

### 2020-06-29 R/ld-write-file.r

@@ -10,7 +10,7 @@
 #' output.
 #' @param file_name the output file to write to.
 #' @examples
-#' \donttest{
+#' \dontrun{
 #' library(ggplot2)
 #'
 #' cc_list <- list(
@@ -21,19 +21,17 @@
 #'    geom_point())
 #'
 #'
-#' # Uncomment the following code if you want to write the files.
-#' #
-#' # saveRDS(cc_list, "cc-list.rds")
-#' #
-#' # ld <- listdown(readRDS("cc-list.rds"),
-#' #                package = "ggplot2")
-#' # 
-#' # ld_write_file(ld_rmarkdown_header(title = "The Anscombe Quartet",
-#' #                                   author = "Francis Anscombe",
-#' #                                   date = "1973"),
-#' #               ld,
-#' #               "anscombe-quartet.rmd")
-#' # }
+#' saveRDS(cc_list, "cc-list.rds")
+#'
+#' ld <- listdown(readRDS("cc-list.rds"),
+#'                package = "ggplot2")
+#'
+#' ld_write_file(ld_rmarkdown_header(title = "The Anscombe Quartet",
+#'                                   author = "Francis Anscombe",
+#'                                   date = "1973"),
+#'               ld,
+#'               "anscombe-quartet.rmd")
+#' }
 #' @importFrom crayon red
 #' @export
 ld_write_file <- function(rmd_header, ld, file_name) {

### 2020-07-01 inst/jss/supplemental-material/listdown-jss.rmd
More CRAN changes.

--- 2020-06-23 inst/jss/kane-listdown/supplemental-material/kane-listdown.Rmd
@@
     email: michael.kane@yale.edu
+  - name: Xun (Tony) Jian
+    affiliation: Amgen Inc
+    address:
+    - One Amgen Center Drive
+    - Thousand Oaks, CA 91320-1799, USA
+    email: xunj@amgen.com
   - name: Simon Urbanek
@@
 is separated from their creation. For this use case, a data processing (or analysis) is performed
-and the results are provided in a single named list, organized heirarchically.
+and the results are provided in a single named list, organized hierarchically.
 List element names denote sections, subsections, subsubsection, etc.

### 2020-07-01 R/as-yml.r

@@ -22,15 +22,17 @@ last_index_as_list <- function(loc) {
 #' @param x a named list of computational components.
 #' @importFrom yaml as.yaml
 #' @examples
-#'  library(ggplot2)
-#'  cc_list <- list(
-#'    Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
-#'   `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
-#'   `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
-#'   `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) +
-#'     geom_point())
+#' if (require("ggplot2")) {
 #'
-#'  as_ld_yml(cc_list)
+#'   cc_list <- list(
+#'     Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+#'    `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
+#'    `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
+#'    `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) +
+#'      geom_point())
+#'
+#'   as_ld_yml(cc_list)
+#' }
 #' @export
 as_ld_yml <- function(x) {
 

### 2020-07-01 R/cc-dendro.r

@@ -8,16 +8,17 @@
 #' @param x a named list of computational components
 #' @importFrom crayon red
 #' @examples
-#' library(ggplot2)
+#' if (require("ggplot2")) {
+#' 
+#'   cc_list <- list(
+#'     Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+#'    `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
+#'    `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
+#'    `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) +
+#'      geom_point())
 #'
-#' cc_list <- list(
-#'   Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
-#'  `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
-#'  `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
-#'  `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) +
-#'    geom_point())
-#'
-#' ld_cc_dendro(cc_list)
+#'   ld_cc_dendro(cc_list)
+#' }
 #' @export
 ld_cc_dendro <- function(x) {
   if (!is.list(x)) {

### 2020-07-01 R/chunk-writer.r

@@ -67,9 +67,21 @@ listdown <- function(load_cc_expr,
     decorator <- as.list(match.call()$decorator)[-1]
   }
   if (is.character(match.call()$load_cc_expr)) {
+    # If it's a string literal, then call str2lang on it.
     load_cc_expr <- str2lang(match.call()$load_cc_expr)
   } else {
-    load_cc_expr <- match.call()$load_cc_expr
+    load_cc_expr <- tryCatch( {
+        lce <- eval(match.call()$load_cc_expr)
+        if (is.character(lce)) {
+          # It's a variable holding a string. Call str2lang on it.
+          str2lang(lce)
+        } else {
+          # It's a bare expression.
+          match.call()$load_cc_expr
+        }
+      },
+      # It's a bare expression.
+      finally = match.call()$load_cc_expr)
   }
   ret <- list(load_cc_expr = load_cc_expr,
               decorator = decorator,
@@ -108,6 +120,9 @@ ld_make_chunks.default <- function(ld) {
 ld_make_chunks.listdown <- function(ld) {
 
   cc_list <- eval(ld$load_cc_expr)
+  if (is.character(cc_list)) {
+    cc_list <- eval(parse(text = cc_list))
+  }
   ret_string <- ""
   if (length(ld$package) > 0 || length(ld$init_expr)) {
     ret_string <-

### 2020-07-01 R/ld-write-file.r

@@ -10,27 +10,30 @@
 #' output.
 #' @param file_name the output file to write to.
 #' @examples
-#' \dontrun{
-#' library(ggplot2)
+#' if (require("ggplot2")) {
 #'
-#' cc_list <- list(
-#'   Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
-#'  `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
-#'  `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
-#'  `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) +
-#'    geom_point())
+#'   cc_list <- list(
+#'     Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+#'     `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
+#'     `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + 
+#'       geom_point(),
+#'     `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) +
+#'       geom_point())
 #'
+#'   rds_file <- file.path(tempdir(), "cc-list.rds")
+#'   saveRDS(cc_list, file = rds_file)
 #'
-#' saveRDS(cc_list, "cc-list.rds")
+#'   read_rds_str <- paste0('readRDS("', rds_file, '")')
+#'   ld <- listdown(read_rds_str,
+#'                  package = "ggplot2")
 #'
-#' ld <- listdown(readRDS("cc-list.rds"),
-#'                package = "ggplot2")
-#'
-#' ld_write_file(ld_rmarkdown_header(title = "The Anscombe Quartet",
-#'                                   author = "Francis Anscombe",
-#'                                   date = "1973"),
-#'               ld,
-#'               "anscombe-quartet.rmd")
+#'   rmd_output <- file.path(tempdir(), "anscombe-quartet.rmd")
+#'   ld_write_file(ld_rmarkdown_header(title = "The Anscombe Quartet",
+#'                                     author = "Francis Anscombe",
+#'                                     date = "1973"),
+#'                 ld,
+#'                 rmd_output)
+#' 
 #' }
 #' @importFrom crayon red
 #' @export

### 2020-07-01 tests/testthat/test-headers.r

@@ -1,6 +1,3 @@
-library(ggplot2)
-library(DT)
-
 context("Headers")
 
 source("make-reference.r")

### 2020-07-01 R/ld-write-file.r
I give up.

@@ -1,3 +1,29 @@
+# @examples
+# if (require("ggplot2")) {
+#
+#   cc_list <- list(
+#     Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+#     `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
+#     `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + 
+#       geom_point(),
+#     `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) +
+#       geom_point())
+#
+#   rds_file <- file.path(tempdir(), "cc-list.rds")
+#   saveRDS(cc_list, file = rds_file)
+#
+#   read_rds_str <- paste0('readRDS("', rds_file, '")')
+#   ld <- listdown(read_rds_str,
+#                  package = "ggplot2")
+#
+#   rmd_output <- file.path(tempdir(), "anscombe-quartet.rmd")
+#   ld_write_file(ld_rmarkdown_header(title = "The Anscombe Quartet",
+#                                     author = "Francis Anscombe",
+#                                     date = "1973"),
+#                 ld,
+#                 rmd_output)
+# 
+# }
 
 #' @title Write to an R Markdown File
 #'
@@ -9,32 +35,6 @@
 #' information on how a presentation object should be displayed in the
 #' output.
 #' @param file_name the output file to write to.
-#' @examples
-#' if (require("ggplot2")) {
-#'
-#'   cc_list <- list(
-#'     Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
-#'     `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
-#'     `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + 
-#'       geom_point(),
-#'     `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) +
-#'       geom_point())
-#'
-#'   rds_file <- file.path(tempdir(), "cc-list.rds")
-#'   saveRDS(cc_list, file = rds_file)
-#'
-#'   read_rds_str <- paste0('readRDS("', rds_file, '")')
-#'   ld <- listdown(read_rds_str,
-#'                  package = "ggplot2")
-#'
-#'   rmd_output <- file.path(tempdir(), "anscombe-quartet.rmd")
[…]

### 2020-07-15 inst/jss/listdown-jss.tex
Addressing JSS suggestions.

@@
 \author{
-Michael Kane\\Yale University \And Simon Urbanek\\The University of
-Aukland
+Michael Kane\\Yale University \And Xun (Tony) Jiang\\Amgen
+Inc \And Simon Urbanek\\The University of Aukland
 }
@@
 
-\Plainauthor{Michael Kane, Simon Urbanek}
+\Plainauthor{Michael Kane, Xun (Tony) Jiang, Simon Urbanek}
 \Plaintitle{On the Programmatic Generation of Reproducible Documents}
@@
 programmatic generation of reproducible by distinguishing components
-than can be created by computational means from those requiring
+that can be created by computational means from those requiring
 human-generated prose, providing guidelines for the generation of these
@@
   E-mail: \href{mailto:michael.kane@yale.edu}{\nolinkurl{michael.kane@yale.edu}}\\
+
+      Xun (Tony) Jiang\\
+  Amgen Inc\\
+  One Amgen Center DriveThousand Oaks, CA 91320-1799, USA\\
+  E-mail: \href{mailto:xunj@amgen.com}{\nolinkurl{xunj@amgen.com}}\\
 
@@
 is performed and the results are provided in a single named list,
-organized heirarchically. List element names denote sections,
+organized hierarchically. List element names denote sections,
 subsections, subsubsection, etc. and the list elements contain the data
@@
 
-One area where we have found \pkg{listdown} is particuarly useful is in
+One area where we have found \pkg{listdown} is particularly useful is in
 the reporting and research of clinical trial data. These collaborations
@@
 analyses are conveyed to a clinician. The associated presentations
-require very little context - clinicians often have a better
-understanding of the data collected than the statistician - often
-eliminating the need for narrative components. At the same time, a large
-number of hierarchical, heterogenous artifacts (tables and multiple
-types of plots) need to be conveyed thereby making the manual creation
-of \proglang{R} Markdown documents inconvenient.
+require very little context - clinicians often have as good an
+understanding of the data collected as that of the statistician's -
+often eliminating or significantly reducing the need for narrative
+components. At the same time, a large number of hierarchical,
+heterogenous artifacts (tables and multiple types of plots) need to be
+conveyed thereby making the manual creation of \proglang{R} Markdown
+documents inconvenient.
 
@@
 
-The rest of this paper is structured as follow. The next section goes
+The rest of this paper is structured as follows. The next section goes
 over basic usage and commentary. This section is meant to convey the
@@
 the code shown below. It could easily be written to a file for rendering
-using the \texttt{writeLines()} function.
+using the \texttt{writeLines()} function, for example.
 
@@
 R> doc <- c(
-R+   as.character(ld_rmarkdown_header("Anscombe's Quartet",
-R+                                    author = "Francis Anscombe",
-R+                                    date = "1973")),
-R+   ld_make_chunks(ld))
+R>   as.character(ld_rmarkdown_header("Anscombe's Quartet",
+R>                                    author = "Francis Anscombe",
+R>                                    date = "1973")),
+R>   ld_make_chunks(ld))
 R> 
+R> # Write the document.
+R> writeLines("anscome-example.rmd")
+R> 
+R> # Show the document.
 R> doc
 \end{CodeInput}
+\end{CodeChunk}
+
+\begin{CodeChunk}
 
@@
 R> 
-R> #cat(paste(ld_make_chunks(ld)[1:7], collapse = "\n"))
+R> # Show the updated chunk where the library is loaded and data is read.
 R> ld_make_chunks(ld)[1:7]
@@
 a document, then \pkg{listdown} may make the generation of their
-presentation more convenient. However, it does not relieve the burden of
-the author to create prose developing a narrative.
+presentation more convenient. Narrative components can even by created
+in \pkg{listdown} by including \code{character} elements with a chunk
+option decorator setting \code{results = "as.is"}. However, it does not
+relieve the burden of the author to create prose developing a narrative.
 
@@
 R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-R>      fig.height = 4.5}
+R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
 R> datatable(cc_list$`Survival Plots`$`Overall {.tabset}`$Table)

### 2020-07-15 inst/jss/supplemental-material/listdown-jss.rmd
Addressing JSS suggestions.

@@
     email: michael.kane@yale.edu
-  - name: Xun (Tony) Jian
+  - name: Xun (Tony) Jiang
     affiliation: Amgen Inc
@@
 While these documents are generally not complete in the sense that they will not include prose content, generated by an author to provide context, a narrative, etc., programmatic generation can provide substantial efficiencies for structuring and constructing documents.
-This paper explores the programmatic generation of reproducible by distinguishing components than can be created by computational means from those requiring human-generated prose, providing guidelines for the generation of these documents, and identifying a use case in clinical trial reporting.
+This paper explores the programmatic generation of reproducible by distinguishing components that can be created by computational means from those requiring human-generated prose, providing guidelines for the generation of these documents, and identifying a use case in clinical trial reporting.
 These concepts and use case are illustrated through the \pkg{listdown} package for the \proglang{R} programming environment, which is is currently available on the Comprehensive R Archive Network (CRAN).
@@
 By separating these components each can be developed independently.
-At the same time, by specifying a contract for the output of those objects, we can establish a consistent means by which processed data can be passed to systems for presentating those data in a structured way.
+At the same time, by specifying a contract for the output of those objects, we can establish a consistent means by which processed data can be passed to systems for presenting those data in a structured way.
 The second reason for programmatic creation of R Markdown documents is convenience.
@@
 
-One area where we have found \pkg{listdown} is particuarly useful is in the reporting and research of clinical trial data.
+One area where we have found \pkg{listdown} is particularly useful is in the reporting and research of clinical trial data.
 These collaborations tend to be between (bio)statisticians and clinicians either analyzing past trial data to formulate a new trial or in trial monitoring where trial telemetry (enrollment, responses, etc.) is reported and initial analyses are conveyed to a clinician.
-The associated presentations require very little context - clinicians often have a better understanding of the data collected than the statistician - often eliminating the need for narrative components.
-At the same time, a large number of hierarchical, heterogenous artifacts (tables and multiple types of plots) need to be conveyed thereby making the manual creation of \proglang{R} Markdown documents inconvenient.
+The associated presentations require very little context - clinicians often have as good an understanding of the data collected as that of the statistician's - often eliminating or significantly reducing the need for narrative components.
+At the same time, a large number of hierarchical, heterogeneous artifacts (tables and multiple types of plots) need to be conveyed thereby making the manual creation of \proglang{R} Markdown documents inconvenient.
 
@@
 To date, we have used listdown to report on five clinical trials, with another two currently in process.
-Results are disseminated using the \pkg{workflowr} package, usually with nine tabs conveying aspects of the data from collection through several different analyses, and each tab containing approxiately five to thirty tables, plots, or other artifacts including \pkg{trelliscopejs} [@trelliscopejs] environments which may hold hundreds of graphs.
+Results are disseminated using the \pkg{workflowr} package, usually with nine tabs conveying aspects of the data from collection through several different analyses, and each tab containing approximately five to thirty tables, plots, or other artifacts including \pkg{trelliscopejs} [@trelliscopejs] environments which may hold hundreds of graphs.
 By generating many presentation artifacts we are able to address data-drive questions and issues during collaborative sessions and by carefully structuring these elements we allowing all members to participate in the process.
@@
 \item{\bf ld\_workflowr\_header() }{- create a worflowr header}
-\item{\bf listdown() }{- create a listdown object to create an R Markdown document}
+\item{\bf listdown() }{- create a listdown object to create an \proglang{R} Markdown document}
+\item{\bf print.listdown()}{- print the listdown options for \proglang{R} Markdown document creation}
 \end{itemize}
 
-The rest of this paper is structured as follow.
+The rest of this paper is structured as follows.
 The next section goes over basic usage and commentary.
@@
 However, it is important to realize that even for analyses on large-scale data, the digital artifacts to be presented are relatively small.
-Centralizing them makes it easier to access them, since they don't need to be found in mulitple locations.
+Centralizing them makes it easier to access them, since they don't need to be found in multiple locations.
 Also, storing them as a list provides a hierarchical structure that translates directly to a document as we will see below.
 
-As a first example, we will consider the a list of visualizations from the anscombe data set.
-The list is composed of four \pkg{ggplot2} [@wickham2016]elements (named Linear, Non Linear, Outlier Vertical, and Outlier Horizontal) each containing a scatter plot from the famous Anscome Quartet - made available in the \pkg{datasets} package [@R].
-From the `computational_components` list, we would like to create a document with four sections with names corresponding to the list names, each containing their respective visualizations.
+As a starting point, we will consider the a list of visualizations from the Anscombe data set below.
+The list is composed of four \pkg{ggplot2} [@wickham2016] elements (named Linear, Non Linear, Outlier Vertical, and Outlier Horizontal) each containing a scatter plot from the Anscombe Quartet - made available in the \pkg{datasets} package [@R] as shown in Figure \ref{cc1}.
+From the \code{computational_components} list, we would like to create a document with four sections with names corresponding to the list names, each containing their respective visualizations.
+The structure of a document derived from the \code{computational_components} list can be visualized using the \code{ld_cc_dendro()} function, and its output is below.
 
-```{r}
-# Use ggplot2 to create the visualizations.
+```{r cc1}
 library(ggplot2)
 
-# Load the Anscombe Quartet.
+library(listdown)
+
 data(anscombe)
 
-# Create the ggplot objects to display.
 computational_components <- list(
@@
 
-# Save the file to disk to be read by the output R Markdown document.
-saveRDS(computational_components, "comp-comp.rds")
+ld_cc_dendro(computational_components)
 ```
@@
 
-Creating a document from the `computational_components` requires two steps.
-First, we will create a `listdown` object that specifies how the `computational_components` object will be loaded into the document,  which libraries and code needs to be included, and how the list elements will be presented in the output R markdown document.
+Creating a document whose structure and content are described \code{computational_components} requires two steps. First, we will create a \code{listdown} object specifying how the \newline
+\code{computational_components} object will be loaded into the document, which libraries and code needs to be included, and how the list elements will be presented in the output R markdown document.
+A human-readable \code{print} function is included in the package and is the default output of the object.
+It should be noted that the output shows options that will be described and illustrated later.
 
 ```{r}
-library(listdown)
+saveRDS(computational_components, "comp-comp.rds")
 
@@
                package = "ggplot2")
+
+ld
 ```
 
-The `ld` object, along with the computational components in the `comp-comp.rds` file are sufficient to to create the sections, subsections, and R chunks of a document.
+The \code{ld} object, along with the computational components in the \code{comp-comp.rds} file are sufficient to to create the sections, subsections, and \proglang{R} chunks of a document.
 The only other thing requires to create the document is the header.
 The listdown package currently supports regular R Markdown and \pkg{workflowr} as \code{yml} objects from the \pkg{yaml} package [@yaml].
-These objects are stored as named lists in R and are easily modified to accomodate document parameters.
+These objects are stored as named lists in \proglang{R} and are easily modified to accommodate document parameters.
 A complete document can then be written to the console using the code shown below.
-It could easily be written to a file for rendering using the `writeLines()` function.
+It could easily be written to a file for rendering using the \code{writeLines()} function, for example.
 
-```{r}
+```{r eval = FALSE}
+doc <- c(
+  as.character(ld_rmarkdown_header("Anscombe's Quartet",
+                                   author = "Francis Anscombe",
+                                   date = "1973")),
+  ld_make_chunks(ld))
+
+writeLines("anscome-example.rmd")
+
+doc
+```
+
+```{r eval = TRUE, echo = FALSE}
 doc <- c(
@@
 
-The `listdown()` function provides _document-wide_ R chunk options for displaying computational components.
+The \code{listdown()} function provides _document-wide_ R chunk options for displaying computational components.
 The chunk options are exactly the same as those in the R markdown document and can be used to tailor the default presentation for a variety of needs.
@@
 
-#cat(paste(ld_make_chunks(ld)[1:7], collapse = "\n"))
 ld_make_chunks(ld)[1:7]
@@
 For example, suppose that, along with showing graphs from the Anscombe Quartet, we would like to include the data themselves.
-We could add the data to the `computational_components` list and then create the document with:
+We could add the data to the \code{computational_components} list and then create the document with:
 
@@
 This is common, especially when the data set is large and requires too much vertical space in the outputted document resulting in too much or irrelevant data being shown.
-Instead, we would like to output to an html document where the data is shown in a `datatable` thereby controlling the amount of real-estate needed to present the data and, at the same time, providing the user with interactivity to sort and search the data set.
+Instead, we would like to output to an html document where the data is shown in a \code{datatable} thereby controlling the amount of real-estate needed to present the data and, at the same time, providing the user with interactivity to sort and search the data set.
 
@@
 A decorator takes the element that will be presented as an argument and returns an object for presentation in the output directory.
-A decorator is specified using the `decorator` parameter of the `listdown()` function using a named list where the name corresponds to the type and the element correspond to the function or method that will decorate an object of that type.
-For example, the `anscombe` data set can be decorated with the `DT::datatable()` function [@xie2020] as:
+A decorator is specified using the \code{decorator} parameter of the \code{listdown()} function using a named list where the name corresponds to the type and the element correspond to the function or method that will decorate an object of that type.
+For example, the \code{anscombe} data set can be decorated with the \code{DT::datatable()} function [@xie2020] as:
 
@@
 
-List names in the `decorator` argument provide a key to which a function or method is mapped.
-The underlying decorator resolution is implemented for a given computational component by going through decorator names sequentially to see if the component inherits from the name using the `inherits()` function.
+List names in the \code{decorator} argument provide a key to which a function or method is mapped.
+The underlying decorator resolution is implemented for a given computational component by going through decorator names sequentially to see if the component inherits from the name using the \code{inherits()} function.
 The function or method is selected from the corresponding name which the element first inherits from.
@@
 It should be noted that an object's type is first checked against the decorator name list and then checked to see if it is a list.
-This allows a user to both decorate a list and retain `"list"` in its class attributes.
+This allows a user to both decorate a list and retain \code{"list"} in its class attributes.
 
-A separate argument, `default_decorator`, allows the user to specify the default decorator for an object whose type does not appear in the `decorator` list.
+A separate argument, \code{default_decorator}, allows the user to specify the default decorator for an object whose type does not appear in the \code{decorator} list.
 This allows the user to specify any class name for the decorator and avoids a potential type name collision with a default decorator whose name is determined by convention.
-By default, this argument is set to `identity` but it can be use to not display a computational component by default if the argument is set to `NULL`.
+By default, this argument is set to \code{identity} but it can be use to not display a computational component by default if the argument is set to \code{NULL}.
 
@@
 The latter has three subsections "Sepal.Width", "Petal.Length", and "Colored".
-The "Colored" subsection has two sub-subsections, "Sepal.Width" and "Petal.Length".
-The structure can be seen using the `ld_cc_dendro()` function.
+The "Colored" subsection has two subsubsections, "Sepal.Width" and "Petal.Length".
+The structure can once again be seen using the \code{ld_cc_dendro()} function.
 
 ```{r}
-# Create a more hierarchical list of computational components.
 comp_comp2 <- list(
@@
 
-# Create the dendrogram.
 ld_cc_dendro(comp_comp2)
@@
 
-Both the `ld_cc_dendro()` and `ld_make_chunks()` functions work by recursively descending the computational components list depth-first.
+Both the \code{ld_cc_dendro()} and \code{ld_make_chunks()} functions work by recursively descending the computational components list depth-first.
 If the list containing and element has a name, it is written to the output as a section, subsection, subsubsection, etc.
@@
 If the visited list element is itself a list, then the same procedure is called on the child list through a recursive call.
-If the element is not a list, then it is outputted inside an R Markdown chunk in the return string using the appropropriate decorator.
+If the element is not a list, then it is outputted inside an R Markdown chunk in the return string using the appropriate decorator.
 
@@
 
-The `listdown()` function facilitates the insertion of initialization code through the `init_expr` argument.
+The \code{listdown()} function facilitates the insertion of initialization code through the \code{init_expr} argument.
 Code is inserted immediately after the libraries are loaded in the R Markdown document.
@@
 If a large number of functions are required by the target \proglang{R} Markdown document then they can be put into a file and sourced using the initial expression.
-As an example, suppose we are creating an html document and presenting data using the `datatable()` function.
+As an example, suppose we are creating an html document and presenting data using the \code{datatable()} function.
 However, we do not want to include the search capabilities provided.
-This can be easily accomplished by creating a new function, `datatable_no_search()`, created using the `partial()` function \cite{purrr} to partially apply `list(dom = 't')` to the `options` argument of `datatable`.
+This can be easily accomplished by creating a new function, \code{datatable_no_search()}, created using the \code{partial()} function \cite{purrr} to partially apply \code{list(dom = 't')} to the \code{options} argument of \code{datatable}.
 
@@
 This can be though of as a chunk-option decorator.
-The second is use for changing the options for an individual chunk in an ad-hoc manner.
+The second is use for changing the options for an individual chunk in an ad hoc manner.
 
@@
 For example, we may want to specify the height and width of a graph, but not a table.
-This is accomplished in the \pkg{listdown} package when a `listdown` object is created using the `decorator_chunk_opts` option in the `listdown()` function.
-For example, associating all `ggplot` objects with \proglang{R} chunks having a width of 100 and a height of 200 can be accomplished with the following code and it can be seen that only chunk options associated with a plot are modified.
+This is accomplished in the \pkg{listdown} package when a \code{listdown} object is created using the \code{decorator_chunk_opts} option in the ]code{listdown()} function.
+For example, associating all \code{ggplot} objects with \proglang{R} chunks having a width of 100 and a height of 200 can be accomplished with the following code and it can be seen that only chunk options associated with a plot are modified.
 
@@
 Along with providing decorator-wide chunk options, it is also possible to control individual chunk options.
-The capability is distinct from the document-wide and decorator-wide specification of options in that it must be applied to the computational component list element whose associated options will be modified, rather than the `listdown` object.
-This is because the `listdown` only specifies how classes of objects should be presented.
-To modify the chunk options associated with a specific list element the list element is provided with a set of attributes that can be queried by the `ld_chunk_opts()` function as the output document is being generated.
+The capability is distinct from the document-wide and decorator-wide specification of options in that it must be applied to the computational component list element whose associated options will be modified, rather than the \code{listdown} object.
+This is because the \code{listdown} only specifies how classes of objects should be presented.
+To modify the chunk options associated with a specific list element the list element is provided with a set of attributes that can be queried by the \code{ld_chunk_opts()} function as the output document is being generated.
 Because of the ad hoc nature of this capability, its use is discouraged.
@@
 For this use case, the context and data collection procedures are well-understood and as a result very few narrative components are needed.
-It is also the case that the modes of presentation (tables, scatterplots, survivalplots, consort diagrams, etc.) are standardized.
+It is also the case that the modes of presentation (tables, scatterplots, survival plots, consort diagrams, etc.) are standardized.
 The goal in presenting the trial characteristics is to identify problems in the data, monitor trial enrollment and response, quantify known relationships among the data, and test hypotheses about a therapy's efficacy.
@@
 These facts, coupled with the privacy constraints make a complete example difficult for the purposes of this paper.
-So, below we provide a simple example of the types of documents we provide using the `gtsummary::trial` dataset.
+So, below we provide a simple example of the types of documents we provide using the \code{gtsummary::trial} data set.
 While it is not complete, it does convey they types of reports we are currently generating for completed and ongoing clinical trials.
@@
 
-# Function to create the computational components.
 make_surv_cc <- function(trial, treat, surv_cond_chars) {
-  # Create Table 1 by treatment
   table_1 <- trial %>%
@@
 
-  # Create survival plots base on survival characteristics
   scs <- lapply(c("1", surv_cond_chars),
@@
 
-# Create the computational components and write to surv-cc.rds.
 surv_cc <- make_surv_cc(trial, treat = "trt",
@@
 
-As shown before, the report is created by saving the computational components, creating a listdown object, writing the \proglang{R} Markdown document, and rendering it.
-The resulting document, trial-report.html, can then be placed in a shared space where it can be viewed and interpreted by stakeholders in the clincial trial.
-The \proglang{R} Markdown document created by this code is shown in Appendix 1.
+As shown before, the report is created by saving the computational components, creating a \code{listdown} object, writing the \proglang{R} Markdown document, and rendering it.
+The resulting document, trial-report.html, can then be placed in a shared space where it can be viewed and interpreted by stakeholders in the clinical trial.
+The \proglang{R} Markdown document created by this code is shown in supplementary materials.
 
 ```{r eval = TRUE, message = FALSE, warning = FALSE}
-# Turn the survplots into a list to show the individual components.
 class(surv_cc$`Survival Plots`$Overall) <- 
@@
 
-# Create a tab for each element of the survplot.
 names(surv_cc$`Survival Plots`) <- 
@@
 
-# Rename the elements
 names(surv_cc$`Survival Plots`$`Overall {.tabset}`) <- 
@@
 
-# Save the updated object for presentation.
 saveRDS(surv_cc, "surv-cc.rds")
 
-# Create the listdown object with appropriate dependencies
-# and presentation parameters.
 ld_surv <- listdown(load_cc_expr = readRDS("surv-cc.rds"),
@@
 
-# Write an RMarkdown header and chunks derived from the 
-# computational components and listdown object to trial-report.rmd.
 writeLines(
@@
 
-# Render the RMarkdown file to html and show it.
 render("trial-report.rmd", quiet = TRUE)
 browseURL("trial-report.html")
-
 ```
@@
 
-While the programmtic generation of reproducible documents has appealing qualities, it also has fundamental limitations that should be kept in mind when deciding if tools like \pkg{listdown} should be employed.
+While the programmatic generation of reproducible documents has appealing qualities, it also has fundamental limitations that should be kept in mind when deciding if tools like \pkg{listdown} should be employed.
 First and foremost, without narrative components a document has very little context.
@@
 This means that if narrative components must be conveyed in a document, then \pkg{listdown} may make the generation of their presentation more convenient.
+Narrative components can even by created in \pkg{listdown} by including \code{character} elements with a chunk option decorator setting \code{results = "as.is"}.
 However, it does not relieve the burden of the author to create prose developing a narrative.
 
-Second, it is difficult if not impossible to construct computational components for an arbitary analyses.
+Second, it is difficult if not impossible to construct computational components for an arbitrary analyses.
 Analyses themselves have context and are built with a set of assumptions and goals.
@@
 This means a standard set of table and visualizations for similarly formatted data.
-In particular, data that is periodicaly updated, without changes to the format, is a case that is particularly amenable to document generation reuse.
+In particular, data that is periodically updated, without changes to the format, is a case that is particularly amenable to document generation reuse.
 
@@
 \bibliography{../references}
-
-\section*{Appendix 1: R Markdown produced in the simple example}
-\label{appendix}
-
-```{r eval = FALSE}
----
-title: Simple Trial Report
-output: html_document
----
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-library(gtsummary)
-library(flextable)
-library(DT)
-library(ggplot2)
-
-cc_list <- readRDS("surv-cc.rds")
-\```
-
-# Table 1
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-cc_list$`Table 1`
-\```
-
-# Survival Plots
-
-## Overall {.tabset}
-
-### Plot
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 6}
-cc_list$`Survival Plots`$`Overall {.tabset}`$Plot
-\```
-
-### Data
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-datatable(cc_list$`Survival Plots`$`Overall {.tabset}`$Data)
-\```
-
-### Table
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-datatable(cc_list$`Survival Plots`$`Overall {.tabset}`$Table)
-\```
-
-## Stage {.tabset}
-
-### Plot
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 6}
-cc_list$`Survival Plots`$`Stage {.tabset}`$Plot
-\```
-
-### Data
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-datatable(cc_list$`Survival Plots`$`Stage {.tabset}`$Data)
-\```
-
-### Table
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-datatable(cc_list$`Survival Plots`$`Stage {.tabset}`$Table)
-\```
-
-## Grade {.tabset}
-
-### Plot
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 6}
-cc_list$`Survival Plots`$`Grade {.tabset}`$Plot
-\```
-
-### Data
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-datatable(cc_list$`Survival Plots`$`Grade {.tabset}`$Data)
-\```
-
-### Table
-
-\```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-datatable(cc_list$`Survival Plots`$`Grade {.tabset}`$Table)
-\```
-```

### 2020-07-15 R/chunk-writer.r

@@ -95,6 +95,100 @@ listdown <- function(load_cc_expr,
   ret
 }
 
+#' @importFrom crayon yellow bold
+#' @export
+print.listdown <- function(x, ...) {
+  cat(bold("\nListdown object description\n"))
+  cat("\n")
+  if ("package" %in% names(x)) {
+    cat(bold("Package(s) imported:\n"))
+    for (package in x$package) {
+      cat("\t", package, "\n", sep = "")
+    }
+  } else {
+    warning(yellow("No packages imported."))
+  }
+  if ("init_expr" %in% names(x)) {
+    cat("\n")
+    cat(bold("Initial expression(s) (run after packages are loaded):\n"))
+    cat("\t")
+    if (length(x$init_expr) == 0) {
+      cat("(none)\n")
+    } else {
+      cat(deparse(x$init_expr), sep = "\n\t")
+    }
+  }
+  if ("load_cc_expr" %in% names(x)) {
+    cat("\n")
+    cat(bold("Expression to read data:\n"))
+    cat("\t", deparse(x$load_cc_expr), "\n", sep = "")
+  } else {
+    warning(yellow("No load_cc expression provided."))
+  }
+  if ("decorator" %in% names(x)) {
+    cat("\n")
+    cat(bold("Decorator(s):\n"))
+    if (length(x$decorators) == 0) {
+      cat("\t(none)\n")
+    } else {
+      ns <- format(c("Type", names(x$decorator)))
+      cv <- c("Method", as.vector(unlist(sapply(x$decorator, deparse))))
+      for (i in seq_along(ns)) {
+        if (i == 1) {
+          cat("\t", bold(ns[i]), "\t", bold(cv[i]), "\n", sep = "")
+        } else {
+          cat("\t", ns[i], "\t", cv[i], "\n", sep = "")
+        }
+      }
+    }
+  }
+  if ("default_decorator" %in% names(x)) {
+    cat("\n")
+    cat(bold("Defaut decorator:\n"))
+    cat("\t", deparse(x$default_decorator), "\n", sep = "")
+  }
+  if ("chunk_opts" %in% names(x)) { 
+    cat("\n")
+    cat(bold("Chunk option(s):\n"))
+    if (length(x$chunk_opts) == 0) {
+      cat("\t(none)\n")
+    } else {
+      for (i in seq_len(x$chunk_opts)) {
+        cat("\t", names(x$chunk_opts)[i], " ", deparse(x$chunk_opts[[i]]), "\n",
[…]

### 2020-07-15 inst/jss/supplemental-material/clean.sh

@@ -1,7 +1,8 @@
 #! /bin/sh
-rm *.rds 
-rm *.pdf 
-rm *.tex 
-rm *.html 
+rm -f *.rds 
+rm -f *.pdf 
+rm -f *.tex 
+rm -f *.html 
+rm -f *.md
 rm -rf figure 
-rm trial-report.rmd
+rm -f trial-report.rmd

### 2020-07-15 inst/jss/supplemental-material/make.sh

@@ -1,0 +1,4 @@
+#!/usr/bin/sh
+
+Rscript -e "knitr::knit('listdown-jss.rmd', tangle = TRUE)"
+Rscript -e "knitr::knit('listdown-jss.rmd')"

### 2020-07-15 tests/testthat/test-make-chunks.r

@@ -41,10 +41,14 @@ ld <- listdown(load_cc_expr = readRDS("reference-data/test_list.rds"),
                  }
                })
 
-
 test_that("A listdown object can be created.", {
   expect_true(inherits(ld, "listdown"))
 })
+
+print(ld)
+#test_that("A listdown object can be printed.", {
+#  expect_equal(ld, print.listdown(ld))
+#})
 
 # Create the RMarkdown string.
 

### 2020-07-15 README.rmd
Styled.
Badge.

@@
 <!-- badges: start -->
+[![](https://www.r-pkg.org/badges/version/listdown?color=blue)](https://cran.r-project.org/package=listdown)
 [![Build Status](https://travis-ci.org/kaneplusplus/listdown.svg?branch=master)](https://travis-ci.org/kaneplusplus/listdown)
@@
 [![codecov](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown)
+[![](http://cranlogs.r-pkg.org/badges/last-month/listdown?color=blue)](https://cran.r-project.org/package=listdown)
 <!-- badges: end -->
@@
 is separated from their creation. For this use case, a data processing (or analysis) is performed
-and the results are provided in a single named list, organized heirarchically.
+and the results are provided in a single named list, organized hierarchically.
 With the list and a {listdown} object a workflowr, pdf, word, or html page.

### 2020-07-27 inst/jss/supplemental-material/listdown-jss.rmd
Updates.

@@
   - name: Xun (Tony) Jiang
-    affiliation: Amgen Inc
+    affiliation: Amgen Inc.
     address:

### 2020-07-27 R/depth-first-pres-list-visitor.r

@@ -23,7 +23,7 @@ list_loc_ind_to_name <- function(pl, env = parent.frame(n = 2)) {
     idx <- substr(pl, re[i], re[i] + re_len[i] - 1)
     idx_name <- names(epp(ret, last_index_as_list(idx)))
     # Wrap in backticks if the names isn't a valid variable name.
-    if (idx_name != make.names(idx_name)) {
+    if (!is.null(idx_name) && idx_name != make.names(idx_name)) {
       idx_name <- paste0("`", idx_name, "`")
     }
     ret <- paste0(

### 2020-07-27 tests/testthat/test-list.r
Prep for release.

@@ -1,0 +1,31 @@
+context("Write file")
+
+library(ggplot2)
+
+source("make-reference.r")
+
+if (make_reference) {
+  dir.create("reference-data", showWarnings = FALSE)
+}
+
+cc_list <- list(
+  Linear = list(
+    ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+    iris[1:10,]))
+
+rds_file <- "cc-list-2.rds"
+
+saveRDS(cc_list, file = rds_file)
+
+ld <- listdown(readRDS("cc-list-2.rds"), package = "ggplot2")
+
+test <- ld_make_chunks(ld)
+
+if (make_reference) {
+  saveRDS(test, file.path("reference-data/ld-cc-list-2-output.rds"))
+}
+
+expect_equal(readRDS(file.path("reference-data/ld-cc-list-2-output.rds")),
+             test)
+
+unlink("cc-list-2.rds")

### 2020-07-27 tests/testthat/test-write-file.r

@@ -1,0 +1,46 @@
+context("Write file")
+
+library(ggplot2)
+
+source("make-reference.r")
+
+if (make_reference) {
+  dir.create("reference-data", showWarnings = FALSE)
+}
+
+
+cc_list <- list(
+  Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+  `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
+  `Outlier Vertical` = ggplot(anscombe, aes(x = x3, y = y3)) + geom_point(),
+  `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + geom_point(),
+  a = list(b = 3, 4))
+
+rds_file <- "cc-list.rds"
+saveRDS(cc_list, file = rds_file)
+
+read_rds_str <- paste0("readRDS('", rds_file, "')")
+
+ld <- listdown(readRDS("cc-list.rds"), package = "ggplot2")
+
+ld_write_file(
+  ld_rmarkdown_header(title = "The Anscombe Quartet",
+                      author = "Francis Anscombe",
+                      date = "1973"),
+  ld,
+  "anscombe-quartet.rmd")
+
+if (make_reference) {
+  ld_write_file(
+    ld_rmarkdown_header(title = "The Anscombe Quartet",
+                        author = "Francis Anscombe",
+                        date = "1973"),
+    ld,
+    file.path("reference-data", "anscombe-quartet.rmd"))
+}
+
+expect_equal(readLines("anscombe-quartet.rmd"), 
+             readLines(file.path("reference-data", "anscombe-quartet.rmd")))
+
+unlink("anscombe-quartet.rmd")
+unlink("cc-list.rds")

### 2020-10-17 inst/jss/pre-review-response.md
Decorators can take the returns of functions.

# Pre-comment response

We would like to thank the editors for their comments and suggestions. We have made considerable changes to both the submission as well as the package based on the feedback provided. Below we address and discuss each of the issues provided.

# Response to the general comments from the editorial team

We have restructured the document and added text describing more specifically how a computational component list's structure maps to the that of an R Markdown document. We have also added an example of the `ld_cc_dendro()` function earlier in the document to illustrate the correspondence between the list and the document.

The progression of the examples has also been revised so that the example builds progressively in complexity and sophistication. We hope that this change allows the reader to digest successively more elaborate concepts and functionality facilitated by the package. However, we would like to remind the reviewers that the goal of the package is to address the creation of the presentation of results in the context described. It is not meant to address how those results are derived. We have added emphasis to this in Section 5.

The advantages and limitations of both the automated reproducible document generation and package are given in Section 1 and the discussion in Section 6. Section 5 and 6 describe those situations for which the package has been shown useful.

The comment concerning the "monolithicness" of the presentation is somewhat difficult to understand. The package itself adrresses the problem creating reproducible documents via lists and, in this sense, the task is singular and perhaps this is the motivation for the comment. However, the conceptual contribution is the separation of narrtive from computational components along with the analysis and dicussion of this characterization and it's consequences. The technical contribution is the implementation of this capability in a way that is general, flexible, and easy to integrate into data processing pipelines. An earlier version of the manuscript was sufficient for analysts (intermediate R users) to create reproducible documents for reporting to clinicians with little to no extra instruction. The manuscript should be sufficent for the reader to understand the underlying concepts, understand how to automate R Markdown document generation for a variety of different types of documents and document types, and extend the use of the package to the users own needs. The paper is not meant to show readers how to create complete reports for a specific domain and the clinical trial example is only meant to illustrate one outlet for the package, which we have found useful. If there are specific suggestions for how else to address this issue, we would be happy to incorporate them.

# Further comments

The manuscript needs to be spell-checked and proofread. The manuscript in its current form is not suitable for review.

- Hopefully it is in the current form.

A print method should be added for listdown objects.

- This is included in the newest revision of the package and is described in the paper.

As replication material an R script, e.g., by purling the Rmd file and  editing the R script output such that it is in a human readable form, needs to be provided.

- This is included in the updated `supplemental-materials` directory.

The submitted package version and the version on CRAN are out of sync. An updated version should be submitted to JSS.

- We have uploaded version 0.2.21 to CRAN and included it in this submission.

Appendix 1 can be omitted, but rather included in plain text form in a standalone file in the supplementary material.

- Done, thanks for the suggestion.

For referring to subsections, do not use Subsection x.y, just Section x.y.

- This has been done. Please note that we do describe creating "subsections" and "subsubsection" in the text and that should be distinguished from the references.

The code presented in the manuscript should not contain comments within the verbatim code. Instead the comments should be made in the normal LaTeX text.

- Done.

For the code layout in R publications, we typically distinguish input/output using Sinput/Soutput (or equivalently CodeInput/CodeOutput). Unless there are special reasons to format it differently, the input should use the text width (up to 76 or 77 characters) and be indented by two spaces, e.g.,

- Done.

As a reminder, please make sure that \proglang, \pkg and \code have been used for highlighting throughout the paper (including titles and references), except where explicitly escaped.

- Done.

Springer-Verlag (not: Springer) ysis.” In Compstat, pp. 575–580. Springer.

- Done. Thanks for pointing this out.

Please make sure that all software packages are cite'd properly.

- Done.

All references should be in title style.

- Done

Please make sure that the files needed to replicate all code/examples within the manuscript are included in a standalone replication script

- Done

### 2020-10-17 inst/jss/supplemental-material/listdown-jss.tex
Decorators can take the returns of functions.

--- 2020-07-15 inst/jss/listdown-jss.tex
@@
 Michael Kane\\Yale University \And Xun (Tony) Jiang\\Amgen
-Inc \And Simon Urbanek\\The University of Aukland
+Inc. \And Simon Urbanek\\The University of Aukland
 }
@@
       Xun (Tony) Jiang\\
-  Amgen Inc\\
+  Amgen Inc.\\
   One Amgen Center DriveThousand Oaks, CA 91320-1799, USA\\
@@
 a consistent means by which processed data can be passed to systems for
-presentating those data in a structured way. The second reason for
+presenting those data in a structured way. The second reason for
 programmatic creation of R Markdown documents is convenience. In
@@
 components. At the same time, a large number of hierarchical,
-heterogenous artifacts (tables and multiple types of plots) need to be
+heterogeneous artifacts (tables and multiple types of plots) need to be
 conveyed thereby making the manual creation of \proglang{R} Markdown
@@
 tabs conveying aspects of the data from collection through several
-different analyses, and each tab containing approxiately five to thirty
+different analyses, and each tab containing approximately five to thirty
 tables, plots, or other artifacts including \pkg{trelliscopejs}
@@
 \item{\bf ld\_workflowr\_header() }{- create a worflowr header}
-\item{\bf listdown() }{- create a listdown object to create an R Markdown document}
+\item{\bf listdown() }{- create a listdown object to create an \proglang{R} Markdown document}
+\item{\bf print.listdown()}{- print the listdown options for \proglang{R} Markdown document creation}
 \end{itemize}
@@
 them makes it easier to access them, since they don't need to be found
-in mulitple locations. Also, storing them as a list provides a
+in multiple locations. Also, storing them as a list provides a
 hierarchical structure that translates directly to a document as we will
@@
 
-As a first example, we will consider the a list of visualizations from
-the anscombe data set. The list is composed of four \pkg{ggplot2}
-\citep{wickham2016}elements (named Linear, Non Linear, Outlier Vertical,
-and Outlier Horizontal) each containing a scatter plot from the famous
-Anscome Quartet - made available in the \pkg{datasets} package
-\citep{R}. From the \texttt{computational\_components} list, we would
-like to create a document with four sections with names corresponding to
-the list names, each containing their respective visualizations.
+As a starting point, we will consider the a list of visualizations from
+the Anscombe data set below. The list is composed of four \pkg{ggplot2}
+\citep{wickham2016} elements (named Linear, Non Linear, Outlier
+Vertical, and Outlier Horizontal) each containing a scatter plot from
+the Anscombe Quartet - made available in the \pkg{datasets} package
+\citep{R} as shown in Figure \ref{cc1}. From the
+\code{computational_components} list, we would like to create a document
+with four sections with names corresponding to the list names, each
+containing their respective visualizations. The structure of a document
+derived from the \code{computational_components} list can be visualized
+using the \code{ld_cc_dendro()} function, and its output is below.
 
@@
 \begin{CodeInput}
-R> # Use ggplot2 to create the visualizations.
 R> library(ggplot2)
 R> 
-R> # Load the Anscombe Quartet.
+R> library(listdown)
+R> 
 R> data(anscombe)
 R> 
-R> # Create the ggplot objects to display.
 R> computational_components <- list(
@@
 R> 
-R> # Save the file to disk to be read by the output R Markdown document.
-R> saveRDS(computational_components, "comp-comp.rds")
+R> ld_cc_dendro(computational_components)
 \end{CodeInput}
+
+\begin{CodeOutput}
+
+computational_components
+  |-- Linear
+  |  o-- object of type(s):gg ggplot
+  |-- Non Linear
+  |  o-- object of type(s):gg ggplot
+  |-- Outlier Vertical
+  |  o-- object of type(s):gg ggplot
+  o-- Outlier Horizontal
+     o-- object of type(s):gg ggplot
+\end{CodeOutput}
 \end{CodeChunk}
@@
 
-Creating a document from the \texttt{computational\_components} requires
-two steps. First, we will create a \texttt{listdown} object that
-specifies how the \texttt{computational\_components} object will be
-loaded into the document, which libraries and code needs to be included,
-and how the list elements will be presented in the output R markdown
-document.
+Creating a document whose structure and content are described
+\code{computational_components} requires two steps. First, we will
+create a \code{listdown} object specifying how the \newline
+\code{computational_components} object will be loaded into the document,
+which libraries and code needs to be included, and how the list elements
+will be presented in the output R markdown document. A human-readable
+\code{print} function is included in the package and is the default
+output of the object. It should be noted that the output shows options
+that will be described and illustrated later.
 
@@
 \begin{CodeInput}
-R> library(listdown)
+R> saveRDS(computational_components, "comp-comp.rds")
 R> 
@@
 R+                package = "ggplot2")
+R> 
+R> ld
 \end{CodeInput}
+
+\begin{CodeOutput}
+
+Listdown object description
+
+Package(s) imported:
+    ggplot2
+
+Initial expression(s) (run after packages are loaded):
+    (none)
+
+Expression to read data:
+    readRDS("comp-comp.rds")
+
+Decorator(s):
+    (none)
+
+Defaut decorator:
+    identity
+
+Chunk option(s):
+    (none)
+
+Decorator chunk option(s):
+    (none)
+\end{CodeOutput}
 \end{CodeChunk}
 
-The \texttt{ld} object, along with the computational components in the
-\texttt{comp-comp.rds} file are sufficient to to create the sections,
-subsections, and R chunks of a document. The only other thing requires
-to create the document is the header. The listdown package currently
-supports regular R Markdown and \pkg{workflowr} as \code{yml} objects
-from the \pkg{yaml} package \citep{yaml}. These objects are stored as
-named lists in R and are easily modified to accomodate document
-parameters. A complete document can then be written to the console using
-the code shown below. It could easily be written to a file for rendering
-using the \texttt{writeLines()} function, for example.
+The \code{ld} object, along with the computational components in the
+\code{comp-comp.rds} file are sufficient to to create the sections,
+subsections, and \proglang{R} chunks of a document. The only other thing
+requires to create the document is the header. The listdown package
+currently supports regular R Markdown and \pkg{workflowr} as \code{yml}
+objects from the \pkg{yaml} package \citep{yaml}. These objects are
+stored as named lists in \proglang{R} and are easily modified to
+accommodate document parameters. A complete document can then be written
+to the console using the code shown below. It could easily be written to
+a file for rendering using the \code{writeLines()} function, for
+example.
 
@@
 R> 
-R> # Write the document.
 R> writeLines("anscome-example.rmd")
 R> 
-R> # Show the document.
 R> doc
@@
 
-The \texttt{listdown()} function provides \emph{document-wide} R chunk
+The \code{listdown()} function provides \emph{document-wide} R chunk
 options for displaying computational components. The chunk options are
@@
 R> 
-R> # Show the updated chunk where the library is loaded and data is read.
 R> ld_make_chunks(ld)[1:7]
@@
 to include the data themselves. We could add the data to the
-\texttt{computational\_components} list and then create the document
-with:
+\code{computational_components} list and then create the document with:
 
@@
 \begin{CodeOutput}
-[1] "# Data"              
-[2] ""                    
-[3] "```{r echo = FALSE}"
-[4] "cc_list$Data"        
-[5] "```"                
+[1] "# Data"              ""                    "```{r echo = FALSE}"
+[4] "cc_list$Data"        "```"                
 \end{CodeOutput}
@@
 we would like to output to an html document where the data is shown in a
-\texttt{datatable} thereby controlling the amount of real-estate needed
-to present the data and, at the same time, providing the user with
+\code{datatable} thereby controlling the amount of real-estate needed to
+present the data and, at the same time, providing the user with
 interactivity to sort and search the data set.
@@
 returns an object for presentation in the output directory. A decorator
-is specified using the \texttt{decorator} parameter of the
-\texttt{listdown()} function using a named list where the name
-corresponds to the type and the element correspond to the function or
-method that will decorate an object of that type. For example, the
-\texttt{anscombe} data set can be decorated with the
-\texttt{DT::datatable()} function \citep{xie2020} as:
+is specified using the \code{decorator} parameter of the
+\code{listdown()} function using a named list where the name corresponds
+to the type and the element correspond to the function or method that
+will decorate an object of that type. For example, the \code{anscombe}
+data set can be decorated with the \code{DT::datatable()} function
+\citep{xie2020} as:
 
@@
 \begin{CodeOutput}
-[1] "# Data"                  
-[2] ""                       
-[3] "```{r}"                  
-[4] "datatable(cc_list$Data)"
+[1] "# Data"                  ""                       
+[3] "```{r}"                  "datatable(cc_list$Data)"
 [5] "```"                    
@@
 
-List names in the \texttt{decorator} argument provide a key to which a
+List names in the \code{decorator} argument provide a key to which a
 function or method is mapped. The underlying decorator resolution is
@@
 decorator names sequentially to see if the component inherits from the
-name using the \texttt{inherits()} function. The function or method is
+name using the \code{inherits()} function. The function or method is
 selected from the corresponding name which the element first inherits
@@
 checked to see if it is a list. This allows a user to both decorate a
-list and retain \texttt{"list"} in its class attributes.
+list and retain \code{"list"} in its class attributes.
 
-A separate argument, \texttt{default\_decorator}, allows the user to
+A separate argument, \code{default_decorator}, allows the user to
 specify the default decorator for an object whose type does not appear
-in the \texttt{decorator} list. This allows the user to specify any
-class name for the decorator and avoids a potential type name collision
-with a default decorator whose name is determined by convention. By
-default, this argument is set to \texttt{identity} but it can be use to
-not display a computational component by default if the argument is set
-to \texttt{NULL}.
+in the \code{decorator} list. This allows the user to specify any class
+name for the decorator and avoids a potential type name collision with a
+default decorator whose name is determined by convention. By default,
+this argument is set to \code{identity} but it can be use to not display
+a computational component by default if the argument is set to
+\code{NULL}.
 
@@
 three subsections ``Sepal.Width'', ``Petal.Length'', and ``Colored''.
-The ``Colored'' subsection has two sub-subsections, ``Sepal.Width'' and
-``Petal.Length''. The structure can be seen using the
-\texttt{ld\_cc\_dendro()} function.
+The ``Colored'' subsection has two subsubsections, ``Sepal.Width'' and
+``Petal.Length''. The structure can once again be seen using the
+\code{ld_cc_dendro()} function.
 
@@
 \begin{CodeInput}
-R> # Create a more hierarchical list of computational components.
 R> comp_comp2 <- list(
@@
 R> 
-R> # Create the dendrogram.
 R> ld_cc_dendro(comp_comp2)
@@
 
-Both the \texttt{ld\_cc\_dendro()} and \texttt{ld\_make\_chunks()}
-functions work by recursively descending the computational components
-list depth-first. If the list containing and element has a name, it is
+Both the \code{ld_cc_dendro()} and \code{ld_make_chunks()} functions
+work by recursively descending the computational components list
+depth-first. If the list containing and element has a name, it is
 written to the output as a section, subsection, subsubsection, etc. to a
@@
 the element is not a list, then it is outputted inside an R Markdown
-chunk in the return string using the appropropriate decorator.
+chunk in the return string using the appropriate decorator.
 
@@
 
-The \texttt{listdown()} function facilitates the insertion of
-initialization code through the \texttt{init\_expr} argument. Code is
+The \code{listdown()} function facilitates the insertion of
+initialization code through the \code{init_expr} argument. Code is
 inserted immediately after the libraries are loaded in the R Markdown
@@
 creating an html document and presenting data using the
-\texttt{datatable()} function. However, we do not want to include the
+\code{datatable()} function. However, we do not want to include the
 search capabilities provided. This can be easily accomplished by
-creating a new function, \texttt{datatable\_no\_search()}, created using
-the \texttt{partial()} function \cite{purrr} to partially apply
-\texttt{list(dom\ =\ \textquotesingle{}t\textquotesingle{})} to the
-\texttt{options} argument of \texttt{datatable}.
+creating a new function, \code{datatable_no_search()}, created using the
+\code{partial()} function \cite{purrr} to partially apply
+\code{list(dom = 't')} to the \code{options} argument of
+\code{datatable}.
 
@@
 decorator. The second is use for changing the options for an individual
-chunk in an ad-hoc manner.
+chunk in an ad hoc manner.
 
@@
 This is accomplished in the \pkg{listdown} package when a
-\texttt{listdown} object is created using the
-\texttt{decorator\_chunk\_opts} option in the \texttt{listdown()}
-function. For example, associating all \texttt{ggplot} objects with
-\proglang{R} chunks having a width of 100 and a height of 200 can be
-accomplished with the following code and it can be seen that only chunk
-options associated with a plot are modified.
+\code{listdown} object is created using the \code{decorator_chunk_opts}
+option in the {]}code\{listdown()\} function. For example, associating
+all \code{ggplot} objects with \proglang{R} chunks having a width of 100
+and a height of 200 can be accomplished with the following code and it
+can be seen that only chunk options associated with a plot are modified.
 
@@
 must be applied to the computational component list element whose
-associated options will be modified, rather than the \texttt{listdown}
-object. This is because the \texttt{listdown} only specifies how classes
+associated options will be modified, rather than the \code{listdown}
+object. This is because the \code{listdown} only specifies how classes
 of objects should be presented. To modify the chunk options associated
 with a specific list element the list element is provided with a set of
-attributes that can be queried by the \texttt{ld\_chunk\_opts()}
-function as the output document is being generated. Because of the ad
-hoc nature of this capability, its use is discouraged. A better
-solution, that maintains the behavior is to add class information to the
-list element and specify decorator-wide chunk options for the new class.
-This maintains the separation of the computational component list, which
+attributes that can be queried by the \code{ld_chunk_opts()} function as
+the output document is being generated. Because of the ad hoc nature of
+this capability, its use is discouraged. A better solution, that
+maintains the behavior is to add class information to the list element
+and specify decorator-wide chunk options for the new class. This
+maintains the separation of the computational component list, which
 maintains the document structure and data for presentation from the
@@
 \begin{CodeOutput}
-[1] "# Iris"             
-[2] ""                   
-[3] "```{r echo = TRUE}"
-[4] "cc_list$Iris"       
-[5] "```"               
+[1] "# Iris"             ""                   "```{r echo = TRUE}"
+[4] "cc_list$Iris"       "```"               
 \end{CodeOutput}
@@
 as a result very few narrative components are needed. It is also the
-case that the modes of presentation (tables, scatterplots,
-survivalplots, consort diagrams, etc.) are standardized. The goal in
-presenting the trial characteristics is to identify problems in the
-data, monitor trial enrollment and response, quantify known
-relationships among the data, and test hypotheses about a therapy's
-efficacy.
+case that the modes of presentation (tables, scatterplots, survival
+plots, consort diagrams, etc.) are standardized. The goal in presenting
+the trial characteristics is to identify problems in the data, monitor
+trial enrollment and response, quantify known relationships among the
+data, and test hypotheses about a therapy's efficacy.
 
@@
 simple example of the types of documents we provide using the
-\texttt{gtsummary::trial} dataset. While it is not complete, it does
+\code{gtsummary::trial} data set. While it is not complete, it does
 convey they types of reports we are currently generating for completed
@@
 R> 
-R> # Function to create the computational components.
 R> make_surv_cc <- function(trial, treat, surv_cond_chars) {
-R+   # Create Table 1 by treatment
 R+   table_1 <- trial %>%
@@
 R+ 
-R+   # Create survival plots base on survival characteristics
 R+   scs <- lapply(c("1", surv_cond_chars),
@@
 R> 
-R> # Create the computational components and write to surv-cc.rds.
 R> surv_cc <- make_surv_cc(trial, treat = "trt",
@@
 As shown before, the report is created by saving the computational
-components, creating a listdown object, writing the \proglang{R}
+components, creating a \code{listdown} object, writing the \proglang{R}
 Markdown document, and rendering it. The resulting document,
 trial-report.html, can then be placed in a shared space where it can be
-viewed and interpreted by stakeholders in the clincial trial. The
-\proglang{R} Markdown document created by this code is shown in Appendix
-1.
+viewed and interpreted by stakeholders in the clinical trial. The
+\proglang{R} Markdown document created by this code is shown in
+supplementary materials.
 
@@
 \begin{CodeInput}
-R> # Turn the survplots into a list to show the individual components.
 R> class(surv_cc$`Survival Plots`$Overall) <- 
@@
 R> 
-R> # Create a tab for each element of the survplot.
 R> names(surv_cc$`Survival Plots`) <- 
@@
 R> 
-R> # Rename the elements
 R> names(surv_cc$`Survival Plots`$`Overall {.tabset}`) <- 
@@
 R>   
-R> # Save the updated object for presentation.
 R> saveRDS(surv_cc, "surv-cc.rds")
 R> 
-R> # Create the listdown object with appropriate dependencies
-R> # and presentation parameters.
 R> ld_surv <- listdown(load_cc_expr = readRDS("surv-cc.rds"),
@@
 R> 
-R> # Write an RMarkdown header and chunks derived from the 
-R> # computational components and listdown object to trial-report.rmd.
 R> writeLines(
@@
 R> 
-R> # Render the RMarkdown file to html and show it.
 R> render("trial-report.rmd", quiet = TRUE)
@@
 
-While the programmtic generation of reproducible documents has appealing
-qualities, it also has fundamental limitations that should be kept in
-mind when deciding if tools like \pkg{listdown} should be employed.
-First and foremost, without narrative components a document has very
-little context. Quantitative analyses require research questions,
-hypotheses, reviews, interpretations, and conclusions. Computational
-components are necessary but generally not sufficient for constructing
-an analysis. This means that if narrative components must be conveyed in
-a document, then \pkg{listdown} may make the generation of their
-presentation more convenient. Narrative components can even by created
-in \pkg{listdown} by including \code{character} elements with a chunk
-option decorator setting \code{results = "as.is"}. However, it does not
-relieve the burden of the author to create prose developing a narrative.
+While the programmatic generation of reproducible documents has
+appealing qualities, it also has fundamental limitations that should be
+kept in mind when deciding if tools like \pkg{listdown} should be
+employed. First and foremost, without narrative components a document
+has very little context. Quantitative analyses require research
+questions, hypotheses, reviews, interpretations, and conclusions.
+Computational components are necessary but generally not sufficient for
+constructing an analysis. This means that if narrative components must
+be conveyed in a document, then \pkg{listdown} may make the generation
+of their presentation more convenient. Narrative components can even by
+created in \pkg{listdown} by including \code{character} elements with a
+chunk option decorator setting \code{results = "as.is"}. However, it
+does not relieve the burden of the author to create prose developing a
+narrative.
 
 Second, it is difficult if not impossible to construct computational
-components for an arbitary analyses. Analyses themselves have context
+components for an arbitrary analyses. Analyses themselves have context
 and are built with a set of assumptions and goals. Our experience shows
@@
 means a standard set of table and visualizations for similarly formatted
-data. In particular, data that is periodicaly updated, without changes
+data. In particular, data that is periodically updated, without changes
 to the format, is a case that is particularly amenable to document
@@
 
-\bibliography{references}
-
-\section*{Appendix 1: R Markdown produced in the simple example}
-\label{appendix}
-
-\begin{CodeChunk}
-
-\begin{CodeInput}
-R> ---
-R> title: Simple Trial Report
-R> output: html_document
-R> ---
-R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-R>      fig.height = 4.5}
-R> library(gtsummary)
-R> library(flextable)
-R> library(DT)
-R> library(ggplot2)
-R> 
-R> cc_list <- readRDS("surv-cc.rds")
-R> \```
-R> 
-R> # Table 1
-R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-R>      fig.height = 4.5}
-R> cc_list$`Table 1`
-R> \```
-R> 
-R> # Survival Plots
-R> 
-R> ## Overall {.tabset}
-R> 
-R> ### Plot
-R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, 
-R>      fig.height = 6}
-R> cc_list$`Survival Plots`$`Overall {.tabset}`$Plot
-R> \```
-R> 
-R> ### Data
-R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-R>      fig.height = 4.5}
-R> datatable(cc_list$`Survival Plots`$`Overall {.tabset}`$Data)
-R> \```
-R> 
-R> ### Table
-R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
-R> datatable(cc_list$`Survival Plots`$`Overall {.tabset}`$Table)
-R> \```
-R> 
-R> ## Stage {.tabset}
-R> 
-R> ### Plot
-R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, 
-R>      fig.height = 6}
-R> cc_list$`Survival Plots`$`Stage {.tabset}`$Plot
-R> \```
-R> 
-R> ### Data
-R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-R>      fig.height = 4.5}
-R> datatable(cc_list$`Survival Plots`$`Stage {.tabset}`$Data)
-R> \```
-R> 
-R> ### Table
-R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-R>      fig.height = 4.5}
-R> datatable(cc_list$`Survival Plots`$`Stage {.tabset}`$Table)
-R> \```
-R> 
-R> ## Grade {.tabset}
-R> 
-R> ### Plot
-R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, 
-R>      fig.height = 6}
-R> cc_list$`Survival Plots`$`Grade {.tabset}`$Plot
-R> \```
-R> 
-R> ### Data
-R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-R>      fig.height = 4.5}
-R> datatable(cc_list$`Survival Plots`$`Grade {.tabset}`$Data)
-R> \```
-R> 
-R> ### Table
-R> 
-R> \```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, 
-R>      fig.height = 4.5}
-R> datatable(cc_list$`Survival Plots`$`Grade {.tabset}`$Table)
-R> \```
-\end{CodeInput}
-\end{CodeChunk}
+\bibliography{../references}
 

### 2020-10-17 inst/jss/supplemental-material/trial-report.rmd
Decorators can take the returns of functions.

---
title: Simple Trial Report
output: html_document
---

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
library(gtsummary)
library(flextable)
library(DT)
library(ggplot2)

cc_list <- readRDS("surv-cc.rds")
```

# Table 1

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
cc_list$`Table 1`
```

# Survival Plots

## Overall {.tabset}

### Plot

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 6}
cc_list$`Survival Plots`$`Overall {.tabset}`$Plot
```

### Data

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
datatable(cc_list$`Survival Plots`$`Overall {.tabset}`$Data)
```

### Table

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
datatable(cc_list$`Survival Plots`$`Overall {.tabset}`$Table)
```

## Stage {.tabset}

### Plot

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 6}
cc_list$`Survival Plots`$`Stage {.tabset}`$Plot
```

### Data

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
datatable(cc_list$`Survival Plots`$`Stage {.tabset}`$Data)
```

### Table

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
datatable(cc_list$`Survival Plots`$`Stage {.tabset}`$Table)
```

## Grade {.tabset}

### Plot

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 6}
cc_list$`Survival Plots`$`Grade {.tabset}`$Plot
```

### Data

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
datatable(cc_list$`Survival Plots`$`Grade {.tabset}`$Data)
```

### Table

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7, fig.height = 4.5}
datatable(cc_list$`Survival Plots`$`Grade {.tabset}`$Table)
```

### 2020-10-17 R/chunk-writer.r

@@ -64,7 +64,11 @@ listdown <- function(load_cc_expr,
   if ( !("decorator" %in% names(match.call())) ) {
     decorator <- NULL
   } else {
-    decorator <- as.list(match.call()$decorator)[-1]
+    if (as.character(as.list(match.call()$decorator)[[1]]) == "list") {
+      decorator <- as.list(match.call()$decorator)[-1]
+    } else {
+      decorator <- eval(match.call()$decorator)
+    }
   }
   if (is.character(match.call()$load_cc_expr)) {
     # If it's a string literal, then call str2lang on it.

### 2020-10-17 inst/jss/supplemental-material/listdown-jss.R

@@ -1,0 +1,192 @@
+## ----cc1----------------------------------------------------------------------
+library(ggplot2)
+
+library(listdown)
+
+data(anscombe)
+
+computational_components <- list(
+  Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
+  `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
+  `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + 
+    geom_point(),
+  `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + 
+    geom_point())
+
+ld_cc_dendro(computational_components)
+
+
+## -----------------------------------------------------------------------------
+saveRDS(computational_components, "comp-comp.rds")
+
+ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"),
+               package = "ggplot2")
+
+ld
+
+
+## ----eval = FALSE-------------------------------------------------------------
+## doc <- c(
+##   as.character(ld_rmarkdown_header("Anscombe's Quartet",
+##                                    author = "Francis Anscombe",
+##                                    date = "1973")),
+##   ld_make_chunks(ld))
+## 
+## writeLines("anscome-example.rmd")
+## 
+## doc
+
+
+## ----eval = TRUE, echo = FALSE------------------------------------------------
+doc <- c(
+  as.character(ld_rmarkdown_header("Anscombe's Quartet",
+                                   author = "Francis Anscombe",
+                                   date = "1973")),
+  ld_make_chunks(ld))
+
+doc
+
+
+## -----------------------------------------------------------------------------
+ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
+               package = "ggplot2",
+               echo = FALSE)
+
+ld_make_chunks(ld)[1:7]
+
+
+## ----results="as.is"----------------------------------------------------------
+computational_components$Data <- anscombe
+saveRDS(computational_components, "comp-comp.rds")
+ld_make_chunks(ld)[32:36]
+
+
+## -----------------------------------------------------------------------------
+ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
+               package = c("ggplot2", "DT"),
+               decorator = list(data.frame = datatable))
+
+ld_make_chunks(ld)[33:37]
+
+
[…]

### 2020-10-17 R/chunk-writer.r
Bug in print.listdown.

@@ -132,7 +132,7 @@ print.listdown <- function(x, ...) {
   if ("decorator" %in% names(x)) {
     cat("\n")
     cat(bold("Decorator(s):\n"))
-    if (length(x$decorators) == 0) {
+    if (length(x$decorator) == 0) {
       cat("\t(none)\n")
     } else {
       ns <- format(c("Type", names(x$decorator)))

### 2020-10-17 R/depth-first-pres-list-visitor.r
Removed multiple decorator warning.

@@ -93,12 +93,11 @@ depth_first_concat <- function(cc_list, ld, heading = "#",
       decorator_index <- which(
         vapply(names(ld$decorator),
                function(x) inherits(eval(parse(text = pl)), x), NA))
-
+    
       if (length(decorator_index) > 1) {
-        warning(yellow("Multiple matches to decorator of types:",
-                       paste(names(decorator_index), collapse = " "),
-                       ".\n\nUsing the first.", sep = " "))
+        decorator_index <- decorator_index[1]
       }
+
 
       chunk_opts <- ld$chunk_opts
 
@@ -107,9 +106,7 @@ depth_first_concat <- function(cc_list, ld, heading = "#",
                function(x) inherits(eval(parse(text = pl)), x), NA))
 
       if (length(chunk_option_index) > 1) {
-        warning(yellow("Multiple matches to chunk elemet option of types:",
-                       paste(names(decorator_index), collapse = " "),
-                       ".\n\nUsing the first.", sep = " "))
+        chunk_option_index <- chunk_option_index[1]
       }
 
       if (length(chunk_option_index) == 1) {

### 2020-12-07 R/chunk-writer.r
No list decorators.

@@ -76,6 +76,10 @@ listdown <- function(package = NULL,
     } else {
       decorator <- eval(match.call()$decorator)
     }
+    if ("list" %in% names(decorator)) {
+      stop("You may not decorate a list. Consider making a list element you ",
+           "would\nlike to present a class instance and define a decorator.")
+    }
   }
   if (!is.null(load_cc_expr)) {
     load_cc_expr <- create_load_cc_expr(match.call()$load_cc_expr)

### 2020-12-07 tests/testthat/test-no-list-decorators.r

@@ -1,0 +1,6 @@
+context("Not list decorators")
+
+expect_error(listdown(load_cc_expr = list(x = 1),
+                      setup_expr = knitr::opts_chunk$set(echo = FALSE),
+                      decorator = list(list = print)))
+

### 2020-12-07 README.rmd
README updated.

@@
 
-<!--
 You can install the released version of listdown from [CRAN](https://CRAN.R-project.org) with:
@@
 
-And the development version from [GitHub](https://github.com/) with:
--->
-
-You can install the development version of {listdown} from [GitHub](https://github.com/) with:
+The development version of {listdown} can be installed from [GitHub](https://github.com/) with:
 

### 2020-12-07 README.rmd
Minor changes.

@@
 [![](http://cranlogs.r-pkg.org/badges/last-month/listdown?color=blue)](https://cran.r-project.org/package=listdown)
+[![Travis build status](https://travis-ci.com/kaneplusplus/listdown.svg?branch=master)](https://travis-ci.com/kaneplusplus/listdown)
 <!-- badges: end -->

### 2020-12-07 inst/jss/listdown-jss.tex
Minor changes.

@@
+% To remove when JSS.cls is fixed
+% https://github.com/rstudio/rticles/issues/329
+\RequirePackage[2020/02/02]{latexrelease}
 \documentclass[
@@
 the programmatic creation of documents whose content is itself
-programmatically generated. While these documents are generally not
-complete in the sense that they will not include prose content,
-generated by an author to provide context, a narrative, etc.,
+programmatically generated. While programmatic content alone may not be
+sufficient for a rendered document since it does not include prose
+(content generated by an author to provide context, a narrative, etc.)
 programmatic generation can provide substantial efficiencies for
 structuring and constructing documents. This paper explores the
-programmatic generation of reproducible by distinguishing components
-that can be created by computational means from those requiring
-human-generated prose, providing guidelines for the generation of these
-documents, and identifying a use case in clinical trial reporting. These
-concepts and use case are illustrated through the \pkg{listdown} package
-for the \proglang{R} programming environment, which is is currently
-available on the Comprehensive R Archive Network (CRAN).
+programmatic generation of reproducible documents by distinguishing
+components that can be created by computational means from those
+requiring human-generation, providing guidelines for the generation of
+these documents, and identifying a use case in clinical trial reporting.
+These concepts and use case are illustrated through the \pkg{listdown}
+package for the \proglang{R} programming environment, which is is
+currently available on the Comprehensive R Archive Network (CRAN).
 }
@@
       Xun (Tony) Jiang\\
-  Amgen Inc\\
+    Amgen Inc.\\
     One Amgen Center DriveThousand Oaks, CA 91320-1799, USA\\
@@
     The University of Aukland\\
-  38 Princes StreetAuckland Central, Aukland 1010, NZ\\
+    38 Princes StreetAuckland Central, Auckland 1010, NZ\\
   E-mail: \href{mailto:s.urbanek@auckland.ac.nz}{\nolinkurl{s.urbanek@auckland.ac.nz}}\\
@@
   }
+
+% Pandoc citation processing
 
@@
 
-\proglang{R} Markdown \citep{baumer2014} facilitates the construction of
-computationally reproducible documents by allowing authors to insert
-\proglang{R} code for data processing, exploration, analysis,
-table-making, and visualization directly into structured, electronic
-documents. The resulting documents are made up of these chunks of
-\proglang{R} code, which we will refer to as \emph{computational
-components} since they are generated by computational means, as well as
-\emph{narrative components}, which (in scientific writing) is prose
-intended to contextualize computational components, provide background,
-define goals, establish themes, and convey the results of the document.
-The integration of narrative and computational components was identified
-as ``Literate Programming'' by \citet{knuth1984} and software tools,
-like Sweave \citep{leisch2002}, have supported this functionality for
-almost two decades.
+\proglang{R} Markdown \citep[\citet{rmarkdownbook}]{baumer2014}
+facilitates the construction of computationally reproducible documents
+by allowing authors to insert \proglang{R} code for data processing,
+exploration, analysis, table-making, and visualization directly into
+structured, electronic documents. The resulting documents are made up of
+these chunks of \proglang{R} code, which we will refer to as
+\emph{computational components} since they are generated by
+computational means, as well as \emph{narrative components}, which (in
+scientific writing) is prose intended to contextualize computational
+components, provide background, define goals, establish themes, and
+convey results. These documents are then used to render output
+documents, for users to read in the form of .html, .pdf, .doc, or other
+formats using the \pkg{knitr} package \citep{knitrbook}.
 
-\proglang{R} Markdown is particularly popular with its success likely
-being driven by two factors. The first is the relative ease with which
-these documents can be constructed. While \LaTeX ~is more expressive, it
-is relatively technical and requires an investment in time to become
-proficient. By contrast \proglang{R} Markdown documents are easier to
-create and format and, when the document is used to create \LaTeX,
-formatting can be passed through to the underlying .tex file. The second
-factor driving adoption is likely its support for creating
-\emph{modifiable} documents, namely Microsoft Word documents.
-Researchers and analysts, especially those creating applied statistical
-analyses, often collaborate with domain experts with less technical
-knowledge. In these cases, the analyst focuses on creating the
-computational components and narrative components related to results and
-interpretation. After this initial document is created, the domain
-expert is free to develop narrative components directly in the document
-without needing to go through the analyst.
+The integration of narrative and computational components was originally
+identified as ``Literate Programming'' by \citet{knuth1984} and software
+tools, like Sweave \citep{leisch2002}, have supported this functionality
+for almost two decades. However, more recently, \proglang{R} Markdown
+has become particularly popular with its success likely being driven by
+two factors. The first is the relative ease with which these documents
+can be constructed. While \LaTeX ~is more expressive, it is relatively
+technical and requires an investment in time to become proficient. By
+contrast \proglang{R} Markdown documents are easier to create and format
+and, when the document is used to create \LaTeX, formatting can be
+passed through to the underlying .tex file. The second factor driving
+adoption is likely its support for creating \emph{modifiable} documents,
+namely Microsoft Word documents. Researchers and analysts, especially
+those creating applied statistical analyses, often collaborate with
+domain experts with less technical knowledge. In these cases, the
+analyst focuses on creating the computational components and narrative
+components related to results and interpretation. After this initial
+document is created, the domain expert is free to develop narrative
+components directly in the document without needing to go through the
+analyst.
 
@@
 results from other steps in a data science or data processing pipeline.
-These other steps including cleaning and analysis often require their
-own environment and configuration with requirements very different than
-the computational needs of creating a presentation. By separating these
+Other steps including cleaning and analysis often require their own
+environment and configuration with requirements very different than the
+computational needs of creating a presentation. By separating these
 components each can be developed independently. At the same time, by
@@
 
-The \pkg{listdown} package itself is relatively simple with 6 distinct
+The \pkg{listdown} package itself is relatively simple with 10 distinct
 methods that can be easily incorporated into existing analysis pipelines
@@
 \item{\bf ld\_workflowr\_header() }{- create a worflowr header}
-\item{\bf listdown() }{- create a listdown object to create an R Markdown document}
+\item{\bf ld\_write\_file() }{- write to and R Markdown file}
+\item{\bf listdown() }{- create a listdown object to create an \proglang{R} Markdown document}
+\item{\bf print.listdown()}{- print the listdown options for \proglang{R} Markdown document creation}
 \end{itemize}
@@
 over basic usage and commentary. This section is meant to convey the
-basic approach used by the package and shows how to describe an output
+approach used by the package and shows how to describe an output
 document using \pkg{listdown}, create a document, and change how the
@@
 
-\hypertarget{basic-usage-and-overview}{%
-\section{Basic usage and overview}\label{basic-usage-and-overview}}
+\hypertarget{basic-usage}{%
+\section{Basic usage}\label{basic-usage}}
 
@@
 
-As a first example, we will consider the a list of visualizations from
-the anscombe data set. The list is composed of four \pkg{ggplot2}
-\citep{wickham2016}elements (named Linear, Non Linear, Outlier Vertical,
-and Outlier Horizontal) each containing a scatter plot from the famous
-Anscome Quartet - made available in the \pkg{datasets} package
-\citep{R}. From the \texttt{computational\_components} list, we would
-like to create a document with four sections with names corresponding to
-the list names, each containing their respective visualizations.
+As a starting point, we will consider the a list of visualizations from
+the Anscombe data set below. The list is composed of four \pkg{ggplot2}
+\citep{wickham2016} elements (named Linear, Non Linear, Outlier
+Vertical, and Outlier Horizontal) each containing a scatter plot from
+the Anscombe Quartet - made available in the \pkg{datasets} package
+\citep{R}. From the \code{computational_components} list, we would like
+to create a document with four sections with names corresponding to the
+list names, each containing their respective visualizations. The
+structure of a document derived from the \code{computational_components}
+list can be visualized using the \code{ld_cc_dendro()} function, and its
+output is below.
 
 \begin{CodeChunk}
-
 \begin{CodeInput}
-R> # Use ggplot2 to create the visualizations.
 R> library(ggplot2)
 R> 
-R> # Load the Anscombe Quartet.
+R> library(listdown)
+R> 
 R> data(anscombe)
 R> 
-R> # Create the ggplot objects to display.
 R> computational_components <- list(
-R+     Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
-R+     `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
-R+     `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + 
-R+       geom_point(),
-R+     `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + 
-R+       geom_point())
++   Linear = ggplot(anscombe, aes(x = x1, y = y1)) + geom_point(),
++   `Non Linear` = ggplot(anscombe, aes(x = x2, y = y2)) + geom_point(),
++   `Outlier Vertical`= ggplot(anscombe, aes(x = x3, y = y3)) + 
++     geom_point(),
++   `Outlier Horizontal` =  ggplot(anscombe, aes(x = x4, y = y4)) + 
++     geom_point())
 R> 
-R> # Save the file to disk to be read by the output R Markdown document.
-R> saveRDS(computational_components, "comp-comp.rds")
+R> ld_cc_dendro(computational_components)
 \end{CodeInput}
+\begin{CodeOutput}
+
+computational_components
+  |-- Linear
+  |  o-- object of type(s):gg ggplot
+  |-- Non Linear
+  |  o-- object of type(s):gg ggplot
+  |-- Outlier Vertical
+  |  o-- object of type(s):gg ggplot
+  o-- Outlier Horizontal
+     o-- object of type(s):gg ggplot
+\end{CodeOutput}
 \end{CodeChunk}
@@
 
-Creating a document from the \texttt{computational\_components} requires
-two steps. First, we will create a \texttt{listdown} object that
-specifies how the \texttt{computational\_components} object will be
-loaded into the document, which libraries and code needs to be included,
-and how the list elements will be presented in the output R markdown
-document.
+Creating a document whose structure and content are described
+\code{computational_components} requires two steps. First, we will
+create a \code{listdown} object specifying how the \newline
+\code{computational_components} object will be loaded into the document,
+which libraries and code needs to be included, and how the list elements
+will be presented in the output R markdown document. A human-readable
+\code{print} function is included in the package and is the default
+output of the object. It should be noted that the output shows options
+that will be described and illustrated later.
 
 \begin{CodeChunk}
-
 \begin{CodeInput}
-R> library(listdown)
+R> saveRDS(computational_components, "comp-comp.rds")
 R> 
 R> ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"),
-R+                package = "ggplot2")
++                package = "ggplot2")
+R> 
+R> ld
+\end{CodeInput}
+\begin{CodeOutput}
+
+Listdown object description
+
+    Package(s) imported:
+    ggplot2
+
+    Setup expression(s) (run before packages are loaded):
+    (none)
+
+    Initial expression(s) (run after packages are loaded):
+    (none)
+
+    Expression to read data:
+    readRDS("comp-comp.rds")
+
+    Decorator(s):
+    (none)
+
+    Defaut decorator:
+    identity
+
+    Chunk option(s):
+    (none)
+
+    Decorator chunk option(s):
+    (none)
+\end{CodeOutput}
+\end{CodeChunk}
+
+The \code{ld} object, along with the computational components in the
+\code{comp-comp.rds} file are sufficient to to create the sections,
+subsections, and \proglang{R} chunks of a document. The only other thing
+required to create the document is the header. The \pkg{listdown}
+package currently supports regular R Markdown and \pkg{workflowr} as
+\code{yml} objects from the \pkg{yaml} package \citep{yaml}. These
+objects are stored as named lists in \proglang{R} and are easily
+modified to accommodate document parameters. A complete document can
+then be written to the console using the code shown below. It could
+easily be written to a file for rendering using the
+\code{ld_write_file()} function, for example.
+
+\begin{CodeChunk}
+\begin{CodeInput}
+R> ld_write_file(ld_rmarkdown_header("Anscombe's Quartet",
++                                   author = "Francis Anscombe",
++                                   date = "1973"),
++               ld,
++               "anscome-example.rmd")
 \end{CodeInput}
@@
 
-The \texttt{ld} object, along with the computational components in the
-\texttt{comp-comp.rds} file are sufficient to to create the sections,
-subsections, and R chunks of a document. The only other thing requires
-to create the document is the header. The listdown package currently
-supports regular R Markdown and \pkg{workflowr} as \code{yml} objects
-from the \pkg{yaml} package \citep{yaml}. These objects are stored as
-named lists in R and are easily modified to accomodate document
-parameters. A complete document can then be written to the console using
-the code shown below. It could easily be written to a file for rendering
-using the \texttt{writeLines()} function, for example.
-
-\begin{CodeChunk}
-
-\begin{CodeInput}
-R> doc <- c(
-R>   as.character(ld_rmarkdown_header("Anscombe's Quartet",
-R>                                    author = "Francis Anscombe",
-R>                                    date = "1973")),
-R>   ld_make_chunks(ld))
-R> 
-R> # Write the document.
-R> writeLines("anscome-example.rmd")
-R> 
-R> # Show the document.
-R> doc
-\end{CodeInput}
-\end{CodeChunk}
-
-\begin{CodeChunk}
-
-\begin{CodeOutput}
- [1] "---"                                  
- [2] "title: Anscombe's Quartet"            
- [3] "author: Francis Anscombe"             
- [4] "date: '1973'"                         
- [5] "output: html_document"                
- [6] "---"                                  
- [7] ""                                     
- [8] "```{r}"                               
- [9] "library(ggplot2)"                     
-[10] ""                                     
-[11] "cc_list <- readRDS(\"comp-comp.rds\")"
-[12] "```"                                  
-[13] ""                                     
-[14] "# Linear"                             
-[15] ""                                     
-[16] "```{r}"                               
-[17] "cc_list$Linear"                       
-[18] "```"                                  
-[19] ""                                     
-[20] "# Non Linear"                         
-[21] ""                                     
-[22] "```{r}"                               
-[23] "cc_list$`Non Linear`"                 
-[24] "```"                                  
-[25] ""                                     
-[26] "# Outlier Vertical"                   
-[27] ""                                     
-[28] "```{r}"                               
-[29] "cc_list$`Outlier Vertical`"           
-[30] "```"                                  
-[31] ""                                     
-[32] "# Outlier Horizontal"                 
-[33] ""                                     
-[34] "```{r}"                               
-[35] "cc_list$`Outlier Horizontal`"         
-[36] "```"                                  
-\end{CodeOutput}
-\end{CodeChunk}
-
-The \texttt{listdown()} function provides \emph{document-wide} R chunk
+The \code{listdown()} function provides \emph{document-wide} R chunk
 options for displaying computational components. The chunk options are
-exactly the same as those in the R markdown document and can be used to
+exactly the same as those in the R Markdown document and can be used to
 tailor the default presentation for a variety of needs. The complete set
@@
 \begin{CodeChunk}
-
 \begin{CodeInput}
 R> ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
-R+                package = "ggplot2",
-R+                echo = FALSE)
++                package = "ggplot2",
++                echo = FALSE)
 R> 
-R> # Show the updated chunk where the library is loaded and data is read.
 R> ld_make_chunks(ld)[1:7]
 \end{CodeInput}
-
 \begin{CodeOutput}
@@
 
-The first example is simple in part because the ggplot objects both
-contains the data we want to display and, at the same time, provides the
-mechanism for presenting them - rendering them in a graph. However, this
-is not always the case. The objects being stored in the list of
-computational components may not translate directly to the presentation
-in a document. In these cases, a function is needed that takes the list
-component and returns an object to be displayed. For example, suppose
-that, along with showing graphs from the Anscombe Quartet, we would like
-to include the data themselves. We could add the data to the
-\texttt{computational\_components} list and then create the document
-with:
+The first example is simple in part because the \code{ggplot} objects
+both contains the data we want to display and, at the same time,
+provides the mechanism for presenting them - rendering them in a
+visualization However, this is not always the case. The objects being
+stored in the list of computational components may not translate
+directly to the presentation in a document. In these cases, a function
+is needed that takes the list component and returns an object to be
+displayed. For example, suppose that, along with showing graphs from the
+Anscombe Quartet, we would like to include the data themselves. We could
+add the data to the \code{computational_components} list and then create
+the document with:
 
 \begin{CodeChunk}
-
 \begin{CodeInput}
@@
 \end{CodeInput}
-
 \begin{CodeOutput}
@@
 returns an object for presentation in the output directory. A decorator
-is specified using the \texttt{decorator} parameter of the
-\texttt{listdown()} function using a named list where the name
-corresponds to the type and the element correspond to the function or
-method that will decorate an object of that type. For example, the
-\texttt{anscombe} data set can be decorated with the
-\texttt{DT::datatable()} function \citep{xie2020} as:
+is specified using the \code{decorator} parameter of the
+\code{listdown()} function using a named list where the name corresponds
+to the type and the element correspond to the function or method that
+will decorate an object of that type. For example, the \code{anscombe}
+data set can be decorated with the \code{DT::datatable()} function
+\citep{xie2020} as:
 
 \begin{CodeChunk}
-
 \begin{CodeInput}
 R> ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
-R+                package = c("ggplot2", "DT"),
-R+                decorator = list(data.frame = datatable))
++                package = c("ggplot2", "DT"),
++                decorator = list(data.frame = datatable))
 R> 
@@
 inherit from a common class, the more abstract classes should appear at
-the end of the list. This will ensure that specialized classes will be
-encountered first in the resolution process. It should be noted that an
-object's type is first checked against the decorator name list and then
-checked to see if it is a list. This allows a user to both decorate a
-list and retain \texttt{"list"} in its class attributes.
+the right-end of the list. This will ensure that specialized classes
+will be encountered first in the resolution process. It should be noted
+that an object's type is first checked against the decorator name list
+and then checked to see if it is a list. This allows a user to both
+decorate a list and retain \code{"list"} in its class attributes.
 
-A separate argument, \texttt{default\_decorator}, allows the user to
+A separate argument, \code{default_decorator}, allows the user to
 specify the default decorator for an object whose type does not appear
-in the \texttt{decorator} list. This allows the user to specify any
-class name for the decorator and avoids a potential type name collision
-with a default decorator whose name is determined by convention. By
-default, this argument is set to \texttt{identity} but it can be use to
-not display a computational component by default if the argument is set
-to \texttt{NULL}.
+in the \code{decorator} list. This allows the user to specify any class
+name for the decorator and avoids a potential type name collision with a
+default decorator whose name is determined by convention. By default,
+this argument is set to \code{identity} but it can be use to not display
+a computational component by default if the argument is set to
+\code{NULL}.
+
+It should be noted that it is not possible to decorate a list and an
+attempt to do so results in an error. This is because, when generating a
+document, the \texttt{ld\_make\_chunks()} function recursively descends
+into the list of computational components. The decision to descend is
+made based on the type of the element being visited. If it is a list,
+then it descends otherwise it presents the object. However, a list can't
+designate both an object to hold elements for presentation and an object
+to be presented. To present arbitrary list elements, including lists, a
+user may add class information to a list element and a corresponding
+decorator.
 
@@
 three subsections ``Sepal.Width'', ``Petal.Length'', and ``Colored''.
-The ``Colored'' subsection has two sub-subsections, ``Sepal.Width'' and
-``Petal.Length''. The structure can be seen using the
-\texttt{ld\_cc\_dendro()} function.
+The ``Colored'' subsection has two subsubsections, ``Sepal.Width'' and
+``Petal.Length''. The structure can once again be seen using the
+\code{ld_cc_dendro()} function.
 
 \begin{CodeChunk}
-
 \begin{CodeInput}
-R> # Create a more hierarchical list of computational components.
 R> comp_comp2 <- list(
-R+   Iris = iris,
-R+   Sepal.Length = list(
-R+     Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + 
-R+       geom_point(),
-R+     Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + 
-R+       geom_point(),
-R+     Colored = list(
-R+       Sepal.Width = ggplot(iris, 
-R+                           aes(x = Sepal.Length, y = Sepal.Width, 
-R+                               color = Species)) + geom_point(),
-R+       Petal.Length = ggplot(iris,
-R+                             aes(x = Sepal.Length, y = Petal.Length, 
-R+                                 color = Species)) + geom_point())))
++   Iris = iris,
++   Sepal.Length = list(
++     Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + 
++       geom_point(),
++     Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + 
++       geom_point(),
++     Colored = list(
++       Sepal.Width = ggplot(iris, 
++                           aes(x = Sepal.Length, y = Sepal.Width, 
++                               color = Species)) + geom_point(),
++       Petal.Length = ggplot(iris,
++                             aes(x = Sepal.Length, y = Petal.Length, 
++                                 color = Species)) + geom_point())))
 R> 
-R> # Create the dendrogram.
 R> ld_cc_dendro(comp_comp2)
 \end{CodeInput}
-
 \begin{CodeOutput}
@@
 
-\hypertarget{initialization-code}{%
-\subsection{Initialization code}\label{initialization-code}}
+\hypertarget{setup-and-initialization-code}{%
+\subsection{Setup and initialization
+code}\label{setup-and-initialization-code}}
 
-The \texttt{listdown()} function facilitates the insertion of
-initialization code through the \texttt{init\_expr} argument. Code is
-inserted immediately after the libraries are loaded in the R Markdown
-document. In general, it is suggested that the number of initial
-expressions be kept small so that the \proglang{R} Markdown document is
-easy to read. If a large number of functions are required by the target
-\proglang{R} Markdown document then they can be put into a file and
-sourced using the initial expression. As an example, suppose we are
-creating an html document and presenting data using the
-\texttt{datatable()} function. However, we do not want to include the
+The \code{listdown()} function facilitates the insertion of setup and
+initialization code through the \code{setup_expr} and \code{init_expr}
+arguments. If and argument is provided to the \code{setup_expr}, then
+the first code chunk of the document will have the specified code
+inserted. This code chunk is named ``setup'' and the include parameter
+is set to \code{FALSE}. When the \code{init_expr} argument is specified,
+code is inserted immediately after the libraries are loaded in the R
+Markdown document. In general, it is suggested that the number of
+initial expressions be kept small so that the \proglang{R} Markdown
+document is easy to read. If a large number of functions are required by
+the target \proglang{R} Markdown document then they can be put into a
+file and sourced using the initial expression. As an example, suppose we
+are creating an html document and presenting data using the
+\code{datatable()} function. However, we do not want to include the
 search capabilities provided. This can be easily accomplished by
-creating a new function, \texttt{datatable\_no\_search()}, created using
-the \texttt{partial()} function \cite{purrr} to partially apply
-\texttt{list(dom\ =\ \textquotesingle{}t\textquotesingle{})} to the
-\texttt{options} argument of \texttt{datatable}.
+creating a new function, \code{datatable_no_search()}, created using the
+\code{partial()} function \cite{purrr} to partially apply
+\code{list(dom = 't')} to the \code{options} argument of
+\code{datatable}.
 
 \begin{CodeChunk}
-
 \begin{CodeInput}
@@
 R> ld <- listdown(load_cc_expr = readRDS("comp-comp2.rds"),
-R+                package = c("ggplot2", "DT", "purrr"),
-R+                decorator = list(ggplot = identity,
-R+                                 data.frame = datatable_no_search),
-R+                init_expr = {
-R+                  datatable_no_search <- partial(datatable,
-R+                                                 options = list(dom = 't'))
-R+                  },
-R+                echo = FALSE)
++                package = c("ggplot2", "DT", "purrr"),
++                decorator = list(ggplot = identity,
++                                 data.frame = datatable_no_search),
++                setup_expr = knitr::opts_chunk$set(echo = FALSE),
++                init_expr = {
++                  datatable_no_search <- partial(datatable,
++                                                 options = list(dom = 't'))
++                  })
 R> 
-R> ld_make_chunks(ld)[2:10]
+R> ld_make_chunks(ld)[2:14]
 \end{CodeInput}
-
 \begin{CodeOutput}
-[1] "```{r echo = FALSE}"                                                   
-[2] "library(ggplot2)"                                                      
-[3] "library(DT)"                                                           
-[4] "library(purrr)"                                                        
-[5] ""                                                                      
-[6] "cc_list <- readRDS(\"comp-comp2.rds\")"                                
-[7] ""                                                                      
-[8] "datatable_no_search <- partial(datatable, options = list(dom = \"t\"))"
-[9] "```"                                                                   
+ [1] "```{r setup, include = FALSE}"                                         
+ [2] "knitr::opts_chunk$set(echo = FALSE)"                                   
+ [3] "```"                                                                   
+ [4] ""                                                                      
+ [5] "```{r}"                                                                
+ [6] "library(ggplot2)"                                                      
+ [7] "library(DT)"                                                           
+ [8] "library(purrr)"                                                        
+ [9] ""                                                                      
+[10] "datatable_no_search <- partial(datatable, options = list(dom = \"t\"))"
+[11] ""                                                                      
+[12] "cc_list <- readRDS(\"comp-comp2.rds\")"                                
+[13] "```"                                                                   
 \end{CodeOutput}
@@
 This is accomplished in the \pkg{listdown} package when a
-\texttt{listdown} object is created using the
-\texttt{decorator\_chunk\_opts} option in the \texttt{listdown()}
-function. For example, associating all \texttt{ggplot} objects with
-\proglang{R} chunks having a width of 100 and a height of 200 can be
-accomplished with the following code and it can be seen that only chunk
-options associated with a plot are modified.
+\code{listdown} object is created using the \code{decorator_chunk_opts}
+option in the {]}code\{listdown()\} function. For example, associating
+all \code{ggplot} objects with \proglang{R} chunks having a width of 100
+and a height of 200 can be accomplished with the following code and it
+can be seen that only chunk options associated with a plot are modified.
 
 \begin{CodeChunk}
-
 \begin{CodeInput}
 R> ld <- listdown(load_cc_expr = readRDS("comp-comp2.rds"),
-R+                package = c("ggplot2", "DT", "purrr"),
-R+                decorator_chunk_opts = 
-R+                  list(ggplot = list(fig.width = 100,
-R+                                     fig.height = 200)),
-R+                init_expr = {
-R+                  datatable_no_search <- partial(datatable,
-R+                                                 options = list(dom = 't'))
-R+                  },
-R+                echo = FALSE)
++                package = c("ggplot2", "DT", "purrr"),
++                decorator_chunk_opts = 
++                  list(ggplot = list(fig.width = 100,
++                                     fig.height = 200)),
++                init_expr = {
++                  datatable_no_search <- partial(datatable,
++                                                 options = list(dom = 't'))
++                  },
++                echo = FALSE)
 R> 
@@
 \begin{CodeChunk}
-
 \begin{CodeInput}
@@
 \end{CodeChunk}
+
+\hypertarget{presenting-base-graphics}{%
+\subsection{Presenting base graphics}\label{presenting-base-graphics}}
+
+Since a base plot does not encapsulate the state and ability to present
+the plot, like a \texttt{ggplot} object, for example it is not possible
+to assign a base graphic to a list element and present it. Instead, it
+is recommended that the corresponding data is held as a list element,
+with base graphic options, and that that element is given a class and a
+corresponding decorator. Using this approach the decorator generates the
+visualization though a call to base graphics when the output document is
+rendered.
 
@@
 R> 
-R> # Function to create the computational components.
 R> make_surv_cc <- function(trial, treat, surv_cond_chars) {
-R+   # Create Table 1 by treatment
-R+   table_1 <- trial %>%
-R+     tbl_summary(by = all_of(treat)) %>%
-R+     gtsummary::as_flextable()
-R+ 
-R+   # Create survival plots base on survival characteristics
-R+   scs <- lapply(c("1", surv_cond_chars),
-R+                 function(sc) {
-R+                   sprintf("Surv(ttdeath, death) ~ %s + %s", treat, sc) %>%
-R+                     as.formula() %>%
-R+                     surv_fit(trial) %>%
-R+                     ggsurvplot()
-R+                 })
-R+   names(scs) <- c("Overall", tools::toTitleCase(surv_cond_chars))
-R+   list(`Table 1` = table_1, `Survival Plots` = scs)
-R+ }
++   table_1 <- trial %>%
++     tbl_summary(by = all_of(treat)) %>%
++     gtsummary::as_flex_table()
++ 
++   scs <- lapply(c("1", surv_cond_chars),
++                 function(sc) {
++                   sprintf("Surv(ttdeath, death) ~ %s + %s", treat, sc) %>%
++                     as.formula() %>%
++                     surv_fit(trial) %>%
++                     ggsurvplot()
++                 })
++   names(scs) <- c("Overall", tools::toTitleCase(surv_cond_chars))
++   list(`Table 1` = table_1, `Survival Plots` = scs)
++ }
 R> 
-R> # Create the computational components and write to surv-cc.rds.
 R> surv_cc <- make_surv_cc(trial, treat = "trt",
-R+                         surv_cond_chars = c("stage", "grade"))
++                         surv_cond_chars = c("stage", "grade"))
 R> 
@@
 As shown before, the report is created by saving the computational
-components, creating a listdown object, writing the \proglang{R}
+components, creating a \code{listdown} object, writing the \proglang{R}
 Markdown document, and rendering it. The resulting document,
 trial-report.html, can then be placed in a shared space where it can be
-viewed and interpreted by stakeholders in the clincial trial. The
-\proglang{R} Markdown document created by this code is shown in Appendix
-1.
+viewed and interpreted by stakeholders in the clinical trial. The
+\proglang{R} Markdown document created by this code is shown in
+supplementary materials.
 
 \begin{CodeChunk}
-
 \begin{CodeInput}
-R> # Turn the survplots into a list to show the individual components.
 R> class(surv_cc$`Survival Plots`$Overall) <- 
-R+   class(surv_cc$`Survival Plots`$Stage) <-
-R+   class(surv_cc$`Survival Plots`$Grade) <- "list"
++   class(surv_cc$`Survival Plots`$Stage) <-
++   class(surv_cc$`Survival Plots`$Grade) <- "list"
 R> 
-R> # Create a tab for each element of the survplot.
 R> names(surv_cc$`Survival Plots`) <- 
-R+   paste(names(surv_cc$`Survival Plots`), "{.tabset}")
++   paste(names(surv_cc$`Survival Plots`), "{.tabset}")
 R> 
-R> # Rename the elements
 R> names(surv_cc$`Survival Plots`$`Overall {.tabset}`) <- 
-R+   names(surv_cc$`Survival Plots`$`Stage {.tabset}`) <- 
-R+   names(surv_cc$`Survival Plots`$`Grade {.tabset}`) <- 
-R+   c("Plot", "Data", "Table")
++   names(surv_cc$`Survival Plots`$`Stage {.tabset}`) <- 
++   names(surv_cc$`Survival Plots`$`Grade {.tabset}`) <- 
++   c("Plot", "Data", "Table")
 R>   
-R> # Save the updated object for presentation.
 R> saveRDS(surv_cc, "surv-cc.rds")
 R> 
-R> # Create the listdown object with appropriate dependencies
-R> # and presentation parameters.
 R> ld_surv <- listdown(load_cc_expr = readRDS("surv-cc.rds"),
-R+                     package = c("gtsummary", "flextable", "DT", 
-R+                                 "ggplot2"),
-R+                     decorator_chunk_opts = 
-R+                       list(gg = list(fig.width = 8,
-R+                                      fig.height = 6)),
-R+                     decorator = list(data.frame = datatable),
-R+                     echo = FALSE,
-R+                     message = FALSE,
-R+                     warning = FALSE,
-R+                     fig.width = 7,
-R+                     fig.height = 4.5)
++                     package = c("gtsummary", "flextable", "DT", 
++                                 "ggplot2"),
++                     decorator_chunk_opts = 
++                       list(gg = list(fig.width = 8,
++                                      fig.height = 6)),
++                     decorator = list(data.frame = datatable),
++                     echo = FALSE,
++                     message = FALSE,
++                     warning = FALSE,
++                     fig.width = 7,
++                     fig.height = 4.5)
 R> 
-R> # Write an RMarkdown header and chunks derived from the 
-R> # computational components and listdown object to trial-report.rmd.
 R> writeLines(
-R+   paste(c(
-R+     as.character(ld_rmarkdown_header("Simple Trial Report")),
-R+     ld_make_chunks(ld_surv))),
-R+   "trial-report.rmd")
++   paste(c(
++     as.character(ld_rmarkdown_header("Simple Trial Report")),
++     ld_make_chunks(ld_surv))),
++   "trial-report.rmd")
 R> 
-R> # Render the RMarkdown file to html and show it.
 R> render("trial-report.rmd", quiet = TRUE)

### 2020-12-07 inst/jss/supplemental-material/listdown-jss.rmd
Minor changes.

@@
     - 38 Princes Street
-    - Auckland Central, Aukland 1010, NZ
+    - Auckland Central, Auckland 1010, NZ
     email: s.urbanek@auckland.ac.nz
@@
   Reproducible document standards, like \proglang{R} Markdown, facilitate the programmatic creation of documents whose content is itself programmatically generated.
-While these documents are generally not complete in the sense that they will not include prose content, generated by an author to provide context, a narrative, etc., programmatic generation can provide substantial efficiencies for structuring and constructing documents.
-This paper explores the programmatic generation of reproducible by distinguishing components that can be created by computational means from those requiring human-generated prose, providing guidelines for the generation of these documents, and identifying a use case in clinical trial reporting.
+While programmatic content alone may not be sufficient for a rendered document since it does not include prose (content generated by an author to provide context, a narrative, etc.) programmatic generation can provide substantial efficiencies for structuring and constructing documents.
+This paper explores the programmatic generation of reproducible documents by distinguishing components that can be created by computational means from those requiring human-generation, providing guidelines for the generation of these documents, and identifying a use case in clinical trial reporting.
 These concepts and use case are illustrated through the \pkg{listdown} package for the \proglang{R} programming environment, which is is currently available on the Comprehensive R Archive Network (CRAN).
@@
 
-\proglang{R} Markdown [@baumer2014] facilitates the construction of computationally reproducible documents by allowing authors to insert \proglang{R} code for data processing, exploration, analysis, table-making, and visualization directly into structured, electronic documents.
-The resulting documents are made up of these chunks of \proglang{R} code, which we will refer to as _computational components_ since they are generated by computational means, as well as _narrative components_, which (in scientific writing) is prose intended to contextualize computational components, provide background, define goals, establish themes, and convey the results of the document.
-The integration of narrative and computational components was identified as "Literate Programming" by @knuth1984 and software tools, like Sweave [@leisch2002], have supported this functionality for almost two decades.
+\proglang{R} Markdown [@baumer2014, @rmarkdownbook] facilitates the construction of computationally reproducible documents by allowing authors to insert \proglang{R} code for data processing, exploration, analysis, table-making, and visualization directly into structured, electronic documents.
+The resulting documents are made up of these chunks of \proglang{R} code, which we will refer to as _computational components_ since they are generated by computational means, as well as _narrative components_, which (in scientific writing) is prose intended to contextualize computational components, provide background, define goals, establish themes, and convey results.
+These documents are then used to render output documents, for users to read in the form of .html, .pdf, .doc, or other formats using the \pkg{knitr} package [@knitrbook].
 
-\proglang{R} Markdown is particularly popular with its success likely being driven by two factors.
+The integration of narrative and computational components was originally identified as "Literate Programming" by @knuth1984 and software tools, like Sweave [@leisch2002], have supported this functionality for almost two decades.
+However, more recently, \proglang{R} Markdown has become particularly popular with its success likely being driven by two factors.
 The first is the relative ease with which these documents can be constructed.
@@
 First, it allows us to distinguish the presentation of analytical results from other steps in a data science or data processing pipeline.
-These other steps including cleaning and analysis often require their own environment and configuration with requirements very different than the computational needs of creating a presentation.
+Other steps including cleaning and analysis often require their own environment and configuration with requirements very different than the computational needs of creating a presentation.
 By separating these components each can be developed independently.
@@
 
-The \pkg{listdown} package itself is relatively simple with 6 distinct methods that can be easily incorporated into existing analysis pipelines for automatically creating documents that can be used for data exploration and reviewing analysis results as well as a starting point for a more formal write up.
+The \pkg{listdown} package itself is relatively simple with 10 distinct methods that can be easily incorporated into existing analysis pipelines for automatically creating documents that can be used for data exploration and reviewing analysis results as well as a starting point for a more formal write up.
 These methods include:
@@
 \item{\bf ld\_workflowr\_header() }{- create a worflowr header}
+\item{\bf ld\_write\_file() }{- write to and R Markdown file}
 \item{\bf listdown() }{- create a listdown object to create an \proglang{R} Markdown document}
@@
 The next section goes over basic usage and commentary.
-This section is meant to convey the basic approach used by the package and shows how to describe an output document using \pkg{listdown}, create a document, and change how the presentation of computational components can be specialized using \pkg{listdown} decorators.
+This section is meant to convey the approach used by the package and shows how to describe an output document using \pkg{listdown}, create a document, and change how the presentation of computational components can be specialized using \pkg{listdown} decorators.
 With the user accustomed to the package's basic usage, section 3 describes the design of the package.
@@
 
-# Basic usage and overview
+# Basic usage
 
@@
 As a starting point, we will consider the a list of visualizations from the Anscombe data set below.
-The list is composed of four \pkg{ggplot2} [@wickham2016] elements (named Linear, Non Linear, Outlier Vertical, and Outlier Horizontal) each containing a scatter plot from the Anscombe Quartet - made available in the \pkg{datasets} package [@R] as shown in Figure \ref{cc1}.
+The list is composed of four \pkg{ggplot2} [@wickham2016] elements (named Linear, Non Linear, Outlier Vertical, and Outlier Horizontal) each containing a scatter plot from the Anscombe Quartet - made available in the \pkg{datasets} package [@R].
 From the \code{computational_components} list, we would like to create a document with four sections with names corresponding to the list names, each containing their respective visualizations.
@@
 The \code{ld} object, along with the computational components in the \code{comp-comp.rds} file are sufficient to to create the sections, subsections, and \proglang{R} chunks of a document.
-The only other thing requires to create the document is the header.
-The listdown package currently supports regular R Markdown and \pkg{workflowr} as \code{yml} objects from the \pkg{yaml} package [@yaml].
+The only other thing required to create the document is the header.
+The \pkg{listdown} package currently supports regular R Markdown and \pkg{workflowr} as \code{yml} objects from the \pkg{yaml} package [@yaml].
 These objects are stored as named lists in \proglang{R} and are easily modified to accommodate document parameters.
 A complete document can then be written to the console using the code shown below.
-It could easily be written to a file for rendering using the \code{writeLines()} function, for example.
+It could easily be written to a file for rendering using the \code{ld_write_file()} function, for example.
 
 ```{r eval = FALSE}
-doc <- c(
-  as.character(ld_rmarkdown_header("Anscombe's Quartet",
+ld_write_file(ld_rmarkdown_header("Anscombe's Quartet",
                                   author = "Francis Anscombe",
-                                   date = "1973")),
-  ld_make_chunks(ld))
-
-writeLines("anscome-example.rmd")
-
-doc
-```
-
-```{r eval = TRUE, echo = FALSE}
-doc <- c(
-  as.character(ld_rmarkdown_header("Anscombe's Quartet",
-                                   author = "Francis Anscombe",
-                                   date = "1973")),
-  ld_make_chunks(ld))
-
-doc
+                                  date = "1973"),
+              ld,
+              "anscome-example.rmd")
 ```
@@
 The \code{listdown()} function provides _document-wide_ R chunk options for displaying computational components.
-The chunk options are exactly the same as those in the R markdown document and can be used to tailor the default presentation for a variety of needs.
+The chunk options are exactly the same as those in the R Markdown document and can be used to tailor the default presentation for a variety of needs.
 The complete set of options can be found in the R Markdown Reference Guide [@rmarkdownref].
@@
 
-The first example is simple in part because the ggplot objects both contains the data we want to display and, at the same time, provides the mechanism for presenting them - rendering them in a graph.
-However, this is not always the case.
+The first example is simple in part because the \code{ggplot} objects both contains the data we want to display and, at the same time, provides the mechanism for presenting them - rendering them in a visualization However, this is not always the case.
 The objects being stored in the list of computational components may not translate directly to the presentation in a document.
@@
 The function or method is selected from the corresponding name which the element first inherits from.
-This means that when customizing the presentation of objects that inherit from a common class, the more abstract classes should appear at the end of the list.
+This means that when customizing the presentation of objects that inherit from a common class, the more abstract classes should appear at the right-end of the list.
 This will ensure that specialized classes will be encountered first in the resolution process.
@@
 By default, this argument is set to \code{identity} but it can be use to not display a computational component by default if the argument is set to \code{NULL}.
+
+It should be noted that it is not possible to decorate a list and an attempt to do so results in an error.
+This is because, when generating a document, the `ld_make_chunks()` function recursively descends into the list of computational components.
+The decision to descend is made based on the type of the element being visited.
+If it is a list, then it descends otherwise it presents the object.
+However, a list can't designate both an object to hold elements for presentation and an object to be presented.
+To present arbitrary list elements, including lists, a user may add class information to a list element and a corresponding decorator.
 
@@
 
-## Initialization code
+## Setup and initialization code
 
-The \code{listdown()} function facilitates the insertion of initialization code through the \code{init_expr} argument.
-Code is inserted immediately after the libraries are loaded in the R Markdown document.
+The \code{listdown()} function facilitates the insertion of setup and initialization code through the \code{setup_expr} and \code{init_expr} arguments.
+If and argument is provided to the \code{setup_expr}, then the first code chunk of the document will have the specified code inserted.
+This code chunk is named "setup" and the include parameter is set to \code{FALSE}.
+When the \code{init_expr} argument is specified,
+code is inserted immediately after the libraries are loaded in the R Markdown document.
 In general, it is suggested that the number of initial expressions be kept small so that the \proglang{R} Markdown document is easy to read.
@@
                                 data.frame = datatable_no_search),
+               setup_expr = knitr::opts_chunk$set(echo = FALSE),
                init_expr = {
@@
                                                 options = list(dom = 't'))
-                 },
-               echo = FALSE)
+                 })
 
-ld_make_chunks(ld)[2:10]
+ld_make_chunks(ld)[2:14]
 ```
@@
 
+## Presenting base graphics
+
+Since a base plot does not encapsulate the state and ability to present the plot, like a `ggplot` object, for example it is not possible to assign a base graphic to a list element and present it.
+Instead, it is recommended that the corresponding data is held as a list element, with base graphic options, and that that element is given a class and a corresponding decorator.
+Using this approach the decorator generates the visualization though a call to base graphics when the output document is rendered.
+
 # A simple example: Reporting on the gtsummary::trial dataset
@@
     tbl_summary(by = all_of(treat)) %>%
-    gtsummary::as_flextable()
+    gtsummary::as_flex_table()
 

### 2020-12-07 R/add-load-cc-expr.r

@@ -6,7 +6,6 @@
 #' return is an unevaluated expression. 
 #' @param load_cc_expr a string or expression that should be use to load 
 #' the computational components.
-#' @export
 create_load_cc_expr <- function(load_cc_expr) {
   if (is.character(load_cc_expr)) {
     # If it's a string literal, then call str2lang on it.

### 2020-12-07 inst/jss/clean.sh

@@ -1,7 +1,7 @@
 #! /bin/sh
-rm *.aux 
-rm *.bbl 
-rm *.blg 
-rm *.log 
-rm *.out 
+rm -f *.aux 
+rm -f *.bbl 
+rm -f *.blg 
+rm -f *.log 
+rm -f *.out 
 rm -rf kane-listdown_files 

### 2020-12-07 inst/jss/supplemental-material/clean.sh

@@ -2,6 +2,11 @@
 rm -f *.rds 
 rm -f *.pdf 
 rm -f *.tex 
+rm -f *.aux
+rm -f *.blg
+rm -f *.log
+rm -f *.out
+rm -f *.bbl
 rm -f *.html 
 rm -f *.md
 rm -rf figure 

### 2020-12-07 inst/jss/supplemental-material/listdown-jss.R

@@ -26,25 +26,11 @@ ld
 
 
 ## ----eval = FALSE-------------------------------------------------------------
-## doc <- c(
-##   as.character(ld_rmarkdown_header("Anscombe's Quartet",
-##                                    author = "Francis Anscombe",
-##                                    date = "1973")),
-##   ld_make_chunks(ld))
-## 
-## writeLines("anscome-example.rmd")
-## 
-## doc
-
-
-## ----eval = TRUE, echo = FALSE------------------------------------------------
-doc <- c(
-  as.character(ld_rmarkdown_header("Anscombe's Quartet",
-                                   author = "Francis Anscombe",
-                                   date = "1973")),
-  ld_make_chunks(ld))
-
-doc
+## ld_write_file(ld_rmarkdown_header("Anscombe's Quartet",
+##                                   author = "Francis Anscombe",
+##                                   date = "1973"),
+##               ld,
+##               "anscome-example.rmd")
 
 
 ## -----------------------------------------------------------------------------
@@ -94,13 +80,13 @@ ld <- listdown(load_cc_expr = readRDS("comp-comp2.rds"),
                package = c("ggplot2", "DT", "purrr"),
                decorator = list(ggplot = identity,
                                 data.frame = datatable_no_search),
+               setup_expr = knitr::opts_chunk$set(echo = FALSE),
                init_expr = {
                  datatable_no_search <- partial(datatable,
                                                 options = list(dom = 't'))
-                 },
-               echo = FALSE)
+                 })
 
-ld_make_chunks(ld)[2:10]
+ld_make_chunks(ld)[2:14]
 
 
 ## -----------------------------------------------------------------------------
@@ -134,7 +120,7 @@ library(rmarkdown)
 make_surv_cc <- function(trial, treat, surv_cond_chars) {
   table_1 <- trial %>%
     tbl_summary(by = all_of(treat)) %>%
-    gtsummary::as_flextable()
+    gtsummary::as_flex_table()
 
   scs <- lapply(c("1", surv_cond_chars),
                 function(sc) {

### 2021-01-04 R/build-site.r
Site building fixes.

@@ -210,7 +210,7 @@ ld_build_html_site <-
   )
 
   if (make_data_dir) {
-    make_dirs_as_needed(data_dir)
+    make_dirs_as_needed(file.path(rmd_dir, data_dir))
   }
   if (make_rmd_dir) {
     make_dirs_as_needed(rmd_dir)
@@ -234,7 +234,7 @@ ld_build_html_site <-
           ("" %in% names(doc_bundles)) ) ) {
     stop("An index.html file must be specified.")
   }
- 
+
   # See if we have an unnamed bundle. It should be the index.rmd file. 
   if (any(names(doc_bundles) == "")) {
     if (sum(names(doc_bundles) == "") > 1) {
@@ -325,12 +325,13 @@ recycle <- function(ind, len) {
 #' @param ... options to send to the rmarkdown::render() function.
 #' @importFrom checkmate assert check_class
 #' @importFrom rmarkdown render
+#' @importFrom fs path_rel
 #' @export
 ld_create_doc <- 
   function(
     ldb, 
     rmd_file_name = basename(tempfile(pattern = "rmarkdown", fileext = ".rmd")),
-    rmd_dir = tempdir(), 
+    rmd_dir = file.path(tempdir(), "rmarkdown"),
     output_dir = file.path(rmd_dir, "pres"),
     render_doc = TRUE,
     cc_file_name = NULL,
@@ -345,22 +346,23 @@ ld_create_doc <-
 
   if (ldb$cc_in_memory) {
     if (is.null(data_dir) && is.null(cc_file_name)) {
-      data_dir <- tempdir()
+      data_dir <- "../data"
       cc_file_name <- basename(tempfile(pattern = "data", fileext = ".rds"))
     }
     if (is.null(data_dir)) {
-      data_dir <- tempdir()
-      warning("Argument `data_dir` is not specified, `tempdir()` will be used.")
+      data_dir <- "../data"
+      warning("Argument `data_dir` is not specified, ../data will be used.")
     }
     if (is.null(cc_file_name)) {
       cc_file_name <- basename(tempfile(pattern = "data", fileext = ".rds"))
       warning("Argument `cc_file_name` not specified ", 
               cc_file_name, " will be used.")
     }
-    data_path <- file.path(path_rel(data_dir, rmd_dir), cc_file_name)
+    data_path <- file.path(rmd_dir, data_dir, cc_file_name)
     saveRDS(ldb$cc, data_path)
[…]

### 2021-01-04 R/chunk-writer.r

@@ -235,9 +235,10 @@ ld_make_chunks.listdown <- function(ld) {
     stop("The load_cc_expr needs to be specified. ",
          "Use `create_load_cc_expr()` to set it.")
   }
-  cc_list <- eval(ld$load_cc_expr)
-  if (is.character(cc_list)) {
-    cc_list <- eval(parse(text = cc_list))
+  if (inherits(ld$load_cc_expr, "call")) {
+    cc_list <- expr_to_string(ld$load_cc_expr)
+  } else {
+    stop("The load_cc_exp element should be a call object.")
   }
   ret_string <- ""
   if (length(ld$setup_expr)) {

### 2021-01-04 tests/testthat/test-create-html-site.r

@@ -56,7 +56,7 @@ site_yaml <-
     rmd_name = c("index.rmd", "iris.rmd"))
 
 site_path <- ld_build_html_site(
-  list(Anscombe = anscombe_page, Iris = iris_page),
+  pages,
   site_yaml,
   view = FALSE,
   quiet = TRUE)

### 2021-01-04 tests/testthat/test-write-file.r

@@ -16,7 +16,7 @@ saveRDS(cc_list, file = rds_file)
 
 read_rds_str <- paste0("readRDS('", rds_file, "')")
 
-ld <- listdown(load_cc_expr = readRDS("cc-list.rds"), package = "ggplot2")
+ld <- listdown(load_cc_expr = read_rds_str, package = "ggplot2")
 
 ld_write_file(
   ld_rmarkdown_header(title = "The Anscombe Quartet",

### 2021-04-26 README.rmd
Yeah.

--- 2020-12-07 README.rmd
@@
 [![](https://www.r-pkg.org/badges/version/listdown?color=blue)](https://cran.r-project.org/package=listdown)
-[![Build Status](https://travis-ci.org/kaneplusplus/listdown.svg?branch=master)](https://travis-ci.org/kaneplusplus/listdown)
-[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kaneplusplus/listdown?branch=master&svg=true)](https://ci.appveyor.com/project/kaneplusplus/listdown)
-[![codecov](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown)
-[![](http://cranlogs.r-pkg.org/badges/last-month/listdown?color=blue)](https://cran.r-project.org/package=listdown)
+[![R-CMD-check](https://github.com/kaneplusplus/listdown/workflows/R-CMD-check/badge.svg)](https://github.com/kaneplusplus/listdown/actions)
 <!-- badges: end -->

### 2021-04-26 R/build-site.r

@@ -345,10 +345,6 @@ ld_create_doc <-
   )
 
   if (ldb$cc_in_memory) {
-    if (is.null(data_dir) && is.null(cc_file_name)) {
-      data_dir <- "../data"
-      cc_file_name <- basename(tempfile(pattern = "data", fileext = ".rds"))
-    }
     if (is.null(data_dir)) {
       data_dir <- "../data"
       warning("Argument `data_dir` is not specified, ../data will be used.")

### 2021-04-26 R/chunk-writer.r

@@ -251,26 +251,26 @@ ld_make_chunks.listdown <- function(ld, rmd_dir = ".") {
            " from directory ", rmd_dir)
     })
   
-  if (is.character(cc_list)) {	   
-    cc_list <- tryCatch(
-      {
-        setwd(rmd_dir)
-        ret <- eval(parse(text = cc_list))
-        setwd(wd)
-        ret
-      },
-      error = function(e) {
-        setwd(wd)
-        stop("Can't evaluate", ld$load_cc_expr, "from directory", rmd_dir)
-      })
-    cc_list <- eval(parse(text = cc_list))
-  }
+#  if (is.character(cc_list)) {	   
+#    cc_list <- tryCatch(
+#      {
+#        setwd(rmd_dir)
+#        ret <- eval(parse(text = cc_list))
+#        setwd(wd)
+#        ret
+#      },
+#      error = function(e) {
+#        setwd(wd)
+#        stop("Can't evaluate", ld$load_cc_expr, "from directory", rmd_dir)
+#      })
+#    cc_list <- eval(parse(text = cc_list))
+#  }
 
-  if (inherits(ld$load_cc_expr, "call")) {
-    cc_list <- expr_to_string(ld$load_cc_expr)
-  } else {
-    stop("The load_cc_expr element should be a call object.")
-  }
+#  if (inherits(ld$load_cc_expr, "call")) {
+#    cc_list <- expr_to_string(ld$load_cc_expr)
+#  } else {
+#    stop("The load_cc_expr element should be a call object.")
+#  }
   ret_string <- ""
   if (length(ld$setup_expr)) {
     ret_string <- c(ret_string, 

### 2021-04-26 R/class-and-tag.r
class_and_tag() added.

@@ -1,0 +1,20 @@
+#' Prepend Class Information and Add Attributes
+#' 
+#' @description listdown decorators map list element to functions. This
+#' function is provided for convenience to prepend a class and attributes,
+#' which can then be used by custom decorators to display those element.
+#' @param .x an object to add class and attribute information to.
+#' @param new_class the name of the class to be prepended to .x.
+#' @param ... the attributes to attach to .x.
+#' @export
+class_and_tag <- function(.x, new_class, ...) {
+  if (!is.character(new_class)) {
+    stop("New class should be of type character.")
+  }
+  dots <- list(...)
+  for (n in names(dots)) {
+    attributes(.x)[[n]] <- dots[[n]]
+  }
+  class(.x) <- c(new_class, class(.x))
+  .x
+}

### 2021-04-26 R/chunk-writer.r
Test fixes.

@@ -209,6 +209,7 @@ print.listdown <- function(x, ...) {
 #' @param ld the listdown object that provides
 #' information on how a presentation object should be displayed in the
 #' output.
+#' @param rmd_dir the R Markdown directory.
 #' @seealso \code{\link{listdown}}
 #' @export
 ld_make_chunks <- function(ld, rmd_dir) {

### 2021-04-26 tests/testthat/test-create-doc.r

@@ -28,8 +28,8 @@ test_that("Create page bundle works", {
 })
 
 
-ldcp <- ld_create_doc(ldb, view = FALSE, quiet = TRUE)
 test_that("A document has been created", {
+  ldcp <- expect_warning(ld_create_doc(ldb, view = FALSE, quiet = TRUE))
   expect_s3_class(ldcp, "ld_page_bundle")
 })
 
@@ -50,6 +50,9 @@ cc_path <- file.path(getwd(), "cc.rds")
 
 read_cc_path_str <- paste0('readRDS("', cc_path, '")')
 ld_bundle_doc(read_cc_path_str, header, ld)
-ld_create_doc(ldb, view = FALSE, quiet = TRUE)
+
+test_that("A document can be created.", {
+  expect_warning(ld_create_doc(ldb, view = FALSE, quiet = TRUE))
+})
 
 unlink("cc.rds")

### 2021-06-14 README.rmd
Code coverage.

@@
 [![R-CMD-check](https://github.com/kaneplusplus/listdown/workflows/R-CMD-check/badge.svg)](https://github.com/kaneplusplus/listdown/actions)
+[![Codecov test coverage](https://codecov.io/gh/kaneplusplus/listdown/branch/master/graph/badge.svg)](https://codecov.io/gh/kaneplusplus/listdown?branch=master)
 <!-- badges: end -->

### 2022-04-11 inst/jss/listdown-jss.tex
Typo.

@@
 package for the \proglang{R} programming environment, which is is
-currently available on the Comprehensive R Archive Network (CRAN).
+currently available on the Comprehensive R Archive Network.
 }
@@
 \begin{itemize}
-\item{\bf as\_ld\_yml() }{- turn a computational component list into YAML with class information}
-\item{\bf ld\_cc\_dendro() }{- create a dendrogram from a list of computational components}
-\item{\bf ld\_chunk\_opts() }{- apply chunk options to a presentation object}
-\item{\bf ld\_ioslides\_header() }{- create an ioslides presentation header}
-\item{\bf ld\_make\_chunks() }{- write a listdown object to a string}
-\item{\bf ld\_rmarkdown\_header() }{- create an R Markdown header}
-\item{\bf ld\_workflowr\_header() }{- create a worflowr header}
-\item{\bf ld\_write\_file() }{- write to and R Markdown file}
-\item{\bf listdown() }{- create a listdown object to create an \proglang{R} Markdown document}
-\item{\bf print.listdown()}{- print the listdown options for \proglang{R} Markdown document creation}
+\item{\bf as\_ld\_yml() }{- turn a computational component list into YAML with class information.}
+\item{\bf ld\_cc\_dendro() }{- create a dendrogram from a list of computational components.}
+\item{\bf ld\_chunk\_opts() }{- apply chunk options to a presentation object.}
+\item{\bf ld\_ioslides\_header() }{- create an ioslides presentation header.}
+\item{\bf ld\_make\_chunks() }{- write a listdown object to a string.}
+\item{\bf ld\_rmarkdown\_header() }{- create an R Markdown header.}
+\item{\bf ld\_workflowr\_header() }{- create a worflowr header.}
+\item{\bf ld\_write\_file() }{- write to and R Markdown file.}
+\item{\bf listdown() }{- create a listdown object to create an \proglang{R} Markdown document.}
+\item{\bf print.listdown()}{- print the listdown options for \proglang{R} Markdown document creation.}
 \end{itemize}
@@
 The rest of this paper is structured as follows. The next section goes
-over basic usage and commentary. This section is meant to convey the
+over basic usage and commentary. It is meant to convey the
 approach used by the package and shows how to describe an output
@@
 \pkg{listdown} decorators. With the user accustomed to the package's
-basic usage, section 3 describes the design of the package. Section 4
+basic usage, Section 3 describes the design of the package. Section 4
 goes over advanced usage of the package including adding initialization
@@
 \begin{CodeInput}
-R> library(ggplot2)
+R> library("ggplot2")
 R> 
-R> library(listdown)
+R> library("listdown")
 R> 
@@
 [2] "```{r echo = FALSE}"                  
-[3] "library(ggplot2)"                     
+[3] "library(\"ggplot2\")"                     
 [4] ""                                     
@@
  [5] "```{r}"                                                                
- [6] "library(ggplot2)"                                                      
- [7] "library(DT)"                                                           
- [8] "library(purrr)"                                                        
+ [6] "library(\"ggplot2\")"
+ [7] "library(\"DT\")" 
+ [8] "library(\"purrr\")"
  [9] ""                                                                      
@@
 \begin{CodeInput}
-R> library(gtsummary)
-R> library(dplyr)
-R> library(survival)
-R> library(survminer)
-R> library(rmarkdown)
+R> library("gtsummary")
+R> library("dplyr")
+R> library("survival")
+R> library("survminer")
+R> library("rmarkdown")
 R> 
@@
 
-\bibliography{../references}
+\bibliography{references}
 

### 2022-04-11 inst/jss/supplemental-material/listdown-jss.rmd
Typo.

@@
 This paper explores the programmatic generation of reproducible documents by distinguishing components that can be created by computational means from those requiring human-generation, providing guidelines for the generation of these documents, and identifying a use case in clinical trial reporting.
-These concepts and use case are illustrated through the \pkg{listdown} package for the \proglang{R} programming environment, which is is currently available on the Comprehensive R Archive Network (CRAN).
+These concepts and use case are illustrated through the \pkg{listdown} package for the \proglang{R} programming environment, which is is currently available on the Comprehensive R Archive Network.
 keywords:
@@
 The next section goes over basic usage and commentary.
-This section is meant to convey the approach used by the package and shows how to describe an output document using \pkg{listdown}, create a document, and change how the presentation of computational components can be specialized using \pkg{listdown} decorators.
-With the user accustomed to the package's basic usage, section 3 describes the design of the package.
+It is meant to convey the approach used by the package and shows how to describe an output document using \pkg{listdown}, create a document, and change how the presentation of computational components can be specialized using \pkg{listdown} decorators.
+With the user accustomed to the package's basic usage, Section 3 describes the design of the package.
 Section 4 goes over advanced usage of the package including adding initialization code to and outputted document as well as how to control chunk-level options.
@@
 ```{r cc1}
-library(ggplot2)
+library("ggplot2")
 
-library(listdown)
+library("listdown")
 
@@
 The \code{listdown()} function facilitates the insertion of setup and initialization code through the \code{setup_expr} and \code{init_expr} arguments.
-If and argument is provided to the \code{setup_expr}, then the first code chunk of the document will have the specified code inserted.
+If an argument is provided to the \code{setup_expr}, then the first code chunk of the document will have the specified code inserted.
 This code chunk is named "setup" and the include parameter is set to \code{FALSE}.
@@
 ```{r, eval = TRUE, message=FALSE, warning=FALSE}
-library(gtsummary)
-library(dplyr)
-library(survival)
-library(survminer)
-library(rmarkdown)
+library("gtsummary")
+library("dplyr")
+library("survival")
+library("survminer")
+library("rmarkdown")
 

### 2022-04-11 R/chunk-writer.r

@@ -175,7 +175,7 @@ print.listdown <- function(x, ...) {
   }
   if ("default_decorator" %in% names(x)) {
     cat("\n")
-    cat("    Defaut decorator:\n")
+    cat("    Default decorator:\n")
     cat("\t", deparse(x$default_decorator), "\n", sep = "")
   }
   if ("chunk_opts" %in% names(x)) { 

### 2022-04-11 inst/jss/supplemental-material/listdown-jss.R

@@ -1,7 +1,7 @@
 ## ----cc1----------------------------------------------------------------------
-library(ggplot2)
+library("ggplot2")
 
-library(listdown)
+library("listdown")
 
 data(anscombe)
 
@@ -111,11 +111,11 @@ ld_make_chunks(ld)[12:16]
 
 
 ## ---- eval = TRUE, message=FALSE, warning=FALSE-------------------------------
-library(gtsummary)
-library(dplyr)
-library(survival)
-library(survminer)
-library(rmarkdown)
+library("gtsummary")
+library("dplyr")
+library("survival")
+library("survminer")
+library("rmarkdown")
 
 make_surv_cc <- function(trial, treat, surv_cond_chars) {
   table_1 <- trial %>%

### 2022-04-11 inst/jss/supplemental-material/make.sh

@@ -1,4 +1,4 @@
 #!/usr/bin/sh
 
 Rscript -e "knitr::knit('listdown-jss.rmd', tangle = TRUE)"
-Rscript -e "knitr::knit('listdown-jss.rmd')"
+Rscript -e "rmarkdown::render('listdown-jss.rmd')"

### 2022-04-11 R/build-site.r
Documentation issue.

@@ -172,6 +172,8 @@ make_dirs_as_needed <- function(dir_paths) {
 #' unnamed bundle, which will be assumed to correspond to an index.rmd file.
 #' @param site_yaml a list of site information, which will be written
 #' to the _site.yml file.
+#' @param site_dir the directory where the site (rmd, data, and html files)
+#' will be written to.
 #' @param rmd_dir the directory where the R Markdown files will reside. By 
 #' default an "rmarkdown" file is written to `tempdir()`.
 #' @param data_dir the location where data can be found for each bundle.

### 2022-11-01 R/build-site.r
?

@@ -36,7 +36,7 @@ ld_bundle_doc <- function(cc, header, ld) {
   mc <- match.call()
 
   cc_in_memory <- FALSE
-  if (inherits(mc$cc, "name")) {
+  if (inherits(mc$cc, "name") || inherits(mc$cc, "call")) {
     if (is.list(cc)) {
       cc_in_memory <- TRUE
     } else if (is.character(cc)) {

### 2022-11-01 tests/testthat/test-create-html-site.r

@@ -49,18 +49,18 @@ anscombe_page <- ld_bundle_doc(anscombe_cc, header, ld)
 
 pages <- list(Anscombe = anscombe_page, Iris = iris_page)
 
-#test_that("Site can be built.", {
-#  site_yaml <- 
-#    ld_site_yaml(
-#      "Test Site", 
-#      tab_name = names(pages),
-#      rmd_name = c("index.Rmd", "iris.Rmd"))
-#
-#  site_path <- ld_build_html_site(
-#    pages,
-#    site_yaml,
-#    view = TRUE,
-#    quiet = TRUE)
-#  expect_equal(basename(site_path), "index.html")
-#})
+test_that("Site can be built.", {
+  site_yaml <- 
+    ld_site_yaml(
+      "Test Site", 
+      tab_name = names(pages),
+      rmd_name = c("index.Rmd", "iris.Rmd"))
+
+  site_path <- ld_build_html_site(
+    pages,
+    site_yaml,
+    view = TRUE,
+    quiet = TRUE)
+  expect_equal(basename(site_path), "index.html")
+})
 

### 2022-11-01 R/build-site.r
Bug fixing on html paths.

@@ -104,7 +104,7 @@ remove_file_extension <- function(x) {
   )
 }
 
-#' Create a Minimalist Site YAML List
+#' Create a Minimal Site YAML List
 #' 
 #' @param site_name the name of the site.
 #' @param tab_name the name of the tabs on the site.
@@ -243,9 +243,8 @@ ld_build_html_site <-
   if (length(data_dir) != 1 && length(data_dir) != length(doc_bundles)) {
     stop("The data directory must be a single directory or one per bundle.")
   }
-
   if (is.null(site_yaml$output_dir) || site_yaml$output_dir == "") {
-    site_yaml$output_dir <- html_dir
+    site_yaml$output_dir <- path_rel(html_dir, rmd_dir)
   } else {
     warning(paste("Output dir specified in yaml list. The `html_dir`", 
                   "argument will be ignored."))
@@ -299,10 +298,11 @@ ld_build_html_site <-
       render_doc = FALSE)
   }
   write_yaml(site_yaml, file.path(rmd_dir, "_site.yml"))
+  
   if (render_site) {
     render_site(rmd_dir, ...)
     if (view) {
-      browseURL(file.path(rmd_dir, html_dir, "index.html"))
+      browseURL(file.path(rmd_dir, site_yaml$output_dir, "index.html"))
     }
   }
   normalizePath(file.path(html_dir, "index.html"), mustWork = FALSE)

### 2022-11-01 tests/testthat/test-create-html-site.r

@@ -60,7 +60,7 @@ test_that("Site can be built.", {
     pages,
     site_yaml,
     view = TRUE,
-    quiet = TRUE)
+    quiet = FALSE)
   expect_equal(basename(site_path), "index.html")
 })
 
